### 2015-08-22 manuscript/moho-inversion.tex
Clean up old tex files and copy make template
from https://github.com/pinga-lab/latex_makefile

\documentclass[twocolumn]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

% Document metadata
% =================
\newcommand{\Title}{
    Sample manuscript
}
\title{\Title}
\author{
    Leonardo Uieda \\ \texttt{my@email.com}
    \and
    Val\'eria C. F. Barbosa \\ \texttt{her@email.com}
}

\usepackage[pdftex,colorlinks=true,hidelinks]{hyperref}
\hypersetup{
    pdftitle={\Title},
    pdfauthor={Leonardo Uieda (my@email.com)},
    pdfsubject={},
    pdfkeywords={},
    pdfcreator={pdfTeX}
}

\begin{document}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nam eu dolor pretium,
egestas mauris sed, dapibus quam. Duis hendrerit mollis nunc a consequat. Nulla
et sem consectetur, interdum velit eget, aliquam ipsum. Praesent sagittis
tortor diam, sed ultrices magna ullamcorper vitae. Proin vitae orci augue.
Morbi dictum ligula gravida sem malesuada facilisis. Mauris nibh metus, cursus
eget imperdiet vitae, pretium at lorem. Praesent nisi mauris, pretium ut risus
fermentum, egestas tincidunt nibh. Mauris nulla orci, consequat eu pharetra
non, mattis ut urna. Mauris facilisis orci eros. Nam mattis non magna iaculis
consectetur. Morbi sodales dolor vitae felis sagittis, eget faucibus turpis
convallis. Nullam malesuada, mauris et ultricies rutrum, odio nulla gravida
nunc, ac volutpat eros lectus eget lacus. Integer venenatis velit vel justo
pellentesque, quis molestie sem vestibulum.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Citing articles in text \citet{Asgharzadeh2007} and with parenthesis
\citep{Braitenberg2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

Ut quis justo non leo malesuada molestie a ut eros. Vestibulum ante ipsum
primis in faucibus orci luctus et ultrices posuere cubilia Curae; Morbi eros
leo, elementum in dictum et, vulputate vel enim. Mauris pharetra lacinia augue
eget placerat. Sed id massa ut massa blandit convallis. Quisque vel dolor eu
nulla volutpat imperdiet. Nunc bibendum sem id elit accumsan, ac luctus leo
gravida. Proin cursus justo sem, vulputate hendrerit libero pulvinar in.
Suspendisse auctor sem at lorem pretium gravida. Vivamus aliquet cursus metus,
ac pellentesque nunc auctor vel. Cras quis nibh ullamcorper, vestibulum est et,
cursus ligula.

\begin{equation}
    \mbf{d}^{\alpha\beta} = \sum\limits_{j=1}^{M} p_j \mbf{a}_j^{\alpha\beta}.
    \label{eq:myeq}
\end{equation}

This is equation \ref{eq:myeq}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%\begin{figure}
    %\centering
    %\includegraphics[width=\columnwidth]{figures/figure}
    %\caption{This is a figure caption.}
    %\label{fig:myfig}
%\end{figure}

%This Figure \ref{fig:myfig}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Nunc euismod nunc nec lectus tempus, ultricies gravida quam rhoncus. Sed
posuere vestibulum nulla, ut accumsan justo venenatis a. Etiam consequat in leo
ac posuere. Fusce mattis ac sem non tempus. Aenean sollicitudin massa eu velit
consequat, sed congue metus tincidunt. Pellentesque posuere, urna a consequat
molestie, turpis libero rhoncus mi, lobortis accumsan nulla lectus at nunc.
Suspendisse fermentum augue vel ornare cursus. Suspendisse sit amet eros
facilisis, placerat nunc et, dapibus metus. Proin dolor enim, tempus at orci
non, pharetra varius justo.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

Maecenas eget turpis vitae lorem pharetra venenatis in sed eros. Pellentesque
orci lorem, egestas eu metus nec, hendrerit condimentum diam. Morbi quam neque,
dictum ac erat a, lacinia facilisis risus. Phasellus ligula quam, suscipit eu
congue ut, condimentum id leo. Donec convallis libero et aliquam mattis. Lorem
ipsum dolor sit amet, consectetur adipiscing elit. Morbi sed vestibulum neque.
Praesent nec nunc pellentesque, suscipit mi a, congue magna. Pellentesque et
libero vitae velit aliquet congue eget id lorem. Etiam dolor sapien, ultrices
vel neque vel, ultrices tempus quam. Nulla ultricies vehicula sagittis. Nunc
pulvinar eros lacus, sit amet viverra enim ultricies sed. Ut sagittis
pellentesque tristique. Proin facilisis tempor enim eu iaculis. In odio nulla,
facilisis non aliquet nec, facilisis non sapien. Sed auctor tincidunt mauris,
at pellentesque nisi lobortis a.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nam eu dolor pretium,
egestas mauris sed, dapibus quam. Duis hendrerit mollis nunc a consequat. Nulla
et sem consectetur, interdum velit eget, aliquam ipsum. Praesent sagittis
tortor diam, sed ultrices magna ullamcorper vitae. Proin vitae orci augue.
Morbi dictum ligula gravida sem malesuada facilisis. Mauris nibh metus, cursus
eget imperdiet vitae, pretium at lorem. Praesent nisi mauris, pretium ut risus
fermentum, egestas tincidunt nibh. Mauris nulla orci, consequat eu pharetra
non, mattis ut urna. Mauris facilisis orci eros. Nam mattis non magna iaculis
consectetur. Morbi sodales dolor vitae felis sagittis, eget faucibus turpis
convallis. Nullam malesuada, mauris et ultricies rutrum, odio nulla gravida
nunc, ac volutpat eros lectus eget lacus. Integer venenatis velit vel justo
pellentesque, quis molestie sem vestibulum.

\bibliographystyle{gji}
\bibliography{biblio}

\end{document}

### 2015-08-22 moho-inversion.tex
Paper section outlines and some notes

\documentclass[]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

\usepackage{todonotes}

% Document metadata
% =================
\newcommand{\Title}{
    Non-linear gravity inversion in spherical coordinates:
    application to the South American Moho
}
\newcommand{\Keywords}{
        Moho;
        gravity inversion;
        spherical coordinates;
        tesseroid;
        South America
}
\title{\Title}
\author{
    Leonardo Uieda \\ \texttt{leo@leouieda.com}
    \and
    Val\'eria C. F. Barbosa
}

\usepackage[pdftex,colorlinks=true,hidelinks]{hyperref}
\hypersetup{
    pdftitle={\Title},
    pdfauthor={Leonardo Uieda (leo@leouieda.com)},
    pdfsubject={},
    pdfkeywords={\Keywords},
    pdfcreator={pdfTeX}
}

\begin{document}

\maketitle

\noindent \textbf{Keywords:} \Keywords

\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

\subsection{Parametrization}

Remove the Normal Earth from observations to get disturbance.
Remove topography using Bouguer and correct crustal sources.
Leaves the relief of the Moho undulating around the Normal Earth Moho
(reference level).
Reference level is the Moho of the Normal Earth.

Assume all other sources were removed.
Only Moho topography around a reference level.
\todo{Include figure of Moho with all else  removed.}
Discretize into tesseroids.
Parameters are the Moho depths.
Establish that the reference level ($h_{ref}$)  and density contrast
($\Delta\rho_j$) are hyper-parameters.

\subsection{Inverse problem}

Formulate regularized inversion using Gauss-Newton and Steepest Descent.
Use full Jacobian.

\subsection{Bott's method}

Bott as Gauss-Newton.
Jacobian is diagonal.
Approximate the Jacobian by making tesseroid size tend to infinity to get
Bouguer slab.
This approximation is good for tesseroids because each will cover a large
enough area.
Show case for the Steepest Descent.
Extend the Jacobian to include lateral density variation.
Important because density-contrast is positive or negative depending if the
Moho is above or below the reference level.
Enforce that the use of a particular

Biggest computation time is in forward modeling.
All matrices involved are sparse.
Solve the sparse linear system with a conjugate gradient method.
\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
Use the regularized inversion because multiplying and solving the linear system
are fast compared to forward modeling.
Not using step size optimization because forward modeling is very slow so
increased convergence doesn't justify the extra time spent on the discarded
step attempts.

\subsection{Determination of hyper-parameters}

\subsection{Software implementation}

\todo{Cite packages in the references.txt file.}

\subsection{Satellite gravity data}

Explain where data came from and what was done to  it.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to synthetic data from a simple model}

%\begin{figure}
    %\centering
    %\includegraphics[width=\columnwidth]{figures/figure}
    %\caption{This is a figure caption.}
    %\label{fig:myfig}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to synthetic data from the CRUST1.0 model}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to the South American Moho}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}

\bibliographystyle{gji}
\bibliography{biblio}

\newpage
\listoftodos[Notes]

\end{document}

### 2015-08-23 moho-inversion.tex
Initial text for methodology, GJI style files

@@
-\documentclass[]{article}
-\usepackage{natbib}
+%\documentclass[]{article}
+%\usepackage{natbib}
+\documentclass[extra,mreferee]{gji}
+\usepackage{timet}
+\usepackage{amsmath}
 \usepackage{graphicx}
-\usepackage{amsmath}
+\usepackage[utf8]{inputenc}
 \newcommand{\mbf}[1]{\mathbf{{#1}}}
@@
 }
-\title{\Title}
-\author{
-    Leonardo Uieda \\ \texttt{leo@leouieda.com}
-    \and
-    Val\'eria C. F. Barbosa
+\title[]{\Title}
+\author[]{
+    Leonardo Uieda$^{1,2}$,
+    Valéria C. F. Barbosa$^{2}$
+    \\
+    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
+    e-mail: leo@leouieda.com
+    \\
+    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
 }
@@
 
+%\label{firstpage}
 \maketitle
@@
 
+We must first isolate the target anomalous density distribution.
+In our case, the target is the relief of the real Moho undulating around a
+reference Moho.
+We do this by removing all other effects from the gravity observations.
+The first correction is to remove the gravity\footnote{The term ``gravity''
+refers the sum of the gravitational and centripetal accelerations.}
+of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
+This is done using the formula presented in \citet{li_ellipsoid_2001}.
+The resulting quantity is known as the gravity disturbance,
+
+\begin{equation}
+    \delta g(P) = g(P) - \gamma(P)
+\end{equation}
+
+\noindent in which $g(P)$ is the measured gravity at an observation point $P$
+and $\gamma(P)$ is the gravity of the Normal Earth (the Normal Gravity)
+calculated on point $P$.
+
+We assume that the crust of our Normal Earth has a standard density of
+$\rho_{crust} = 2670\ kg.m^{-3}$ and depth $z_{ref}$.
+The disturbance contains only the gravitational effects of density
+distributions that are anomalous with respect to the Normal Earth.
+This includes all masses above the surface of the ellipsoid (the topography),
+the mass deficiency of the oceans,
+the mass deficiency of sedimentary basins,
+crustal sources (e.g., igneous intrusions, lateral density changes, etc),
+heterogeneities below the upper mantle,
+and
+the mass excesses and deficiencies caused by differences between the real Moho
+topography and the reference Moho ($z_{ref}$).
+The last is what we are interested in.
+All effects must either be removed or assumed negligible.
+The input data for the inversion is assumed to be the isolated gravitational
+effect of the anomalous Moho.
+
 \subsection{Parametrization}
-
-Remove the Normal Earth from observations to get disturbance.
-Remove topography using Bouguer and correct crustal sources.
-Leaves the relief of the Moho undulating around the Normal Earth Moho
-(reference level).
-Reference level is the Moho of the Normal Earth.
 
@@
 
+Meh.
+
 %\begin{figure}
@@
 
+Meh.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Application to the South American Moho}
+
+Meh.
 
@@
 
+Meh.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
+
+Meh.
 
@@
 
+Meh.
+
 \bibliographystyle{gji}
@@
 
-\newpage
-\listoftodos[Notes]
-
 \end{document}

### 2015-08-24 moho-inversion.tex
Add SAm data and sed model figures
A few more words in methods intro

@@
 %\usepackage{natbib}
-\documentclass[extra,mreferee]{gji}
+%\documentclass[extra,mreferee]{gji}
+\documentclass[extra]{gji}
 \usepackage{timet}
@@
 \usepackage{graphicx}
+\usepackage{url}
 \usepackage[utf8]{inputenc}
@@
 
+% Useful commands
+% ===============
+\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\figs}[2]{Figs.\ref{fig:#1}-\ref{fig:#2}}
+\newcommand{\subfig}[2]{Fig.~\ref{fig:#1}#2}
+\newcommand{\subfigs}[3]{Figs.\ref{fig:#1}#2-\ref{fig:#1}#3}
+\newcommand{\eq}[1]{Eq.~\ref{eq:#1}}
+\newcommand{\eqs}[2]{Eqs.~\ref{eq:#1}-\ref{eq:#2}}
+
 \begin{document}
@@
 
-\noindent \textbf{Keywords:} \Keywords
-
 \begin{abstract}
 \end{abstract}
+
+\noindent\textbf{Key words:} \Keywords
 
@@
 
-We must first isolate the target anomalous density distribution.
+In potential field methods,
+we must isolate the target anomalous density distribution prior to modeling and
+inversion.
 In our case, the target is the relief of the real Moho undulating around a
@@
 We do this by removing all other effects from the gravity observations.
-The first correction is to remove the gravity\footnote{The term ``gravity''
-refers the sum of the gravitational and centripetal accelerations.}
+The first correction is to remove the
+gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
+centripetal accelerations.}
 of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
-This is done using the formula presented in \citet{li_ellipsoid_2001}.
+This is done using the closed-form solution presented in \citet{li_ellipsoid_2001}.
 The resulting quantity is known as the gravity disturbance,
@@
 We assume that the crust of our Normal Earth has a standard density of
-$\rho_{crust} = 2670\ kg.m^{-3}$ and depth $z_{ref}$.
+$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
 The disturbance contains only the gravitational effects of density
@@
 topography and the reference Moho ($z_{ref}$).
-The last is what we are interested in.
-All effects must either be removed or assumed negligible.
-The input data for the inversion is assumed to be the isolated gravitational
-effect of the anomalous Moho.
+The latter is what we are interested in.
+In order to invert for the Moho topography, all effects must either be removed
+or assumed negligible.
+The gravitational effects of topography and sedimentary basins is
+removed using the models
+ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
+\citep{amante_c._and_b._w._eakins_etopo1_2009}
+and CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}}
+\citep{laske_update_2013}.
+Lateral variations in density along the Moho cannot be properly accounted for
+in regions where information coverage is sparse and readily accessible models
+are not available, like in the South American and African continents.
 
@@
 
-Assume all other sources were removed.
+We parameterize the forward problem by discretizing the Moho undulation around
+the reference depth into tesseroids.
+
 Only Moho topography around a reference level.
@@
 Use full Jacobian.
+Steepest has poor convergence when close to the solution
+\citep{kelley_iterative_1987}.
 
@@
 
-%\begin{figure}
-    %\centering
-    %\includegraphics[width=\columnwidth]{figures/figure}
-    %\caption{This is a figure caption.}
-    %\label{fig:myfig}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Meh.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
+    \caption{This is a figure caption.}
+    \label{fig:sam-data}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
+    \caption{This is a figure caption.}
+    \label{fig:sam-sed}
+\end{figure*}
+
+\fig{sam-data}, \figs{sam-data}{sam-sed}, \subfigs{sam-data}{a}{f}.
 

### 2015-08-24 moho-inversion.tex
Finish parametrization. Formulate gauss-newton.

@@
 \usepackage[utf8]{inputenc}
-\newcommand{\mbf}[1]{\mathbf{{#1}}}
 
@@
 
-\usepackage[pdftex,colorlinks=true,hidelinks]{hyperref}
+\usepackage[pdftex,colorlinks=true]{hyperref}
 \hypersetup{
@@
     pdfkeywords={\Keywords},
-    pdfcreator={pdfTeX}
+    pdfcreator={pdfTeX},
+    allcolors=blue,
 }
@@
 \newcommand{\eqs}[2]{Eqs.~\ref{eq:#1}-\ref{eq:#2}}
+
+%\newcommand{\mbf}[1]{\mathbf{{#1}}}
+\newcommand{\mbf}[1]{\hbox{\mathversion{bold}$#1$}}
 
@@
 
-We parameterize the forward problem by discretizing the Moho undulation around
-the reference depth into tesseroids.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/paper/tesseroid-coord-sys}
+    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
+        system (X, Y, Z).
+        Observations are made at point P with respect to it's local
+        North-oriented coordinate system (x, y, z).
+        After \citet{uieda_tesserioid_2015},
+        available at
+        \url{http://dx.doi.org/10.6084/m9.figshare.1495525}.
+    }
+    \label{fig:tess}
+\end{figure}
 
-Only Moho topography around a reference level.
-\todo{Include figure of Moho with all else  removed.}
-Discretize into tesseroids.
-Parameters are the Moho depths.
-Establish that the reference level ($h_{ref}$)  and density contrast
-($\Delta\rho_j$) are hyper-parameters.
+We parameterize the forward problem by discretizing the Moho undulation
+into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids (\fig{tess}).
+\todo{Cite source separation figure}
+In cases where the Moho is above the reference depth ($z_{ref}$),
+the top of the tesseroid is the Moho depth at the location of the $k$-eth
+tesseroid ($z_{k}$),
+the bottom is $z_{ref}$, and the density-contrast is positive.
+If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
+the bottom is the Moho depth, and the density-contrast is negative.
+
+Considering that the density-contrast of each tesseroid is fixed,
+the predicted gravity anomaly of the Moho is a non-linear function of the
+parameters $z_k$, $k=1, \ldots, M$,
+
+\begin{equation}
+    d_i = f_i(\mbf{p}),
+\end{equation}
+
+\noindent in which $d_i$ is the $i$th element of the predicted data vector
+$\mbf{d}$, $\mbf{p}$ is the parameter vector containing the Moho depths
+($z_k$),
+and
+$f_i$ is the $i$th non-linear function that maps the parameters onto the data.
 
@@
 
-Formulate regularized inversion using Gauss-Newton and Steepest Descent.
-Use full Jacobian.
+We wish to estimate the parameter vector $\mbf{p}$ from a set of observed
+gravity anomaly data $\mbf{d}^o$.
+The least-squares estimate is the one that minimizes the data-misfit function
+
+\begin{equation}
+    \phi(\mbf{p}) = \|\mbf{d}^o - \mbf{d}(\mbf{p})\|_2^2
+    = [\mbf{d}^o - \mbf{d}(\mbf{p})]^T[\mbf{d}^o - \mbf{d}(\mbf{p})].
+\end{equation}
+
+\noindent However, non-linear inversions for the relief of an interface (like
+the Moho) are ill-posed and required additional constraints in the form of
+regularization \citep{silva_potential-field_2001}.
+We will use the first-order Tikhonov regularization to impose smoothness on the
+solution,
+
+\begin{equation}
+    \theta(\mbf{p}) = \|\mbf{R}\mbf{p}\|^2_2
+    = \mbf{p}^T\mbf{R}^T\mbf{R}\mbf{p},
+\end{equation}
+
+\noindent where $\mbf{R}$ is an $L \times M$ finite-difference matrix
+representing the $L$ first-order differences between adjacent tesseroids.
+
+The solution $\hat{\mbf{p}}$ to the regularized inverse problem is the one that
+minimizes the goal function
+
+\begin{equation}
+    \Gamma(\mbf{p}) = \phi(\mbf{p}) + \mu\theta(\mbf{p}).
+\end{equation}
+
+\noindent $\Gamma(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
+Thus, we can find the minimum of the goal function using gradient-based
+iterative optimization
+methods like the Gauss-Newton method or the Steepest Descent method.
+Such methods start from an initial estimate $\mbf{p}^0$ and  repeatedly update
+the estimate.
+The update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
+for the Gauss-Newton method is
+
+\begin{equation}
+    \mbf{H}(\mbf{p}^k)\mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k),
+\end{equation}
+
+\noindent in which
+$\mbf{H}$ is the Hessian matrix of $\Gamma$,
+
+\begin{equation}
+    \mbf{H}(\mbf{p}^k) = 2\mbf{A}(\mbf{p}^k)^T\mbf{A}(\mbf{p}^k) +
+    2\mu\mbf{R}^T\mbf{R},
+\end{equation}
+
+\noindent
+$\mbf{\nabla}\Gamma$ is the gradient vector of $\Gamma$,
+
+\begin{equation}
+    \mbf{\nabla}\Gamma(\mbf{p}^k) = -2\mbf{A}(\mbf{p}^k)^T[\mbf{d}^o - \mbf{d}] +
+    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
+\end{equation}
+
+\noindent and
+$\mbf{A}$ is the Jacobian or sensitivity matrix,
+
+\begin{equation}
+    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p}).
+\end{equation}
+
 Steepest has poor convergence when close to the solution

### 2015-09-04 moho-inversion.tex
Reorganize inv formulation a bit

@@
 
-\noindent in which $d_i$ is the $i$th element of the predicted data vector
-$\mbf{d}$, $\mbf{p}$ is the parameter vector containing the Moho depths
-($z_k$),
-and
-$f_i$ is the $i$th non-linear function that maps the parameters onto the data.
+\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
+data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
+containing the Moho depths ($z_k$),
+and $f_i$ is the $i$th non-linear function that maps the parameters onto the
+data.
 
@@
 iterative optimization
-methods like the Gauss-Newton method or the Steepest Descent method.
+methods like the Gauss-Newton or Steepest Descent methods.
 Such methods start from an initial estimate $\mbf{p}^0$ and repeatedly update
-the estimate.
+the estimate until a minimum of the goal function is reached.
+
 The update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
-for the Gauss-Newton method is
+for Gauss-Newton method is
 
@@
 \noindent in which
-$\mbf{H}$ is the Hessian matrix of $\Gamma$,
+$\mbf{\nabla}\Gamma$ is the gradient vector and
+$\mbf{H}$ is the Hessian matrix of $\Gamma$.
+The gradient is given by
 
 \begin{equation}
-    \mbf{H}(\mbf{p}^k) = 2\mbf{A}(\mbf{p}^k)^T\mbf{A}(\mbf{p}^k) +
-    2\mu\mbf{R}^T\mbf{R},
+    \mbf{\nabla}\Gamma(\mbf{p}^k) =
+    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}] +
+    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
+    \label{eq:gradient}
+\end{equation}
+
+\noindent in which
+$\mbf{A}$ is the Jacobian or sensitivity matrix,
+
+\begin{equation}
+    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
 \end{equation}
@@
 \noindent
-$\mbf{\nabla}\Gamma$ is the gradient vector of $\Gamma$,
+In practice, the derivative above is often calculated through a first-order
+finite-difference approximation.
+
+The first term of \eq{gradient} is the gradient of the data-misfit
+function $\phi$ and the second term is the gradient of the regularizing
+function $\theta$.
+
+The Hessian matrix is given by
 
 \begin{equation}
-    \mbf{\nabla}\Gamma(\mbf{p}^k) = -2\mbf{A}(\mbf{p}^k)^T[\mbf{d}^o - \mbf{d}] +
-    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
+    \mbf{H}(\mbf{p}^k) = 2\mbf{A}^T\mbf{A} +
+    2\mu\mbf{R}^T\mbf{R}.
+    \label{eq:hessian}
 \end{equation}
 
-\noindent and
-$\mbf{A}$ is the Jacobian or sensitivity matrix,
+\noindent
+The first term of \eq{hessian} is the Gauss-Newton approximation of the Hessian
+matrix of $\phi$ and the second term is the Hessian of $\theta$.
+
+The Steepest Descent method uses only the gradient direction to
+update the initial estimate,
 
 \begin{equation}
-    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p}).
+    \mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k).
 \end{equation}
 
-Steepest has poor convergence when close to the solution
+\noindent
+Because of this, the Steepest Descent method has poor convergence when the
+current solution is close to the minimum of the goal function
 \citep{kelley_iterative_1987}.
+
+Both methods require the computationally expensive evaluation of the Jacobian
+matrix $\mbf{A}$.
+\todo{Talk a bit about why this is slow and difficult}
 

### 2015-10-04 moho-inversion.tex
Tweaks to initial methods section
Moved ETODO and CRUST correction references to real data application
section

@@
 \noindent in which $g(P)$ is the measured gravity at an observation point $P$
-and $\gamma(P)$ is the gravity of the Normal Earth (the Normal Gravity)
-calculated on point $P$.
+and $\gamma(P)$ is the gravity of the Normal Earth
+calculated at point $P$.
 
@@
 and
-the mass excesses and deficiencies caused by differences between the real Moho
+the effect of the difference between the real Moho
 topography and the reference Moho ($z_{ref}$).
-The latter is what we are interested in.
 In order to invert for the Moho topography, all effects must either be removed
 or assumed negligible.
-The gravitational effects of topography and sedimentary basins is
-removed using the models
-ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
-\citep{amante_c._and_b._w._eakins_etopo1_2009}
-and CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}}
-\citep{laske_update_2013}.
-Lateral variations in density along the Moho cannot be properly accounted for
-in regions where information coverage is sparse and readily accessible models
-are not available, like in the South American and African continents.
 
@@
 data.
+\todo{Say something about tesseroid forward modeling and cite paper.}
 
@@
 \begin{equation}
-    \mbf{H}(\mbf{p}^k)\mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k),
+    \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
 \end{equation}
@@
 \noindent in which
-$\mbf{\nabla}\Gamma$ is the gradient vector and
-$\mbf{H}$ is the Hessian matrix of $\Gamma$.
+$\mbf{\nabla}\Gamma^k$ is the gradient vector and
+$\mbf{H}^k$ is the Hessian matrix of $\Gamma$.
+
 The gradient is given by
@@
 \begin{equation}
-    \mbf{\nabla}\Gamma(\mbf{p}^k) =
-    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}] +
+    \mbf{\nabla}\Gamma^k =
+    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)] +
     2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
@@
     A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
+    \label{eq:jacobian}
 \end{equation}
@@
 \noindent
-In practice, the derivative above is often calculated through a first-order
-finite-difference approximation.
-
 The first term of \eq{gradient} is the gradient of the data-misfit
@@
 \begin{equation}
-    \mbf{H}(\mbf{p}^k) = 2\mbf{A}^T\mbf{A} +
+    \mbf{H}^k = 2\mbf{A}^T\mbf{A} +
     2\mu\mbf{R}^T\mbf{R}.
@@
 \begin{equation}
-    \mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k).
+    \mbf{\Delta p} = -\mbf{\nabla}\Gamma^k.
 \end{equation}
@@
 matrix $\mbf{A}$.
-\todo{Talk a bit about why this is slow and difficult}
+In practice, the derivative in \eq{jacobian} is often calculated through a
+first-order finite-difference approximation.
+Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
+operations for each iteration of the gradient descent algorithm.
+When using tesseroids, forward modeling requires several trigonometric function
+evaluations as well as adaptive discretization.
+\todo{Cite forward modeling paper}
+Both factor contribute significantly to the total computation time.
 
@@
 
-\subsection{Satellite gravity data}
-
-Explain where data came from and what was done to  it.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Application to the South American Moho}
+
+\subsection{Gravity data}
+
+The gravitational effect of the topography
+is removed using the
+ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
+digital terrain model
+\citep{amante_c._and_b._w._eakins_etopo1_2009}.
+The effect of sedimentary basins is removed using the
+CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}} model
+by
+\citet{laske_update_2013}.
+Lateral variations in density along the Moho cannot be properly accounted for
+in regions where information coverage is sparse and readily accessible models
+are not available, like in the South American and African continents.
+For the purposes of this study, we will assume that all other crustal sources
+and lateral variations in density are negligible.
 
@@
 \fig{sam-data}, \figs{sam-data}{sam-sed}, \subfigs{sam-data}{a}{f}.
+
+\subsection{Inversion results}
 

### 2015-10-13 moho-inversion.tex
Small methods tweaks

@@
 of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
-This is done using the closed-form solution presented in \citet{li_ellipsoid_2001}.
+This is done using the closed-form solution presented in
+\citet{li_ellipsoid_2001}.
+\todo{Needs review}
 The resulting quantity is known as the gravity disturbance,
@@
 \begin{equation}
-    \delta g(P) = g(P) - \gamma(P)
+    \delta(P) = g(P) - \gamma(P)
 \end{equation}
@@
 data.
-\todo{Say something about tesseroid forward modeling and cite paper.}
+$f_i$ is the radial component of the gravitational attraction of the tesseroid
+model.
+The gravitational attraction of a tesseroid is calculated using the
+Gauss-Legendre Quadrature (GLQ) integration.
+The accuracy of the GLQ integration is improved by an adaptive discretization
+scheme.
+\todo{Cite tesseroids paper.}
 
@@
 operations for each iteration of the gradient descent algorithm.
-When using tesseroids, forward modeling requires several trigonometric function
-evaluations as well as adaptive discretization.
+Forward modeling using tesseroids requires several trigonometric function
+evaluations and numerical integration.
 \todo{Cite forward modeling paper}
-Both factor contribute significantly to the total computation time.
+Both factors contribute significantly to the total computation time required to
+evaluate $\mbf{A}$.
 

### 2015-10-13 moho-inversion.tex
Initial text to botts method

@@
     \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
+    \label{eq:gaussnewton}
 \end{equation}
@@
 \subsection{Bott's method}
+
+\citet{bott_use_1960} developed an efficient method to determined the basement
+relief of a sedimentary basin from gravity observations.
+The method requires data on a regular grid of $N_x \times N_y = N$
+observations.
+The method discretizes the basement relief into an equal grid of $N_x \times
+N_y$ elements.
+The method starts with an initial estimate of the basement relief
+$\mbf{p}^0$ equal to the null vector and updates the estimate using the formula
+
+\begin{equation}
+    \mbf{\Delta p} = \dfrac{\mbf{d}^o - \mbf{d}(\mbf{p}^k)}{2\pi G \Delta \rho},
+    \label{eq:bott}
+\end{equation}
+
+\noindent
+in which $G$ is the gravitational constant and $\Delta \rho$ is the basin
+density contrast.
+The iterative process stops when the inversion residuals
+$\mbf{r} = \mbf{d}^o - \mbf{d}(\mbf{p}^k)$ fall below the assumed noise level
+of the data.
+
+\citet{silva_fast_2014} showed that Bott's method can be formulated as
+the Gauss-Newton method (\eq{gaussnewton})
+by setting the Jacobian matrix to
+
+\begin{equation}
+    \mbf{A} = 2\pi G \Delta \rho \mbf{I},
+    \label{eq:bott-jacobian}
+\end{equation}
+
+\noindent
+in which $\mbf{I}$ is the identity matrix.
+In this framework, Bott's method uses a Bouguer plate approximation to
+linearize the Jacobian matrix.
+Bott's method maintains the non-linearity of the predicted data
+$\mbf{d}(\mbf{p}^k)$.
+
+Bott's method can also be formulated as the Steepest Descent method
+(\eq{steepest}) by setting the Jacobian matrix to
+
+\begin{equation}
+    \mbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mbf{I}.
+    \label{eq:bott-steepest}
+\end{equation}
 

### 2015-10-13 moho-inversion.tex
Separate the equations for regularized inversion
This makes it easier to tie into bott's method

@@
 \begin{equation}
-    \phi(\mbf{p}) = \|\mbf{d}^o - \mbf{d}(\mbf{p})\|_2^2
-    = [\mbf{d}^o - \mbf{d}(\mbf{p})]^T[\mbf{d}^o - \mbf{d}(\mbf{p})].
+    \phi(\mbf{p}) =
+    [\mbf{d}^o - \mbf{d}(\mbf{p})]^T[\mbf{d}^o - \mbf{d}(\mbf{p})].
+    \label{eq:data-misfit}
 \end{equation}
 
-\noindent However, non-linear inversions for the relief of an interface (like
+Function $\phi(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
+Thus, we can find its minimum using gradient-based
+iterative optimization
+methods like the Gauss-Newton or Steepest Descent methods.
+Such methods start from an initial estimate $\mbf{p}^0$ and repeatedly update
+the estimate until a minimum is reached.
+
+For the Gauss-Newton method,
+the update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
+is the solution of the linear system
+
+\begin{equation}
+    \mbf{H}^k\mbf{\Delta p} = -\mbf{g}^k,
+    \label{eq:gaussnewton}
+\end{equation}
+
+\noindent in which
+$\mbf{g}^k$ and $\mbf{H}^k$ are, respectively,
+the gradient vector and the Hessian matrix of $\phi(\mbf{p})$.
+
+The Steepest Descent method uses only the gradient direction
+to update the initial estimate
+
+\begin{equation}
+    \mbf{\Delta p} = -\mbf{g}^k.
+    \label{eq:steepest}
+\end{equation}
+
+\noindent
+Thus, it does not require the computation and storage of the Hessian matrix
+nor the solution of linear systems.
+However, the Steepest Descent method has poor convergence when the
+current solution is close to the minimum of the goal function
+\citep{kelley_iterative_1987}.
+
+The gradient vector and the Gauss-Newton approximation of the Hessian matrix
+of $\phi(\mbf{p})$ are, respectively,
+
+\begin{equation}
+    \mbf{g}^k = -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)],
+    \label{eq:gradient}
+\end{equation}
+
+\noindent
+and
+
+\begin{equation}
+    \mbf{H}^k = 2\mbf{A}^T\mbf{A},
+    \label{eq:hessian}
+\end{equation}
+
+\noindent in which
+$\mbf{A}$ is the Jacobian or sensitivity matrix,
+
+\begin{equation}
+    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
+    \label{eq:jacobian}
+\end{equation}
+
+The computation and storage of the dense matrix $\mbf{A}$ is time consuming
+and is often times the bottleneck of an inversion algorithm.
+In practice, the derivative in \eq{jacobian} is often calculated through a
+first-order finite-difference approximation.
+Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
+operations for each iteration of the gradient descent algorithm.
+Forward modeling using tesseroids requires several trigonometric function
+evaluations and numerical integration.
+\todo{Cite forward modeling paper}
+Both factors contribute significantly to the total computation time required to
+evaluate $\mbf{A}$.
+
+\subsection{Regularization}
+
+Non-linear inversions for the relief of an interface (like
 the Moho) are ill-posed and required additional constraints in the form of
 regularization \citep{silva_potential-field_2001}.
-We will use the first-order Tikhonov regularization to impose smoothness on the
-solution,
+A common approach is to use the first-order Tikhonov regularization to impose
+smoothness on the solution,
 
 \begin{equation}
-    \theta(\mbf{p}) = \|\mbf{R}\mbf{p}\|^2_2
-    = \mbf{p}^T\mbf{R}^T\mbf{R}\mbf{p},
+    \theta(\mbf{p}) = \mbf{p}^T\mbf{R}^T\mbf{R}\mbf{p},
 \end{equation}
@@
 
-\noindent $\Gamma(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
-Thus, we can find the minimum of the goal function using gradient-based
-iterative optimization
-methods like the Gauss-Newton or Steepest Descent methods.
-Such methods start from an initial estimate $\mbf{p}^0$ and repeatedly update
-the estimate until a minimum of the goal function is reached.
+\noindent
+The regularization parameter $\mu$ controls the balance between fitting the
+observed data and obeying the smoothness constraint.
 
-The update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
-for Gauss-Newton method is
+The goal function $\Gamma(\mbf{p})$ is also non-linear with respect to
+$\mbf{p}$ and can be minimized using the Gauss-Newton or Steepest Descent
+methods.
+The gradient vector and Hessian matrix of the goal function are, respectively,
 
 \begin{equation}
-    \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
-    \label{eq:gaussnewton}
+    \mbf{g}^k =
+        -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)] +
+        2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
+    \label{eq:gradient-regul}
 \end{equation}
 
-\noindent in which
-$\mbf{\nabla}\Gamma^k$ is the gradient vector and
-$\mbf{H}^k$ is the Hessian matrix of $\Gamma$.
-
-The gradient is given by
+\noindent and
 
 \begin{equation}
-    \mbf{\nabla}\Gamma^k =
-    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)] +
-    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
-    \label{eq:gradient}
+    \mbf{H}^k = 2\mbf{A}^T\mbf{A} + 2\mu\mbf{R}^T\mbf{R}.
+    \label{eq:hessian-regul}
 \end{equation}
-
-\noindent in which
-$\mbf{A}$ is the Jacobian or sensitivity matrix,
-
-\begin{equation}
-    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
-    \label{eq:jacobian}
-\end{equation}
-
-\noindent
-The first term of \eq{gradient} is the gradient of the data-misfit
-function $\phi$ and the second term is the gradient of the regularizing
-function $\theta$.
-
-The Hessian matrix is given by
-
-\begin{equation}
-    \mbf{H}^k = 2\mbf{A}^T\mbf{A} +
-    2\mu\mbf{R}^T\mbf{R}.
-    \label{eq:hessian}
-\end{equation}
-
-\noindent
-The first term of \eq{hessian} is the Gauss-Newton approximation of the Hessian
-matrix of $\phi$ and the second term is the Hessian of $\theta$.
-
-The Steepest Descent method uses only the gradient direction to
-update the initial estimate,
-
-\begin{equation}
-    \mbf{\Delta p} = -\mbf{\nabla}\Gamma^k.
-\end{equation}
-
-\noindent
-Because of this, the Steepest Descent method has poor convergence when the
-current solution is close to the minimum of the goal function
-\citep{kelley_iterative_1987}.
-
-Both methods require the computationally expensive evaluation of the Jacobian
-matrix $\mbf{A}$.
-In practice, the derivative in \eq{jacobian} is often calculated through a
-first-order finite-difference approximation.
-Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
-operations for each iteration of the gradient descent algorithm.
-Forward modeling using tesseroids requires several trigonometric function
-evaluations and numerical integration.
-\todo{Cite forward modeling paper}
-Both factors contribute significantly to the total computation time required to
-evaluate $\mbf{A}$.
 

### 2015-10-13 moho-inversion.tex
Talk ab problems with A in Bott's method section

@@
 
-The computation and storage of the dense matrix $\mbf{A}$ is time consuming
-and is often times the bottleneck of an inversion algorithm.
-In practice, the derivative in \eq{jacobian} is often calculated through a
-first-order finite-difference approximation.
-Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
-operations for each iteration of the gradient descent algorithm.
-Forward modeling using tesseroids requires several trigonometric function
-evaluations and numerical integration.
-\todo{Cite forward modeling paper}
-Both factors contribute significantly to the total computation time required to
-evaluate $\mbf{A}$.
-
 \subsection{Regularization}
@@
 observations.
-The method discretizes the basement relief into an equal grid of $N_x \times
-N_y$ elements.
-The method starts with an initial estimate of the basement relief
+The basement relief is then discretized into an equal grid of $M_x \times
+M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
+Bott's iterative method starts with an initial estimate of the basement relief
 $\mbf{p}^0$ equal to the null vector and updates the estimate using the formula
@@
 \citet{silva_fast_2014} showed that Bott's method can be formulated as
-the Gauss-Newton method (\eq{gaussnewton})
-by setting the Jacobian matrix to
+a special case of the Gauss-Newton method (\eq{gaussnewton})
+by setting the Jacobian matrix (\eq{jacobian}) to
 
@@
 in which $\mbf{I}$ is the identity matrix.
-In this framework, Bott's method uses a Bouguer plate approximation to
+In this framework,
+Bott's method uses a Bouguer plate approximation of the relief to
 linearize the Jacobian matrix.
-Bott's method maintains the non-linearity of the predicted data
-$\mbf{d}(\mbf{p}^k)$.
+However, the non-linearity of the predicted data $\mbf{d}(\mbf{p}^k)$ is
+preserved.
 
-Bott's method can also be formulated as the Steepest Descent method
-(\eq{steepest}) by setting the Jacobian matrix to
+We propose that Bott's method can also be formulated as a special case of the
+Steepest Descent method (\eq{steepest}) by setting the Jacobian matrix to
 
@@
 
-Bott as Gauss-Newton.
-Jacobian is diagonal.
+One of the advantages of Bott's method over the traditional Gauss-Newton or
+Steepest Descent is eliminating the computation and storage of the dense
+Jacobian matrix $\mbf{A}$.
+In practice, the derivatives in \eq{jacobian} are often calculated through a
+first-order finite-difference approximation.
+Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
+operations for each iteration of the gradient descent algorithm.
+Bott's method also does not require the solution of equation systems.
+
+A disadvantage of Bott's method is that it suffers from instability
+\citep{silva_fast_2014}.
+A common approach to solve this issue is to apply a smoothing filter, like a
+moving average, to the unstable estimate.
+
+\subsection{Regularized Bott's method in spherical coordinates}
+
 Approximate the Jacobian by making tesseroid size tend to infinity to get

### 2015-11-01 manuscript.tex
Make  paper in manuscript  style
Remove special latex commands to simplify later

--- 2015-10-13 moho-inversion.tex
@@
 %\usepackage{natbib}
-%\documentclass[extra,mreferee]{gji}
-\documentclass[extra]{gji}
+\documentclass[extra,mreferee]{gji}
+%\documentclass[extra]{gji}
 \usepackage{timet}
@@
 % ===============
-\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
-\newcommand{\figs}[2]{Figs.\ref{fig:#1}-\ref{fig:#2}}
-\newcommand{\subfig}[2]{Fig.~\ref{fig:#1}#2}
-\newcommand{\subfigs}[3]{Figs.\ref{fig:#1}#2-\ref{fig:#1}#3}
-\newcommand{\eq}[1]{Eq.~\ref{eq:#1}}
-\newcommand{\eqs}[2]{Eqs.~\ref{eq:#1}-\ref{eq:#2}}
-
-%\newcommand{\mbf}[1]{\mathbf{{#1}}}
-\newcommand{\mbf}[1]{\hbox{\mathversion{bold}$#1$}}
 
@@
 We parameterize the forward problem by discretizing the Moho undulation
-into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids (\fig{tess}).
+into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids (Fig.~\ref{fig:tess}).
 \todo{Cite source separation figure}
@@
 \begin{equation}
-    d_i = f_i(\mbf{p}),
+    d_i = f_i(\mathbf{p}),
 \end{equation}
@@
 \noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
-data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
+data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
 containing the Moho depths ($z_k$),
@@
 
-We wish to estimate the parameter vector $\mbf{p}$ from a set of observed
-gravity anomaly data $\mbf{d}^o$.
+We wish to estimate the parameter vector $\mathbf{p}$ from a set of observed
+gravity anomaly data $\mathbf{d}^o$.
 The least-squares estimate is the one that minimizes the data-misfit function
@@
 \begin{equation}
-    \phi(\mbf{p}) =
-    [\mbf{d}^o - \mbf{d}(\mbf{p})]^T[\mbf{d}^o - \mbf{d}(\mbf{p})].
+    \phi(\mathbf{p}) =
+    [\mathbf{d}^o - \mathbf{d}(\mathbf{p})]^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p})].
     \label{eq:data-misfit}
@@
 
-Function $\phi(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
+Function $\phi(\mathbf{p})$ is non-linear with respect to $\mathbf{p}$.
 Thus, we can find its minimum using gradient-based
@@
 methods like the Gauss-Newton or Steepest Descent methods.
-Such methods start from an initial estimate $\mbf{p}^0$ and repeatedly update
+Such methods start from an initial estimate $\mathbf{p}^0$ and repeatedly update
 the estimate until a minimum is reached.
@@
 For the Gauss-Newton method,
-the update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
+the update at the $k$th iteration $\mathbf{\Delta p} = \mathbf{p}^{k+1} - \mathbf{p}^k$
 is the solution of the linear system
@@
 \begin{equation}
-    \mbf{H}^k\mbf{\Delta p} = -\mbf{g}^k,
+    \mathbf{H}^k\mathbf{\Delta p} = -\mathbf{g}^k,
     \label{eq:gaussnewton}
@@
 \noindent in which
-$\mbf{g}^k$ and $\mbf{H}^k$ are, respectively,
-the gradient vector and the Hessian matrix of $\phi(\mbf{p})$.
+$\mathbf{g}^k$ and $\mathbf{H}^k$ are, respectively,
+the gradient vector and the Hessian matrix of $\phi(\mathbf{p})$.
 
@@
 \begin{equation}
-    \mbf{\Delta p} = -\mbf{g}^k.
+    \mathbf{\Delta p} = -\mathbf{g}^k.
     \label{eq:steepest}
@@
 The gradient vector and the Gauss-Newton approximation of the Hessian matrix
-of $\phi(\mbf{p})$ are, respectively,
+of $\phi(\mathbf{p})$ are, respectively,
 
 \begin{equation}
-    \mbf{g}^k = -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)],
+    \mathbf{g}^k = -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)],
     \label{eq:gradient}
@@
 \begin{equation}
-    \mbf{H}^k = 2\mbf{A}^T\mbf{A},
+    \mathbf{H}^k = 2\mathbf{A}^T\mathbf{A},
     \label{eq:hessian}
@@
 \noindent in which
-$\mbf{A}$ is the Jacobian or sensitivity matrix,
+$\mathbf{A}$ is the Jacobian or sensitivity matrix,
 
 \begin{equation}
-    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
+    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mathbf{p^k}).
     \label{eq:jacobian}
@@
 \begin{equation}
-    \theta(\mbf{p}) = \mbf{p}^T\mbf{R}^T\mbf{R}\mbf{p},
+    \theta(\mathbf{p}) = \mathbf{p}^T\mathbf{R}^T\mathbf{R}\mathbf{p},
 \end{equation}
 
-\noindent where $\mbf{R}$ is an $L \times M$ finite-difference matrix
+\noindent where $\mathbf{R}$ is an $L \times M$ finite-difference matrix
 representing the $L$ first-order differences between adjacent tesseroids.
 
-The solution $\hat{\mbf{p}}$ to the regularized inverse problem is the one that
+The solution $\hat{\mathbf{p}}$ to the regularized inverse problem is the one that
 minimizes the goal function
@@
 \begin{equation}
-    \Gamma(\mbf{p}) = \phi(\mbf{p}) + \mu\theta(\mbf{p}).
+    \Gamma(\mathbf{p}) = \phi(\mathbf{p}) + \mu\theta(\mathbf{p}).
 \end{equation}
@@
 
-The goal function $\Gamma(\mbf{p})$ is also non-linear with respect to
-$\mbf{p}$ and can be minimized using the Gauss-Newton or Steepest Descent
+The goal function $\Gamma(\mathbf{p})$ is also non-linear with respect to
+$\mathbf{p}$ and can be minimized using the Gauss-Newton or Steepest Descent
 methods.
@@
 \begin{equation}
-    \mbf{g}^k =
-        -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)] +
-        2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
+    \mathbf{g}^k =
+        -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] +
+        2\mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
     \label{eq:gradient-regul}
@@
 \begin{equation}
-    \mbf{H}^k = 2\mbf{A}^T\mbf{A} + 2\mu\mbf{R}^T\mbf{R}.
+    \mathbf{H}^k = 2\mathbf{A}^T\mathbf{A} + 2\mu\mathbf{R}^T\mathbf{R}.
     \label{eq:hessian-regul}
@@
 Bott's iterative method starts with an initial estimate of the basement relief
-$\mbf{p}^0$ equal to the null vector and updates the estimate using the formula
+$\mathbf{p}^0$ equal to the null vector and updates the estimate using the formula
 
 \begin{equation}
-    \mbf{\Delta p} = \dfrac{\mbf{d}^o - \mbf{d}(\mbf{p}^k)}{2\pi G \Delta \rho},
+    \mathbf{\Delta p} = \dfrac{\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)}{2\pi G \Delta \rho},
     \label{eq:bott}
@@
 The iterative process stops when the inversion residuals
-$\mbf{r} = \mbf{d}^o - \mbf{d}(\mbf{p}^k)$ fall below the assumed noise level
+$\mathbf{r} = \mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)$ fall below the assumed noise level
 of the data.
@@
 \citet{silva_fast_2014} showed that Bott's method can be formulated as
-a special case of the Gauss-Newton method (\eq{gaussnewton})
-by setting the Jacobian matrix (\eq{jacobian}) to
+a special case of the Gauss-Newton method (Eq.~\ref{eq:gaussnewton})
+by setting the Jacobian matrix (Eq.~\ref{eq:jacobian}) to
 
 \begin{equation}
-    \mbf{A} = 2\pi G \Delta \rho \mbf{I},
+    \mathbf{A} = 2\pi G \Delta \rho \mathbf{I},
     \label{eq:bott-jacobian}
@@
 \noindent
-in which $\mbf{I}$ is the identity matrix.
+in which $\mathbf{I}$ is the identity matrix.
 In this framework,
@@
 linearize the Jacobian matrix.
-However, the non-linearity of the predicted data $\mbf{d}(\mbf{p}^k)$ is
+However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
 preserved.
@@
 We propose that Bott's method can also be formulated as a special case of the
-Steepest Descent method (\eq{steepest}) by setting the Jacobian matrix to
+Steepest Descent method (Eq.~\ref{eq:steepest}) by setting the Jacobian matrix to
 
 \begin{equation}
-    \mbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mbf{I}.
+    \mathbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mathbf{I}.
     \label{eq:bott-steepest}
@@
 Steepest Descent is eliminating the computation and storage of the dense
-Jacobian matrix $\mbf{A}$.
-In practice, the derivatives in \eq{jacobian} are often calculated through a
+Jacobian matrix $\mathbf{A}$.
+In practice, the derivatives in Eq.~\ref{eq:jacobian} are often calculated through a
 first-order finite-difference approximation.
-Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
+Thus, evaluating $\mathbf{A}$ requires $2\times M \times N$ forward modeling
 operations for each iteration of the gradient descent algorithm.
@@
 
-\fig{sam-data}, \figs{sam-data}{sam-sed}, \subfigs{sam-data}{a}{f}.
-
 \subsection{Inversion results}

### 2015-11-01 manuscript.tex
Simpler bibtex keys and restructure methods intro

@@
 The first correction is to remove the
-gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
-centripetal accelerations.}
-of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
-This is done using the closed-form solution presented in
-\citet{li_ellipsoid_2001}.
-\todo{Needs review}
-The resulting quantity is known as the gravity disturbance,
+scalar gravity of an ellipsoidal reference Earth (the Normal Earth),
+hereafter denoted as $\gamma$.
+This effect is calculated on the same point $P$ where the observation was made
+using the closed-form solution presented by \citet{li_2001}.
+The difference between the observed gravity ($g$) and Normal gravity
+is known as the gravity disturbance,
 
 \begin{equation}
-    \delta(P) = g(P) - \gamma(P)
+    \delta(P) = g(P) - \gamma(P).
 \end{equation}
 
-\noindent in which $g(P)$ is the measured gravity at an observation point $P$
-and $\gamma(P)$ is the gravity of the Normal Earth
-calculated at point $P$.
-
-We assume that the crust of our Normal Earth has a standard density of
-$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
 The disturbance contains only the gravitational effects of density
@@
 heterogeneities below the upper mantle,
-and
-the effect of the difference between the real Moho
-topography and the reference Moho ($z_{ref}$).
-In order to invert for the Moho topography, all effects must either be removed
-or assumed negligible.
+and the effect of the difference between the real Moho
+topography and the Moho of the Normal Earth.
+
+All effects must either be removed or assumed negligible
+to invert for the anomalous Moho.
+The gravitational attraction of the topography, oceans, and basins are
+calculated in a spherical Earth approximation by forward modeling using
+tesseroids
+(Fig.~\ref{fig:tesseroid}).
+The tesseroid effects are calculated numerically using
+Gauss-Legendre Quadrature (GLQ) integration \citep{asgharzadeh_2007}.
+The accuracy of the GLQ integration is improved by the adaptive discretization
+scheme of \citet{uieda_2016}.
 
@@
         North-oriented coordinate system (x, y, z).
-        After \citet{uieda_tesserioid_2015},
+        After \citet{uieda_2015},
         available at
@@
     }
-    \label{fig:tess}
+    \label{fig:tesseroid}
 \end{figure}
@@
 We parameterize the forward problem by discretizing the Moho undulation
-into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids (Fig.~\ref{fig:tess}).
-\todo{Cite source separation figure}
+into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids
+(Fig.~\ref{fig:tesseroid}).
 In cases where the Moho is above the reference depth ($z_{ref}$),
@@
 $f_i$ is the radial component of the gravitational attraction of the tesseroid
-model.
-The gravitational attraction of a tesseroid is calculated using the
-Gauss-Legendre Quadrature (GLQ) integration.
-The accuracy of the GLQ integration is improved by an adaptive discretization
-scheme.
-\todo{Cite tesseroids paper.}
+model of the anomalous Moho.
 
@@
 current solution is close to the minimum of the goal function
-\citep{kelley_iterative_1987}.
+\citep{kelley_1987}.
 
@@
 the Moho) are ill-posed and required additional constraints in the form of
-regularization \citep{silva_potential-field_2001}.
+regularization \citep{silva_2001}.
 A common approach is to use the first-order Tikhonov regularization to impose
@@
 
-\citet{bott_use_1960} developed an efficient method to determined the basement
+\citet{bott_1960} developed an efficient method to determined the basement
 relief of a sedimentary basin from gravity observations.
@@
 
-\citet{silva_fast_2014} showed that Bott's method can be formulated as
+\citet{silva_2014} showed that Bott's method can be formulated as
 a special case of the Gauss-Newton method (Eq.~\ref{eq:gaussnewton})
@@
 A disadvantage of Bott's method is that it suffers from instability
-\citep{silva_fast_2014}.
+\citep{silva_2014}.
 A common approach to solve this issue is to apply a smoothing filter, like a
@@
 digital terrain model
-\citep{amante_c._and_b._w._eakins_etopo1_2009}.
+\citep{amante_2009}.
 The effect of sedimentary basins is removed using the
@@
 by
-\citet{laske_update_2013}.
+\citet{laske_2013}.
 Lateral variations in density along the Moho cannot be properly accounted for

### 2015-11-01 manuscript.tex
Tweaks to parametrization

@@
 is known as the gravity disturbance,
+\todo{Figura do seminário acompanha}
 
@@
 
-\subsection{Parametrization}
-
 \begin{figure}
@@
 
+\subsection{Parametrization}
+
 We parameterize the forward problem by discretizing the Moho undulation
-into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids
-(Fig.~\ref{fig:tesseroid}).
+into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids.
 In cases where the Moho is above the reference depth ($z_{ref}$),
@@
 the bottom is the Moho depth, and the density-contrast is negative.
+\todo{Figura do seminário}
 
@@
 data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
-containing the Moho depths ($z_k$),
+containing the $M$ Moho depths ($z_k$),
 and $f_i$ is the $i$th non-linear function that maps the parameters onto the
 data.
-$f_i$ is the radial component of the gravitational attraction of the tesseroid
-model of the anomalous Moho.
+The functions $f_i$ are the radial component of the gravitational attraction
+of the tesseroid Moho model.
 

### 2015-11-01 manuscript.tex
Add "Fast" to title

@@
 \newcommand{\Title}{
-    Non-linear gravity inversion in spherical coordinates:
+    Fast non-linear gravity inversion in spherical coordinates:
     application to the South American Moho
@@
     $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
-    e-mail: leo@leouieda.com
+    e-mail: leouieda@gmail.com
     \\
@@
     pdftitle={\Title},
-    pdfauthor={Leonardo Uieda (leo@leouieda.com)},
+    pdfauthor={Leonardo Uieda (leouieda@gmail.com)},
     pdfsubject={},

### 2015-11-02 manuscript.tex
Tweaks to inverse problem and bibtex keys without _

@@
 This effect is calculated on the same point $P$ where the observation was made
-using the closed-form solution presented by \citet{li_2001}.
+using the closed-form solution presented by \citet{li2001}.
 The difference between the observed gravity ($g$) and Normal gravity
@@
 The tesseroid effects are calculated numerically using
-Gauss-Legendre Quadrature (GLQ) integration \citep{asgharzadeh_2007}.
+Gauss-Legendre Quadrature (GLQ) integration \citep{asgharzadeh2007}.
 The accuracy of the GLQ integration is improved by the adaptive discretization
-scheme of \citet{uieda_2016}.
+scheme of \citet{uieda2016}.
 
@@
         North-oriented coordinate system (x, y, z).
-        After \citet{uieda_2015},
+        After \citet{uieda2015},
         available at
@@
 Function $\phi(\mathbf{p})$ is non-linear with respect to $\mathbf{p}$.
-Thus, we can find its minimum using gradient-based
+Thus, we can determine its minimum using gradient-based
 iterative optimization
-methods like the Gauss-Newton or Steepest Descent methods.
-Such methods start from an initial estimate $\mathbf{p}^0$ and repeatedly update
-the estimate until a minimum is reached.
+methods like Gauss-Newton or Steepest Descent.
+Such methods start from an initial estimate $\mathbf{p}^0$ and repeatedly
+update the estimate until a minimum is reached.
 
 For the Gauss-Newton method,
-the update at the $k$th iteration $\mathbf{\Delta p} = \mathbf{p}^{k+1} - \mathbf{p}^k$
+the update at the $k$th iteration,
+$\mathbf{\Delta p} = \mathbf{p}^{k+1} - \mathbf{p}^k$,
 is the solution of the linear system
@@
 \begin{equation}
-    \mathbf{H}^k\mathbf{\Delta p} = -\mathbf{g}^k,
+    \mathbf{H}^k\mathbf{\Delta p} = -\mathbf{\nabla\phi}^k,
     \label{eq:gaussnewton}
@@
 \noindent in which
-$\mathbf{g}^k$ and $\mathbf{H}^k$ are, respectively,
+$\mathbf{\nabla\phi}^k$ and $\mathbf{H}^k$ are, respectively,
 the gradient vector and the Hessian matrix of $\phi(\mathbf{p})$.
@@
 The Steepest Descent method uses only the gradient direction
-to update the initial estimate
+to update the initial estimate \citep{kelley1987}.
+The update at the $k$th iteration is achieved by equating the Hessian
+in Eq.~\ref{eq:gaussnewton} to the identity matrix,
 
 \begin{equation}
-    \mathbf{\Delta p} = -\mathbf{g}^k.
+    \mathbf{\Delta p} = -\mathbf{\nabla\phi}^k.
     \label{eq:steepest}
@@
 current solution is close to the minimum of the goal function
-\citep{kelley_1987}.
+\citep{kelley1987}.
 
@@
 \begin{equation}
-    \mathbf{g}^k = -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)],
+    \mathbf{\nabla\phi}^k = -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)],
     \label{eq:gradient}
@@
 \begin{equation}
-    \mathbf{H}^k = 2\mathbf{A}^T\mathbf{A},
+    \mathbf{H}^k \approx 2\mathbf{A}^T\mathbf{A},
     \label{eq:hessian}
@@
 the Moho) are ill-posed and required additional constraints in the form of
-regularization \citep{silva_2001}.
+regularization \citep{silva2001}.
 A common approach is to use the first-order Tikhonov regularization to impose
@@
 \begin{equation}
-    \mathbf{g}^k =
+    \mathbf{\nabla\Gamma}^k =
         -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] +
@@
 
-\citet{bott_1960} developed an efficient method to determined the basement
+\citet{bott1960} developed an efficient method to determined the basement
 relief of a sedimentary basin from gravity observations.
@@
 
-\citet{silva_2014} showed that Bott's method can be formulated as
+\citet{silva2014} showed that Bott's method can be formulated as
 a special case of the Gauss-Newton method (Eq.~\ref{eq:gaussnewton})
@@
 A disadvantage of Bott's method is that it suffers from instability
-\citep{silva_2014}.
+\citep{silva2014}.
 A common approach to solve this issue is to apply a smoothing filter, like a
@@
 digital terrain model
-\citep{amante_2009}.
+\citep{amante2009}.
 The effect of sedimentary basins is removed using the
@@
 by
-\citet{laske_2013}.
+\citet{laske2013}.
 Lateral variations in density along the Moho cannot be properly accounted for

### 2015-11-02 manuscript.tex
Discuss Jacobian in regularization before Bott
This sets the stage for why Bott is good and fast

@@
 
-Non-linear inversions for the relief of an interface (like
-the Moho) are ill-posed and required additional constraints in the form of
+Non-linear inversions for the relief of an interface (like the Moho)
+are ill-posed and require additional constraints in the form of
 regularization \citep{silva2001}.
 A common approach is to use the first-order Tikhonov regularization to impose
-smoothness on the solution,
+smoothness on the solution.
+The cost function for smoothness regularization is given by
 
@@
 \begin{equation}
-    \Gamma(\mathbf{p}) = \phi(\mathbf{p}) + \mu\theta(\mathbf{p}).
+    \Gamma(\mathbf{p}) = \phi(\mathbf{p}) + \mu\theta(\mathbf{p}),
 \end{equation}
@@
 \noindent
-The regularization parameter $\mu$ controls the balance between fitting the
-observed data and obeying the smoothness constraint.
+in which $\mu$ is the regularization parameter that controls the balance
+between fitting the observed data and obeying the smoothness constraint.
 
@@
 \end{equation}
+
+Producing the regularized solution is computationally costly because of two
+main factors:
+(1) the evaluation and storage of the dense $N \times M$ Jacobian matrix
+$\mathbf{A}$
+and (2) the solution of the resulting $M \times M$ equation system
+(not required for Steepest Descent).
+In practice, the derivatives in the Jacobian (Eq.~\ref{eq:jacobian})
+are often calculated through a first-order finite-difference approximation.
+Thus, evaluating $\mathbf{A}$ requires $2\times M \times N$ forward modeling
+operations for each iteration of the gradient descent algorithm.
+These computations are performed for each iteration of the optimization.
 
@@
 Jacobian matrix $\mathbf{A}$.
-In practice, the derivatives in Eq.~\ref{eq:jacobian} are often calculated through a
-first-order finite-difference approximation.
-Thus, evaluating $\mathbf{A}$ requires $2\times M \times N$ forward modeling
-operations for each iteration of the gradient descent algorithm.
 Bott's method also does not require the solution of equation systems.

### 2015-11-02 manuscript.tex
Tweaks to Bott

@@
 In this framework,
-Bott's method uses a Bouguer plate approximation of the relief to
-linearize the Jacobian matrix.
+Bott's method uses a Bouguer plate approximation of the gravitational effect of
+the relief, $d_i = 2\pi G \Delta\rho z_i$.
+The derivative of $d_i$ with respect to the parameter $z_i$ is
+$2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
 However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
@@
 
+\noindent
+In practice, both formulations lead to Eq.~\ref{eq:bott}.
 One of the advantages of Bott's method over the traditional Gauss-Newton or
@@
 Jacobian matrix $\mathbf{A}$.
-Bott's method also does not require the solution of equation systems.
-
-A disadvantage of Bott's method is that it suffers from instability
+Furthermore, Bott's method also does not require the solution of equation
+systems.
+However, a disadvantage of Bott's method is that it suffers from instability
 \citep{silva2014}.
-A common approach to solve this issue is to apply a smoothing filter, like a
-moving average, to the unstable estimate.
+A common approach to counter this issue is to apply a smoothing filter after
+the inversion to the unstable estimate, as in \citet{silva2014}.
 

### 2015-11-02 manuscript.tex
Add the full equation for regularized solutions
For both Gauss-Newton and steepest descent. Will use them later to
explain our method.

@@
 
-Producing the regularized solution is computationally costly because of two
-main factors:
+\noindent The parameter updates for the regularized Gauss-Newton and Steepest
+Descent methods, respectively, then become
+
+\begin{equation}
+    \left[\mathbf{A}^T\mathbf{A} + \mu\mathbf{R}^T\mathbf{R}\right]
+    \mathbf{\Delta p} =
+        \mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] -
+        \mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
+    \label{eq:gaussnewton-regul}
+\end{equation}
+
+\noindent and
+
+\begin{equation}
+    \mathbf{\Delta p} =
+        \mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] -
+        \mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
+    \label{eq:steepest-regul}
+\end{equation}
+
+Producing the regularized solution using the above equations is computationally
+costly because of two main factors:
 (1) the evaluation and storage of the dense $N \times M$ Jacobian matrix

### 2015-11-02 manuscript.tex
Draft of regularized bott section

@@
     \mathbf{A} = 2\pi G \Delta \rho \mathbf{I},
-    \label{eq:bott-jacobian}
+    \label{eq:bott-gaussnewton}
 \end{equation}
@@
 
-Approximate the Jacobian by making tesseroid size tend to infinity to get
-Bouguer slab.
-This approximation is good for tesseroids because each will cover a large
-enough area.
-Show case for the Steepest Descent.
-Extend the Jacobian to include lateral density variation.
-Important because density-contrast is positive or negative depending if the
-Moho is above or below the reference level.
-Enforce that the use of a particular
-
-Biggest computation time is in forward modeling.
-All matrices involved are sparse.
-Solve the sparse linear system with a conjugate gradient method.
-\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
-Use the regularized inversion because multiplying and solving the linear system
-are fast compared to forward modeling.
-Not using step size optimization because forward modeling is very slow so
-increased convergence doesn't justify the extra time spent on the discarded
-step attempts.
+We propose a regularized version of Bott's method to invert for the relief of
+the anomalous Moho in spherical coordinates.
+Our formulation maintains the regularized solutions
+for Gauss-Newton (Eq.~\ref{eq:gaussnewton-regul}) and
+Steepest Descent (Eq.~\ref{eq:steepest-regul})
+but replaces the full Jacobian matrix with the Bouguer plate approximations
+(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:bott-steepest}).
+This linearizes the Jacobian matrix and reduces it to a sparse diagonal matrix,
+thus eliminating the cost of computing and storing $\mathbf{A}$.
+Matrix arithmetic operations can be performed efficiently by taking advantage
+of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$.
+The same is true for solving the equation system in the Gauss-Newton method
+(Eq.~\ref{eq:gaussnewton-regul}).
+However, the computational cost of forward modeling is still present.
+Particularly, forward modeling using tesseroids is more computationally
+intensive than using right-rectangular prisms
+because of the numerical integration and adaptive discretization.
+Benchmarks suggest that forward modeling accounts for approximately $99\%$ of
+\todo{Checar esse número}
+the computation time for a Gauss-Newton inversion
+(see supplementary material)\todo{Referência melhor pra isso}.
+Hence, this formulation allows us to retain the efficiency of Bott's method
+while stabilizing the solution through the well established formalism of
+Tikhonov regularization.
 
@@
 \todo{Cite packages in the references.txt file.}
+\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
 

### 2015-11-02 manuscript.tex
Better define zref in parametrization
Needed this well defined to use in the cross-validation section.

@@
 is known as the gravity disturbance,
-\todo{Figura do seminário acompanha}
+\todo{Seminar figure here}
 
@@
 
-We parameterize the forward problem by discretizing the Moho undulation
+We parameterize the forward problem by discretizing the anomalous Moho
 into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids.
-In cases where the Moho is above the reference depth ($z_{ref}$),
-the top of the tesseroid is the Moho depth at the location of the $k$-eth
-tesseroid ($z_{k}$),
-the bottom is $z_{ref}$, and the density-contrast is positive.
-If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
-the bottom is the Moho depth, and the density-contrast is negative.
-\todo{Figura do seminário}
+The true (real Earth) Moho varies in depth
+with respect to the Moho of the Normal Earth.
+Hereafter we will refer to the depth of the Normal Earth Moho as $z_{ref}$.
+In cases where the true Moho is above $z_{ref}$,
+the top of the $k$th tesseroid is the Moho depth $z_{k}$,
+the bottom is $z_{ref}$, and the density-contrast ($\Delta\rho$) is positive.
+If the Moho is below $z_{ref}$, the top of the tesseroid is $z_{ref}$,
+the bottom is $z_k$, and $\Delta\rho$ is negative.
+\todo{Seminar figure here}
 
-Considering that the density-contrast of each tesseroid is fixed,
+Considering that the density-contrasts of the tesseroids are fixed parameters,
 the predicted gravity anomaly of the Moho is a non-linear function of the
@@
 because of the numerical integration and adaptive discretization.
-Benchmarks suggest that forward modeling accounts for approximately $99\%$ of
-\todo{Checar esse número}
-the computation time for a Gauss-Newton inversion
-(see supplementary material)\todo{Referência melhor pra isso}.
+Benchmarks suggest that
+forward modeling accounts for approximately $99\%$
+\todo{Check this number}
+of the computation time for a Gauss-Newton inversion
+(see supplementary material).
+\todo{Better reference}
 Hence, this formulation allows us to retain the efficiency of Bott's method
@@
 \subsection{Determination of hyper-parameters}
+
+There are three hyper-parameters that control the inversion results:
+(1) the regularization parameter $\mu$
+(2) the depth of the Moho of the reference ellipsoid
+(3) the density-contrast between the
 

### 2015-11-02 manuscript.tex
Started CV for regul param section

@@
 
-\subsection{Determination of hyper-parameters}
+\subsection{Estimating the regularization parameter}
 
-There are three hyper-parameters that control the inversion results:
-(1) the regularization parameter $\mu$
-(2) the depth of the Moho of the reference ellipsoid
-(3) the density-contrast between the
+The regularization parameter $\mu$ controls how much smoothness is applied to
+the inversion result.
+An optimal value of $\mu$ will stabilize and smooth the solution while not
+compromising the fit to the observed data.
+Two widely used methods to estimate an optimal $\mu$ are
+the L-curve criterion and cross-validation \citep{hansen1992}.
+Here, we will adopt the hold-out method of cross-validation \citep{kim2009}.
+\todo{Not the best reference}
+The hold-out method consists of splitting the observed data set into two
+independent parts:
+a training set $\mathbf{d}^o_{inv}$
+and a testing set $\mathbf{d}^o_{test}$.
+The training set is used in the inversion
+while the testing set is kept back
+and used to judge the quality of the chosen value of $\mu$.
+For a value of the regularization parameter $\mu_k$,
+the training set is inverted using $\mu_k$
+to obtain an estimate $\mathbf{\hat{p}}^k$.
+This estimate is used to calculate predicted data
+on the same points as the testing set
+via forward modeling
+($\mathbf{d}_{test}^k = \mathbf{f}(\mathbf{\hat{p}}^k$)).
+The metric chosen to evaluate $\mu_k$ is
+the mean square error (MSE) of the misfit
+between the observed and predicted testing data sets,
+
+\begin{equation}
+    MSE_k = \dfrac{\|\mathbf{d}^o_{test} - \mathbf{d}^k_{test}\|^2}{N_{test}},
+    \label{eq:msemu}
+\end{equation}
+
+\noindent
+in which $N_{test}$ is the number of data in the testing set.
+The optimal value of $\mu$ will be the one that minimizes the MSE,
+i.e. the one that best predicts the testing data.
+We emphasize that the inversion is performed only on the training data set.
+
+The algorithm for the hold-out cross-validation is summarized as follows:
+
+\begin{enumerate}
+    \item Divide the observed data into
+        the training ($\mathbf{d}^o_{inv}$)
+        and testing ($\mathbf{d}^o_{test}$) sets.
+    \item For each $\mu_k \in [\mu_1, \mu_2, \ldots, \mu_{N_{\mu}}]$:
+    \begin{enumerate}
+        \item Estimate $\mathbf{\hat{p}}^k$ by inverting the training set
+            $\mathbf{d}^o_{inv}$.
+        \item Use $\mathbf{\hat{p}}^k$ to calculate the predicted testing set
+            $\mathbf{d}^k_{test}$.
+        \item Calculate the mean square error $MSE_k$ using Eq.~\ref{eq:msemu}.
+    \end{enumerate}
+    \item The final solution is the $\mathbf{\hat{p}}^k$ corresponding to the
+        smallest $MSE_k$.
+\end{enumerate}
+
+Bott's method requires the same number of observed data ($N$)
+and model parameters ($M$).
+Limited ways to separate the training and testing data sets.
+Data and model must be on a regular grid.
+Cannot randomly separate.
+Use a dense data grid.
+Take for the training set a sub grid with double the original grid spacing.
+Every other point is included in the testing data set.
+The testing data set will have more points than training data set.
+One can generate observed data on a grid with half of the desired grid spacing.
+This is easy for data generated from spherical harmonic models.
+
+\subsection{Estimating $z_{ref}$ and $\Delta\rho$}
 

### 2015-11-02 manuscript.tex
More about the data set separation for CV

@@
 
-Bott's method requires the same number of observed data ($N$)
-and model parameters ($M$).
-Limited ways to separate the training and testing data sets.
-Data and model must be on a regular grid.
-Cannot randomly separate.
-Use a dense data grid.
-Take for the training set a sub grid with double the original grid spacing.
-Every other point is included in the testing data set.
-The testing data set will have more points than training data set.
-One can generate observed data on a grid with half of the desired grid spacing.
-This is easy for data generated from spherical harmonic models.
+The separation of the training and testing data sets is commonly done by taking
+random samples from the full data set.
+However, we cannot perform the separation in this way because
+Bott's method requires data on a regular grid as well as having model elements
+directly below each data point.
+Thus, we take as our training set the points from the observed data grid that
+fall on a similar grid but with twice the grid spacing
+(see Fig.~\ref{fig:grid_separation}).
+\todo{Include fig from seminar}
+All other points from the original data grid
+make up the testing data set.
+This separation will lead to
+a testing data set with more points than the training data set.
+A way to balance this loss of data in the inversion
+is to generate a data grid with half of the desired grid spacing,
+either through interpolation
+or from a spherical harmonic model.
+
+\begin{figure}
+    \centering
+    %\includegraphics[width=\columnwidth]{figures/paper/sam-gravity-data}
+    \caption{This is a figure caption.}
+    \label{fig:grid_separation}
+\end{figure}
 

### 2015-11-02 manuscript.tex
Finished estimation of zref and density contrast

@@
 
+The depth of the Normal Earth Moho ($z_{ref}$)
+and the density-contrast of the anomalous Moho ($\Delta\rho$)
+are other hyper-parameters of the inversion.
+That is, their value influences the final solution
+but they are not estimated during the inversion.
+Both hyper-parameters cannot be determined from the gravity data alone.
+Estimating $z_{ref}$ and $\Delta\rho$ requires
+information that is independent of the gravity data,
+such as knowledge of the parameters at certain points.
+This information can be used in a manner similar to
+the cross-validation described in the previous section.
+In this study, we use point estimates of the Moho depth
+to determine the optimal values of $z_{ref}$ and $\Delta\rho$.
+These points will generally come from seismologic studies,
+like receiver functions, surface wave dispersion, and deep refraction
+experiments.
+
+Let $\mathbf{z}_s^o$ be a vector of $N_s$ known Moho depths.
+We use the mean square error (MSE)
+as a measure of how well a given inversion output $\mathbf{\hat{p}}^k$
+fits the know depths.
+The optimal values of $z_{ref}$ and $\Delta\rho$
+are the ones that best fit the independent known Moho depths
+(i.e., produce the smallest MSE).
+However, the points do not necessarily coincide
+with the model elements of the inversion.
+Before computing the MSE,
+we interpolate $\mathbf{\hat{p}}^k$ on the known points
+to obtain the predicted depths $\mathbf{z}_s^k$.
+The MSE is defined as
+
+\begin{equation}
+    MSE = \dfrac{\|\mathbf{z}^o_s - \mathbf{z}^k_{s}\|^2}{N_s}.
+    \label{eq:msehyper}
+\end{equation}
+
+The algorithm for estimating $z_{ref}$ and $\Delta\rho$ is:
+
+\begin{enumerate}
+    \item For each combination of
+        $z_{ref,l} \in [z_{ref,1},z_{ref,2},\ldots,z_{ref,N_z}]$ and
+        $\Delta\rho_m \in
+         [\Delta\rho_1,\Delta\rho_2,\ldots,\Delta\rho_{N_{\rho}}]$:
+    \begin{enumerate}
+        \item Perform the inversion on the training data set
+            $\mathbf{d}^o_{inv}$ using $z_{ref,l}$, $\Delta\rho_m$, and
+            the previously estimated value of $\mu$.
+            The inversion output is the vector $\mathbf{\hat{p}}^{l,m}$.
+        \item Interpolate $\mathbf{\hat{p}}^{l,m}$
+            on the known points to obtain the predicted depths
+            $\mathbf{z}_s^{l,m}$.
+        \item Calculate the MSE between $\mathbf{z}_s^o$ and
+            $\mathbf{z}_s^{l,m}$ using Eq.~\ref{eq:msehyper}.
+    \end{enumerate}
+    \item The final solution is the $\mathbf{\hat{p}}^{l,m}$ corresponding to
+        the smallest MSE.
+\end{enumerate}
+
+A similar approach was used by \citet{martins2010}
+to estimate the parameters defining
+the density-contrast variation with depth
+of a sedimentary basin.
+\citet{vandermeijde2013} also had
+a similar methodology for dealing with the hyper-parameters,
+though in a less formalized way.
+
 \subsection{Software implementation}

### 2015-11-02 manuscript.tex
Better bibtex entries for software
Had to tweak where the url fields would go to show on the reference
list. Kind of hacky but works.
Cite software packages

@@
 
-\todo{Cite packages in the references.txt file.}
-\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
+The implementation relies on the open-source libraries
+scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
+for array-based computations,
+matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
+and seaborn
+\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
+for plots and maps,
+and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
+for geophysics specific tasks (e.g., forward modeling).
+
+The computational experiments
+(e.g., data processing, synthetic tests, real data application)
+were performed in
+Jupyter (formerly IPython) notebooks
+\citep[][ \url{http://jupyter.org/}]{perez2007}.
+
+\todo{Check which conjugate gradient scipy uses}
 
@@
 
-Meh.
+The authors are indebted to the developers and maintainers of the open-source
+software without which this work would not have been possible.
 

### 2015-11-02 manuscript.tex
About notebooks and where to find code

@@
 \citep[][ \url{http://jupyter.org/}]{perez2007}.
+The notebook files combine the source code used to run the experiments,
+the results and figures generated by the code,
+and rich text to explain and document the analysis.
+
+The Python implementation of the inversion as well as the Jupyter notebooks are
+freely available under the terms of the BSD 3-clause open-source license.
+Both can be found at the online repository
+\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
+An archived version is also available at
+\url{http://dx.doi.org/DOI_HERE} (made available upon publication).
+\todo{Insert Zenodo DOI here}
 

### 2015-11-02 manuscript.tex
Hide figs for now. urls in text for real data

@@
 is removed using the
-ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
-digital terrain model
-\citep{amante2009}.
+ETOPO1 digital terrain model
+\citep[][ \url{http://dx.doi.org/10.7289/V5C8276M}]{amante2009}.
 The effect of sedimentary basins is removed using the
-CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}} model
-by
-\citet{laske2013}.
+CRUST1.0 model
+\citep[][ \url{http://igppweb.ucsd.edu/~gabi/rem.html}]{laske2013}.
 Lateral variations in density along the Moho cannot be properly accounted for
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
-    \caption{This is a figure caption.}
-    \label{fig:sam-data}
-\end{figure*}
+%\begin{figure*}
+    %\centering
+    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
+    %\caption{This is a figure caption.}
+    %\label{fig:sam-data}
+%\end{figure*}
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
-    \caption{This is a figure caption.}
-    \label{fig:sam-sed}
-\end{figure*}
+%\begin{figure*}
+    %\centering
+    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
+    %\caption{This is a figure caption.}
+    %\label{fig:sam-sed}
+%\end{figure*}
 

### 2015-11-03 manuscript.tex
Add placeholder figures for missing ones

@@
 is known as the gravity disturbance,
-\todo{Seminar figure here}
 
@@
 The disturbance contains only the gravitational effects of density
-distributions that are anomalous with respect to the Normal Earth.
+distributions that are anomalous with respect to the Normal Earth
+(see Fig.~\ref{fig:anomalysketch}).
 This includes all masses above the surface of the ellipsoid (the topography),
@@
 
+% Sketches to explain the methodology
+
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{figures/paper/tesseroid-coord-sys}
+    \includegraphics[width=0.5\columnwidth]{figures/default_figure}
+    \caption{Sketch explaining disturbance and parametrization from ON seminar.}
+    \label{fig:anomalysketch}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figures/paper/tesseroid-coord-sys}
     \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
@@
 with respect to the Moho of the Normal Earth.
-Hereafter we will refer to the depth of the Normal Earth Moho as $z_{ref}$.
+Hereafter we will refer to the depth of the Normal Earth Moho as $z_{ref}$
+(see Fig.~\ref{fig:anomalysketch}).
 In cases where the true Moho is above $z_{ref}$,
@@
 the bottom is $z_k$, and $\Delta\rho$ is negative.
-\todo{Seminar figure here}
 
@@
 (see Fig.~\ref{fig:grid_separation}).
-\todo{Include fig from seminar}
 All other points from the original data grid
@@
     \centering
-    %\includegraphics[width=\columnwidth]{figures/paper/sam-gravity-data}
-    \caption{This is a figure caption.}
+    \includegraphics[width=0.5\columnwidth]{figures/default_figure}
+    \caption{Include figure of the grid point separation from ON seminar}
     \label{fig:grid_separation}

### 2015-11-03 manuscript.tex
Finished software implementation part

@@
 
-The implementation relies on the open-source libraries
+The inversion method proposed here is implemented in the Python programming
+language.
+The software is freely available
+under the terms of the BSD 3-clause open-source software license.
+Our implementation relies on the open-source libraries
 scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
@@
 and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
-for geophysics specific tasks (e.g., forward modeling).
+for geophysics specific tasks,
+particularly for forward modeling using tesseroids.
+We use the scipy.sparse package for sparse matrix arithmetic and linear
+algebra.
 
@@
 
-The Python implementation of the inversion as well as the Jupyter notebooks are
-freely available under the terms of the BSD 3-clause open-source license.
-Both can be found at the online repository
+All source code, data, and Jupyter notebooks
+used here can be found at the online repository
 \url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
 An archived version is also available at
-\url{http://dx.doi.org/DOI_HERE} (made available upon publication).
-\todo{Insert Zenodo DOI here}
-
-\todo{Check which conjugate gradient scipy uses}
+\url{http://dx.doi.org/DOI} (made available upon publication).
+The repository also contains instructions for installing the necessary software
+and reproducing all results presented here.
 
@@
 
-%\begin{figure*}
-    %\centering
-    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
-    %\caption{This is a figure caption.}
-    %\label{fig:sam-data}
-%\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
+    \caption{This is a figure caption.}
+    \label{fig:sam-data}
+\end{figure*}
 
-%\begin{figure*}
-    %\centering
-    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
-    %\caption{This is a figure caption.}
-    %\label{fig:sam-sed}
-%\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
+    \caption{This is a figure caption.}
+    \label{fig:sam-sed}
+\end{figure*}
 

### 2016-01-17 manuscript/manuscript.tex
Move ms files to manuscript folder

--- 2015-11-03 manuscript.tex
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/paper/tesseroid-coord-sys}
+    \includegraphics[width=0.5\columnwidth]{figures/tesseroid-coord-sys}
     \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
@@
 methods like Gauss-Newton or Steepest Descent.
-Such methods start from an initial estimate $\mathbf{p}^0$ and repeatedly
+Such methods start from an initial estimate $\mathbf{p}^0$ and iteratively
 update the estimate until a minimum is reached.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
+    \includegraphics[width=\textwidth]{figures/sam-gravity-data}
     \caption{This is a figure caption.}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
+    \includegraphics[width=\textwidth]{figures/sam-gravity-sed}
     \caption{This is a figure caption.}

### 2016-01-17 code/datasets.py
Tweaks and moves of the python modules
Rename moho.py to mohoinv and move the TesseroidRelief there. Better
module docstrings. Re-run example notebooks and make some tweaks to the
plots.

Had forgotten the future module dependency.

@@ -4,26 +4,31 @@ Defines classes and functions to load and manipulate the datasets we use.
 
 All datasets are provided in the 'data' directory of this repository.
 
+See the Jupyter notebook 'datasets-example.ipynb' to examples and instructions
+of how to use this module.
+
 CRUST1.0 model
 --------------
 
-* ``fetch_crust1``: loads the model from the zip archive (you can download 
-  it from http://igppweb.ucsd.edu/~gabi/crust1.html ). The function will 
+* ``fetch_crust1``: loads the model from the zip archive (you can download
+  it from http://igppweb.ucsd.edu/~gabi/crust1.html ). The function will
   return a *Crust1* object which you can use to interact with the model.
+* ``Crust1``: class to represent the CRUST1.0 model. Use it to extract the
+  desired layers and attributes from the model.
 
 Moho depth
 ----------
 
 * ``fetch_assumpcao_moho_points``: loads the point data from the
   seismic crustal thickness compilation of Assumpção et al. (2012).
-  
+
 ICGEM data files
 ----------------
 
 * ``load_icgem_gdf``: loads data from an ICGEM (http://icgem.gfz-potsdam.de/ICGEM/)
   ``.gdf`` file.
 * ``down_sample``: down-sample the grid data.
-  
+
 """
 from __future__ import division
 import tarfile
@@ -31,48 +36,48 @@ import hashlib
 import copy
 import numpy as np
 from fatiando.mesher import Tesseroid
-    
-    
+
+
 def down_sample(arrays, shape, every):
     """
     Down-sample data by taking every other data point.
-    
+
     Parameters:
-    
+
     * arrays : list of 1d-arrays
         The data arrays to down-sample
     * shape : tuple = (nlat, nlon)
         The original shape of the data.
     * every : int
         Will take every *every* data. For example, if
-        ``every=3``, will take every 3 data points. 
+        ``every=3``, will take every 3 data points.
         Equivalent of doing ``[::3, ::3]`` on a numpy
         2d-array.
-     
+
     Returns:
-    
+
     * array1, array2, array3, ..., shape
         The down-sampled arrays and the new shape of the
         data grid.
-        
+
     """
     downsampled = [array.reshape(shape)[::every, ::every]
                    for array in arrays]
     newshape = downsampled[0].shape
     return [v.ravel() for v in downsampled] + [newshape]
 
-    
+
 def load_icgem_gdf(fname, usecols=None):
     """
     Load data from an ICGEM .gdf file.
-    
+
[…]

### 2016-01-17 code/mohoinv.py

@@ -1,13 +1,25 @@
 """
-The gravity inversion class for the relief of the Moho.
+Implements the proposed Moho inversion method.
 
-Uses the base classes from *fatiando.inversion*.
+See the Jupyter notebooks 'moho-inversion-example.ipynb' and
+'tesseroid-relief-example.ipynb' for instructions and example usage of these
+classes.
+
+Defines the classes:
+
+* `MohoGravityInvSpherical`: Performs the inversion itself. Uses the classes
+  from *fatiando.inversion* as a base and *fatiando.gravmag.tesseroid* for
+  forward modeling.
+
+* `TesseroidRelief`: Class to represent a relief undulating around a reference
+  level and discretized into tesseroids.
+
 """
 from __future__ import division
 from fatiando.inversion import Misfit, CachedMethodPermanent, CachedMethod
 from fatiando.gravmag import tesseroid
 from fatiando import constants, utils, gridder
-from tesseroid_mesh import TesseroidRelief
+from fatiando.mesher import Tesseroid
 import scipy.sparse
 import numpy as np
 import copy
@@ -18,12 +30,12 @@ import warnings
 def make_mesh(area, shape, relief=None, reference=None):
     """
     Make a TesseroidRelief mesh for use in MohoGravityInvSpherical.
-    
-    This functions will create a mesh that has one tesseroid below each 
+
+    This functions will create a mesh that has one tesseroid below each
     data point. Data is considered to be on a regular grid.
-    
+
     Parameters:
-    
+
     * area : list = (s, n, w, e)
         The dimensions of the data grid in degrees.
     * shape : list = (nlat, nlon)
@@ -32,12 +44,12 @@ def make_mesh(area, shape, relief=None, reference=None):
         The relief of the interface. If None, will use a constant of 1.
     * reference : float
         The reference level. If None, will use a constant of 0.
-        
+
     Returns:
-    
+
     * mesh : TesseroidRelief
         The generated mesh.
-        
+
     """
     dlat, dlon = gridder.spacing(area, shape)
     s, n, w, e = area
@@ -54,13 +66,13 @@ class MohoGravityInvSpherical(Misfit):
     """
     Gravity inversion for the relief of the Moho using tesseroids.
     """
-    
+
     def __init__(self, lat, lon, height, data, mesh, njobs=1, field='gz'):
-        super(MohoGravityInvSpherical, self).__init__(data=data, nparams=mesh.size, 
+        super(MohoGravityInvSpherical, self).__init__(data=data, nparams=mesh.size,
[…]

### 2016-01-17 code/mohoinv.py
Started reorganizing simple sinthetic
Moved split_data function to  the mohoinv module. It's used in many
places. Need to run the notebook again and commit the results as well.

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 """
 Implements the proposed Moho inversion method.
 
@@ -25,6 +26,46 @@ import numpy as np
 import copy
 import multiprocessing
 import warnings
+
+
+def split_data(data, shape, every_other):
+    """
+    Split the data into inversion and test datasets
+    
+    Parameters:
+    
+    * data : list of 1d-arrays
+        List with the data arrays that will be divided (like lon, lat, 
+        gravity, etc)
+    * shape : tuple = (nlat, nlon)
+        The original shape of the data grid
+    * every_other : int
+        Will divide by taking every other "every_other" grid point
+        for the inversion dataset. The remaining points will be the 
+        test data.
+        
+    Returns:
+    
+    * inversion_set, test_set, inversion_shape:
+        The inversion_set and test_set are lists in the same order as "data".
+        inversion_shape is the shape of the new inversion dataset
+        
+    """
+    data = [i.reshape(shape) for i in data]
+    # Take "every_other" point for the inversion
+    inversion = [i[::every_other, ::every_other] for i in data]
+    # mask marks the grid points I didn't take for inversion
+    mask = np.ones(shape, dtype=np.bool)
+    mask[::every_other, ::every_other] = False  # These are the ones I took
+    test = [i[mask] for i in data]
+    shape = inversion[0].shape
+    # Sanity checks
+    assert all(t.size + i.size == d.size for t, i, d in zip(test, inversion, data)), \
+        "Number of points in inversion + test set different from original data."
+    assert all(t.size == test[0].size for t in test), "Test set has differet number of points"
+    assert all(i.size == inversion[0].size for i in inversion), "Inversion set has differet number of points"
+    assert all(i.shape == inversion[0].shape for i in inversion), "Inversion set has differet shape"
+    return [i.ravel() for i in inversion], test, shape
 
 
 def make_mesh(area, shape, relief=None, reference=None):

### 2016-02-05 code/mohoinv.py
Forgot to rename seismic_residuals call

@@ -90,7 +90,7 @@ def score_seismic_constraints(moho, lat, lon, height):
     """
     Return the MSE between the moho estimate and the point constraints.
     """
-    predicted = seismic_residuals(moho, lat, lon, height)
+    predicted = predict_seismic(moho, lat, lon)
     score = np.sum((predicted - height)**2)/height.size
     return score
 

### 2016-02-05 code/mohoinv.py
score_all takes the meshes, not the solvers

@@ -45,7 +45,7 @@ def score_all(solutions, test_data, points, njobs=1):
     If points is True, will assume test_data are the seismic point constraints.
     Otherwise, will assume it's the test data set.
     """
-    args = [[s.estimate_, test_data, points] for s in solutions]
+    args = [[moho, test_data, points] for moho in solutions]
     if njobs > 1:
         pool = multiprocessing.Pool(njobs)
         results = pool.map(_call_score, args)

### 2016-02-06 manuscript/manuscript.tex
Better wording in intro methods + figure reference
Reference the new problem concept figure in the manuscript.

@@
 %\usepackage{natbib}
-\documentclass[extra,mreferee]{gji}
-%\documentclass[extra]{gji}
+% \documentclass[extra,mreferee]{gji}
+\documentclass[extra]{gji}
 \usepackage{timet}
@@
 hereafter denoted as $\gamma$.
-This effect is calculated on the same point $P$ where the observation was made
-using the closed-form solution presented by \citet{li2001}.
-The difference between the observed gravity ($g$) and Normal gravity
+This effect is calculated on the same point $P$ where
+the gravity observation was made
+(Fig~\ref{fig:anomalysketch}a-b).
+$\gamma(P)$ is calculated using
+the closed-form solution presented by \citet{li2001}.
+The difference between the observed gravity at point P ($g(P)$)
+and Normal gravity at the same point
 is known as the gravity disturbance,
@@
 distributions that are anomalous with respect to the Normal Earth
-(see Fig.~\ref{fig:anomalysketch}).
+(see Fig.~\ref{fig:anomalysketch}c).
 This includes all masses above the surface of the ellipsoid (the topography),
@@
 
-All effects must either be removed or assumed negligible
-to invert for the anomalous Moho.
+In order to invert for the anomalous Moho relief,
+we must first isolate its gravitational attraction.
+Thus, all other effects
+must be either removed or assumed negligible.
+Here, we will remove the effect of the topography and oceans
+in order to obtain the full Bouguer disturbance
+(Fig~\ref{fig:anomalysketch}d),
+
+\begin{equation}
+    \delta_{bg}(P) = \delta(P) - g_{topo}(P).
+\end{equation}
+
+\noindent
+We will remove the effect of sedimentary basins
+but assume that the effects of
+other crustal and mantle sources are negligible.
+Thus, the only effect left will be that of the anomalous Moho relief
+(Fig~\ref{fig:anomalysketch}e).
 The gravitational attraction of the topography, oceans, and basins are
 calculated in a spherical Earth approximation by forward modeling using
-tesseroids
-(Fig.~\ref{fig:tesseroid}).
+tesseroids (Fig.~\ref{fig:tesseroid}).
 The tesseroid effects are calculated numerically using
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/default_figure}
+    \includegraphics[width=\columnwidth]{figures/problem-concept}
     \caption{Sketch explaining disturbance and parametrization from ON seminar.}
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/tesseroid-coord-sys}
+    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
     \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
@@
 We parameterize the forward problem by discretizing the anomalous Moho
-into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids.
+into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids
+(Fig~\ref{fig:anomalysketch}f).
 The true (real Earth) Moho varies in depth
@@
 Hereafter we will refer to the depth of the Normal Earth Moho as $z_{ref}$
-(see Fig.~\ref{fig:anomalysketch}).
+(see Fig.~\ref{fig:anomalysketch}b).
 In cases where the true Moho is above $z_{ref}$,
 the top of the $k$th tesseroid is the Moho depth $z_{k}$,
-the bottom is $z_{ref}$, and the density-contrast ($\Delta\rho$) is positive.
+the bottom is $z_{ref}$, and the density-contrast ($\Delta\rho$) is positive
+(red tesseroids in Fig~\ref{fig:anomalysketch}f).
 If the Moho is below $z_{ref}$, the top of the tesseroid is $z_{ref}$,
-the bottom is $z_k$, and $\Delta\rho$ is negative.
+the bottom is $z_k$, and $\Delta\rho$ is negative
+(grey tesseroids in Fig~\ref{fig:anomalysketch}f).
 
-Considering that the density-contrasts of the tesseroids are fixed parameters,
+Considering that the absolute value of the density-contrasts
+of the tesseroids is a fixed parameter,
 the predicted gravity anomaly of the Moho is a non-linear function of the

### 2016-02-06 manuscript/manuscript.tex
Reference grid separation figure in text

@@
 fall on a similar grid but with twice the grid spacing
-(see Fig.~\ref{fig:grid_separation}).
+(white dots with black outlines in Fig.~\ref{fig:grid_separation}).
 All other points from the original data grid
-make up the testing data set.
+make up the testing data set
+(black dots in Fig.~\ref{fig:grid_separation}).
 This separation will lead to
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/default_figure}
-    \caption{Include figure of the grid point separation from ON seminar}
+    \includegraphics[width=\columnwidth]{figures/cv-grid-separation}
+    \caption{Sketch of a data grid separated into
+        the training (white dots with black outlines)
+        and testing (black dots) data sets.
+        The training data set is still displayed on a regular grid
+        but with twice the grid spacing
+        of the original data grid.}
     \label{fig:grid_separation}

### 2016-02-09 manuscript/manuscript.tex
Caption for problem concept sketch

@@
 \newcommand{\Title}{
-    Fast non-linear gravity inversion in spherical coordinates:
-    application to the South American Moho
+    Fast non-linear gravity inversion in spherical coordinates
+    with application to the South American Moho
 }
@@
     \includegraphics[width=\columnwidth]{figures/problem-concept}
-    \caption{Sketch explaining disturbance and parametrization from ON seminar.}
+    \caption{
+        Sketch of the stages in gravity data correction and
+        the discretization of the anomalous Moho relief using tesseroids.
+        (a) The Earth and the measured gravity at point P ($g(P)$).
+        (b) The Normal Earth and the calculated normal gravity at point P
+        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
+        (c) The gravity disturbance ($\delta(P)$) and
+        the corresponding density anomalies after removal of the normal gravity:
+        topography, oceans, crustal heterogeneities, and the anomalous Moho.
+        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
+        correction and the remaining density anomalies.
+        (e) All density anomalies save the anomalous Moho are assumed to have
+        been removed before inversion.
+        (f) The discretization of the anomalous Moho in tesseroids. Grey
+        tesseroids will have a negative density contrast while red tesseroids
+        will have a positive one.
+    }
     \label{fig:anomalysketch}
@@
         North-oriented coordinate system (x, y, z).
-        After \citet{uieda2015},
-        available at
-        \url{http://dx.doi.org/10.6084/m9.figshare.1495525}.
+        After \citet{uieda2015}.
     }

### 2016-02-10 manuscript/manuscript.tex
Figure for model and data in simple synthetic

@@
 
-Meh.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
+    \caption{
+        A simple Moho model made of tesseroids for synthetic data application.
+        (a) The Moho depth of the model in kilometers.
+        The model transitions from a deep Moho in the right to a shallow Moho in
+        left, simulating the transition between a continental and an oceanic
+        Moho.
+        Each pixel in the pseudo-color image corresponds to a tesseroid of the
+        model.
+        (b) Noise-corrupted synthetic gravity data generated from the model
+        shown in (a).
+    }
+    \label{fig:simple-data}
+\end{figure}
 

### 2016-02-10 manuscript/manuscript.tex
Caption for simple synthetic results figure

@@
     \Gamma(\mathbf{p}) = \phi(\mathbf{p}) + \mu\theta(\mathbf{p}),
+    \label{eq:goalfunction}
 \end{equation}
@@
 
+Bla bla bla.
+
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure*}
+    \centering
+    \includegraphics[]{figures/synthetic-simple-results}
+    \caption{
+        Results from the inversion of the simple synthetic data.
+        (a) The estimated Moho depth.
+        (b) The difference between the true model depths
+        and the estimated depths.
+        (c) The inversion residuals (observed data minus
+        the data predicted by the estimate).
+        (d) Normalized histogram of the residuals. Also shown are the calculated
+        mean and standard deviation (std) of the residuals.
+        Note that the data were contaminated with normally distributed
+        pseudo-random noise with zero mean and 5 mGal standard deviation.
+        (e) Cross-validation curve used to determine the optimal regularization
+        parameter (Eq.~\ref{eq:goalfunction}).
+        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
+        $\mu = 0.00046$ (red triangle).
+        (f) Goal function value (Eq.~\ref{eq:goalfunction}) per Gauss-Newton
+        iteration showing the convergence of the gradient descent.
+    }
+    \label{fig:simple-results}
+\end{figure*}
 

### 2016-02-12 manuscript/manuscript.tex
Caption for crust1 synthetic data figure
Add seismic points to crust1 data figure
Had to make the figure whole page and include the new plot  in the
caption.

@@
 
-Meh.
+Bla bla bla.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/synthetic-crust1-data}
+    \caption{
+        Synthetic data of a model derived from CRUST1.0.
+        The model is made of tesseroids with an constant density-contrast
+        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
+        $z_{ref} = 30\ km$.
+        (a) The Moho depth of the model in kilometers.
+        Each pixel in the pseudo-color image corresponds to a tesseroid of the
+        model.
+        (b) Noise-corrupted synthetic gravity data generated from the model.
+        (c) Synthetic seismic data simulating point estimates of Moho depth.
+        The point estimates were obtained by interpolating
+        the Moho depth in (a).
+    }
+    \label{fig:crust1-data}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[]{figures/synthetic-crust1-results}
+    \caption{
+    CRUST1 results.
+    }
+    \label{fig:crust1-results}
+\end{figure*}
 

### 2016-02-14 manuscript/manuscript.tex
Figure for SAm data stages in processing
Grouped the sediment model in this figure as well. Replaces the old data
figure. Will put the final gravity data in a separate figure.

Placeholders for figures in the paper.
Map of the sediment-free Bouguer for SAm
Figure for the Assumpção seismic data
Remove width setting in figures
Don't need it and it messes up figures when using manuscript mode.
Add width only to full page figures
The page width in manuscript mode is smaller than 7in so I need this.
Figure for the estimated Moho depth for SAm
Plot seismic diff in same figure as inversion results
Fi

@@
 %\usepackage{natbib}
-% \documentclass[extra,mreferee]{gji}
-\documentclass[extra]{gji}
+\documentclass[extra,mreferee]{gji}
+% \documentclass[extra]{gji}
 \usepackage{timet}
@@
 }
-
-% Useful commands
-% ===============
 
@@
 
-% Sketches to explain the methodology
-
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{figures/problem-concept}
+    \includegraphics{figures/problem-concept}
     \caption{
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
+    \includegraphics{figures/tesseroid-coord-sys}
     \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/cv-grid-separation}
+    \includegraphics{figures/cv-grid-separation}
     \caption{Sketch of a data grid separated into
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
+    \includegraphics{figures/synthetic-simple-data}
     \caption{
@@
     \centering
-    \includegraphics[]{figures/synthetic-simple-results}
+    \includegraphics[width=\textwidth]{figures/synthetic-simple-results}
     \caption{
@@
         the data predicted by the estimate).
-        (d) Normalized histogram of the residuals. Also shown are the calculated
+        (d) Histogram of the residuals. Also shown are the calculated
         mean and standard deviation (std) of the residuals.
@@
     \centering
-    \includegraphics{figures/synthetic-crust1-data}
+    \includegraphics[width=\textwidth]{figures/synthetic-crust1-data}
     \caption{
@@
     \centering
-    \includegraphics[]{figures/synthetic-crust1-results}
+    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
     \caption{
-    CRUST1 results.
+        Inversion results from the CRUST1.0 synthetic data.
+        (a) The estimated Moho depth.
+        (b) The inversion residuals (observed minus predicted data).
+        (c) Histogram of the residuals shown in (b).
+        (d) Cross-validation curve used to determine
+        the regularization parameter (Eq.~\ref{eq:goalfunction}).
+        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
+        $\mu = 0.0001$ (red triangle).
+        (e) difference between the CRUST1.0 model depths
+        (Fig.~\ref{fig:crust1-data}a)
+        and the estimated depths.
+        (f) Difference between the synthetic seismic observations
+        (Fig.~\ref{fig:crust1-data}c)
+        and the estimated depths.
+        (g) Histogram of the differences shown in (f).
+        (h) Cross-validation results used to determine
+        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
+        The colored contours represent
+        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
+        The minimum (red triangle) is found at $z_{ref} = 30\ km$
+        and $\Delta\rho = 350\ kg/m^3$.
     }
@@
 
-\subsection{Gravity data}
+\subsection{Gravity and seismic data}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/sam-gravity-data}
-    \caption{This is a figure caption.}
-    \label{fig:sam-data}
+    \includegraphics[width=\textwidth]{figures/south-america-corrections}
+    \caption{Gravity data and corrections.}
+    \label{fig:sam-corrections}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/sam-gravity-sed}
-    \caption{This is a figure caption.}
-    \label{fig:sam-sed}
+    \includegraphics[width=\textwidth]{figures/south-america-data}
+    \caption{Input data for the inversion.
+        (a) Sediment-free Bouguer disturbance for South America.
+        (b) Map of seismic point estimates of Moho depth.}
+    \label{fig:sam-data}
 \end{figure*}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+Bla bla bla.
 
-Meh.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/south-america-moho}
+    \caption{The estimated Moho of South America.}
+    \label{fig:sam-moho}
+\end{figure*}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/south-america-residuals}
+    \caption{Residuals with histogram and convergence.}
+    \label{fig:sam-residuals}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/south-america-cv}
+    \caption{Cross-validation.}
+    \label{fig:sam-cv}
+\end{figure}
 

### 2016-02-14 manuscript/manuscript.tex
Caption for SAm data corrections figure

@@
     \delta(P) = g(P) - \gamma(P).
+    \label{eq:disturbance}
 \end{equation}
@@
     \delta_{bg}(P) = \delta(P) - g_{topo}(P).
+    \label{eq:bouguer}
 \end{equation}
@@
     \includegraphics[width=\textwidth]{figures/south-america-corrections}
-    \caption{Gravity data and corrections.}
+    \caption{
+        Gravity data for South America and the models used in the data
+        corrections.
+        (a) Topography from ETOPO1 sampled at $0.1^\circ$ grid spacing.
+        (b) Gravitational attraction of the topography calculated
+        at the observation height using tesseroids.
+        (c) The gravity disturbance (Eq.~\ref{eq:disturbance}) calculated from
+        the raw gravity data.
+        (d) The Bouguer disturbance (Eq.~\ref{eq:bouguer}) obtained by
+        subtracting (b) from (c).
+        The upper (e), middle (f), and lower (g) sediment layer thicknesses
+        from the CRUST1.0 model.
+        (h) The total gravitational attraction of the sediment layers shown in
+        (e), (f), and (g), calculated using tesseroids.
+        }
     \label{fig:sam-corrections}

### 2016-02-14 manuscript/manuscript.tex
Caption for SAm inversion data figure
Caption for the SAm residuals figure

@@
     \includegraphics[width=\textwidth]{figures/south-america-data}
-    \caption{Input data for the inversion.
+    \caption{
+        Input data for the South American Moho inversion.
         (a) Sediment-free Bouguer disturbance for South America.
-        (b) Map of seismic point estimates of Moho depth.}
+        Obtained by subtracting the total sediment gravitational effect
+        (Fig.~\ref{fig:sam-corrections}h) from the Bouguer disturbance
+        (Fig.~\ref{fig:sam-corrections}d).
+        (b) Seismological Moho depth estimates from
+        \citet{assumpcao2012}.
+    }
     \label{fig:sam-data}
@@
     \includegraphics[width=\textwidth]{figures/south-america-moho}
-    \caption{The estimated Moho of South America.}
+    \caption{
+        Inversion results for the South American Moho.
+        (a) The estimated Moho depth of South America.
+        (b) Differences between the seismological depths of
+        \citet{assumpcao2012} and our gravity-derived estimate shown in (a).
+        The inset in (b) shows a histogram of the differences along with their
+        calculated mean and standard deviation (std).
+    }
     \label{fig:sam-moho}
@@
     \includegraphics{figures/south-america-residuals}
-    \caption{Residuals with histogram and convergence.}
+    \caption{
+        Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
+        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a)
+        shown as (a) a map and (b) a histogram with the calculated mean and
+        standard deviation.
+        (c) The value of the goal function (Eq.~\ref{eq:goalfunction})
+        per Gauss-Newton iteration showing the convergence of the algorithm.
+        Note that the y-axis is in logarithmic scale.
+    }
     \label{fig:sam-residuals}

### 2016-02-14 manuscript/manuscript.tex
Caption for the SAm CV figure

@@
     \caption{
-        Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
-        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a)
-        shown as (a) a map and (b) a histogram with the calculated mean and
+        Residuals for the South American Moho inversion.
+        The residuals are the observed data in Fig.~\ref{fig:sam-data}a
+        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a.
+        Shown as (a) a map and (b) a histogram with the calculated mean and
         standard deviation.
@@
     \includegraphics{figures/south-america-cv}
-    \caption{Cross-validation.}
+    \caption{
+        Cross-validation results for the South American Moho inversion.
+        (a) Cross-validation to determine the regularization parameter $\mu$
+        (Eq.~\ref{eq:goalfunction}).
+        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
+        shown as a red triangle,
+        corresponds to $\mu = 10^{-10}$.
+        (b) Cross-validation to determine
+        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
+        The colored contours represent
+        the Mean Square Error (Eq.~\ref{eq:msehyper}).
+        The minimum (red triangle) is found at $z_{ref} = 35\ km$
+        and $\Delta\rho = 400\ kg/m^3$.
+    }
     \label{fig:sam-cv}

### 2016-02-20 manuscript/profiling.tex
Run synthetic simple profiling and remove steepest
Removed all steepest descent runs from the notebook, leave only the
newton runs. Remove the steepest results files as well. Regenerate
figures from new results. Add profiling results.

\begin{table}
    \centering
    \caption{
        Total time spent on each function during a single inversion of
        simple synthetic data.
        The inversion was performed on a laptop computer with a
        Intel(R) Core(TM) i7-3612QM CPU @ 2.10GHz processor.
        The total time for the inversion was 42.133 seconds.        
    }
    \label{profiling}
    \begin{tabular}{lcc}
        Function description & Time & Percentage of total time\\
        \hline 
        Sparse conjugate gradient & 0.021 s & 0.050\%\\
        Sparse dot product & 0.007 s & 0.017\%\\
        Tesseroid forward modeling & 42.059 s & 99.824\%\\
        \hline
    \end{tabular}
\end{table}

### 2016-02-21 manuscript/manuscript.tex
Run synthetic simple profiling and remove steepest
Removed all steepest descent runs from the notebook, leave only the
newton runs. Remove the steepest results files as well. Regenerate
figures from new results. Add profiling results.
Reference profiling results in methods
To justify solving the sparse systems

@@
 Benchmarks suggest that
-forward modeling accounts for approximately $99\%$
-\todo{Check this number}
+forward modeling accounts for approximately $99.8\%$
 of the computation time for a Gauss-Newton inversion
-(see supplementary material).
-\todo{Better reference}
+(see section~\ref{sec:simple-synthetic} and table~\ref{profiling} below).
 Hence, this formulation allows us to retain the efficiency of Bott's method
@@
 \section{Application to synthetic data from a simple model}
+\label{sec:simple-synthetic}
 
 Bla bla bla.
+
+\input{profiling.tex}
 

### 2016-02-21 manuscript/manuscript.tex
Better note to reviewers regarding archived repo

@@
 All source code, data, and Jupyter notebooks
-used here can be found at the online repository
+can be found at the online repository
 \url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
-An archived version is also available at
-\url{http://dx.doi.org/DOI} (made available upon publication).
-The repository also contains instructions for installing the necessary software
-and reproducing all results presented here.
+The repository also contains instructions for replicating all results presented
+here.
+An archived version of this repository is also available at
+\url{http://dx.doi.org/...}
+(\textbf{Note to reviewers: the archived version will be uploaded only upon
+publication}).
 

### 2016-02-21 manuscript/manuscript.tex
Join both synthetic data section into a single one
They are subsections now. Wrote an introductory paragraph to the new
section.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to synthetic data from a simple model}
+\section{Application to synthetic data}
+
+We test and illustrate the proposed inversion method
+by applying it to two noise-corrupted synthetic data sets.
+The first data set is generated by a simple Moho model simulating the transition
+from a thicker continental crust to a thinner oceanic crust.
+This application uses cross-validation to estimate the regularizing parameter
+($\mu$) while assuming that the anomalous Moho density-contrast ($\Delta\rho$)
+and the Normal Earth Moho depth ($z_{ref}$) are known quantities.
+The second data set is generated by a more complex model derived from
+the CRUST1.0 model \citep{laske2013}.
+This application uses cross-validation to estimate all three hyper-parameters:
+$\mu$, $\Delta\rho$, and $z_{ref}$.
+The model is restricted to South America and is meant to simulate
+with more fidelity the real data application.
+
+\subsection{Simple model}
 \label{sec:simple-synthetic}
 
-Bla bla bla.
+We have applied
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to synthetic data from the CRUST1.0 model}
+\subsection{Model based on CRUST1.0}
 

### 2016-02-21 manuscript/manuscript.tex
Don't mention steepest in methods for spherical coordinates inversion

@@
     \theta(\mathbf{p}) = \mathbf{p}^T\mathbf{R}^T\mathbf{R}\mathbf{p},
+    \label{eq:regul}
 \end{equation}
@@
 the anomalous Moho in spherical coordinates.
-Our formulation maintains the regularized solutions
-for Gauss-Newton (Eq.~\ref{eq:gaussnewton-regul}) and
-Steepest Descent (Eq.~\ref{eq:steepest-regul})
-but replaces the full Jacobian matrix with the Bouguer plate approximations
-(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:bott-steepest}).
+Our formulation maintains the regularized solution
+for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
+but replaces the full Jacobian matrix with the Bouguer plate approximation
+(Eq.~\ref{eq:bott-gaussnewton}).
 This linearizes the Jacobian matrix and reduces it to a sparse diagonal matrix,
@@
 Matrix arithmetic operations can be performed efficiently by taking advantage
-of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$.
+of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$
+(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:regul}).
 The same is true for solving the equation system in the Gauss-Newton method
@@
 intensive than using right-rectangular prisms
-because of the numerical integration and adaptive discretization.
+because of the numerical integration and adaptive discretization
+\citep{uieda2016}.
 Benchmarks suggest that

### 2016-02-21 manuscript/manuscript.tex
Paragraph describing simple model and data

@@
 %\usepackage{natbib}
-\documentclass[extra,mreferee]{gji}
-% \documentclass[extra]{gji}
+% \documentclass[extra,mreferee]{gji}
+\documentclass[extra]{gji}
 \usepackage{timet}
@@
 
-We have applied
+We simulate the transition from a continental-type Moho to an oceanic-type Moho
+using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
+juxtaposed tesseroids (a total of $M = 2000$ model elements).
+The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
+and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
+Fig.~\ref{fig:simple-data}a shows the model Moho depths,
+where each pixel in the pseudo-color image corresponds to
+a tesseroid of the model.
+
+The synthetic data were forward modeled on a regular grid of
+$N_{lat} \times N_{lon} = 79 \times 99$ points
+(a total of $N = 7821$ observations)
+at a constant height of 50 km.
+The data were contaminated with pseudo-random noise
+sampled from a normal distribution with zero mean and 5 mGal standard deviation.
+Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set.
+The data grid spacing is half the grid spacing of the tesseroid model
+so that, when separating the training and testing data sets
+(Fig.~\ref{fig:grid_separation}),
+the training data set points will fall directly above each model element.
 

### 2016-02-21 manuscript/manuscript.tex
Paragraphs describing the simple synthetic application

@@
 
+We separated the synthetic data into training and testing data sets
+following Fig.~\ref{fig:grid_separation}.
+The training data set is a regular grid of
+$N_{lat} \times N_{lon} = 40 \times 50$ points
+(a total of $N_{train} = 2000$).
+The testing data set is composed of $N_{test} = 5821$ observations.
+We used cross-validation to estimate an optimal regularization parameter ($\mu$)
+from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
+between $10^{-6}$ and $10^{-1}$.
+We ran our regularized inversion on the training data set
+for each value of $\mu$,
+obtaining 16 Moho depth estimates.
+We computed the mean square error (MSE, Eq.~\ref{eq:msemu}) for each estimate.
+The final estimated Moho depth is the one that minimizes the MSE.
+
+Fig.~\ref{fig:simple-results} summarizes the inversion results.
+Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
+after cross-validation.
+The recovered model is smooth, indicating that the cross-validation procedure
+was effective at estimating an optimal regularization parameter.
+Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
+(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
+The differences appear to be semi-randomly distributed with a maximum
+coinciding with a short-wavelength feature in the true model.
+The maximum and minimum differences are approximately
+2.19 and -2.13 km, respectively.
+Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
+the observed and predicted data), in mGal.
+The largest residual (in absolute value) coincides with the largest difference
+between the true model and the estimate.
+The inversion residuals are normally distributed,
+as shown in Fig.~\ref{fig:simple-results}d,
+with 0.02 mGal mean and a standard deviation of 3.63 mGal.
+The cross-validation curve in Fig.~\ref{fig:simple-results}e
+shows a clear minimum MSE at $\mu = 0.00046$
+(indicated by the red triangle).
+Fig.~\ref{fig:simple-results}f shows the convergence of
+the Gauss-Newton optimization in eight iterations.
+
 \input{profiling.tex}
@@
         parameter (Eq.~\ref{eq:goalfunction}).
+        Both axis are in logarithmic scale.
         The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
@@
         iteration showing the convergence of the gradient descent.
+        The y-axis is in logarithmic scale.
     }

### 2016-02-21 manuscript/manuscript.tex
Add paragraph about the profiling

@@
     d_i = f_i(\mathbf{p}),
+    \label{eq:forward}
 \end{equation}
@@
 algebra.
+The sparse linear system in Eq.~\ref{eq:gaussnewton-regul}
+is solved using the conjugate gradient method implemented in scipy.sparse.
 
@@
 the Gauss-Newton optimization in eight iterations.
+
+We investigated the computation time spent in each section of the inversion
+process using a source code profiler.
+The profiler measures how much time is spent inside each function during
+the execution of a program.
+We ran the profiler on a single inversion of the training data set
+using the estimated regularization parameter.
+We tracked the total time spent inside each of the three functions
+that represent the largest computational bottlenecks of the inversion:
+solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
+using the conjugate gradient method,
+performing the dot products required to compute
+the Hessian matrix (Eq.~\ref{eq:hessian-regul})
+and the gradient vector (Eq.~\ref{eq:gradient-regul}),
+and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
+The profiling results are presented in table~\ref{profiling}.
+The time spent on forward modeling accounts for approximately
+99.8\% of the total computation time.
 

### 2016-02-21 manuscript/manuscript.tex
Better wording about the profiling results
Fixes #4

@@
 and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
-The profiling results are presented in table~\ref{profiling}.
-The time spent on forward modeling accounts for approximately
+The profiling results presented in table~\ref{profiling}
+show that the time spent on forward modeling accounts for approximately
 99.8\% of the total computation time.

### 2016-02-22 manuscript/manuscript.tex
Add some marker comments for each section

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Parametrization}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Inverse problem}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Regularization}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Bott's method}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Regularized Bott's method in spherical coordinates}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Estimating the regularization parameter}
@@
 Here, we will adopt the hold-out method of cross-validation \citep{kim2009}.
-\todo{Not the best reference}
 The hold-out method consists of splitting the observed data set into two
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Estimating $z_{ref}$ and $\Delta\rho$}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Software implementation}
@@
 
-\subsection{Simple model}
-\label{sec:simple-synthetic}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simple model}\label{sec:simple-synthetic}
 
@@
 
-We investigated the computation time spent in each section of the inversion
+We also investigated the computation time spent in each section of the inversion
 process using a source code profiler.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Model based on CRUST1.0}
-
-Bla bla bla.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Gravity and seismic data}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Inversion results}

### 2016-02-22 manuscript/manuscript.tex
Paragraphs about model and data in CRUST1 synthetic
Also some tweaks to the simple synthetic test, particularly including
the initial estimate used.

@@
 and the Normal Earth Moho depth ($z_{ref}$) are known quantities.
+This first test is simplified in order to investigate solely
+the efficiency of the inversion and
+the cross-validation procedure to estimate $\mu$.
 The second data set is generated by a more complex model derived from
-the CRUST1.0 model \citep{laske2013}.
+the South American portion of the global CRUST1.0 model \citep{laske2013}.
 This application uses cross-validation to estimate all three hyper-parameters:
 $\mu$, $\Delta\rho$, and $z_{ref}$.
-The model is restricted to South America and is meant to simulate
+The model and corresponding synthetic data are meant to simulate
 with more fidelity the real data application.
@@
 obtaining 16 Moho depth estimates.
-We computed the mean square error (MSE, Eq.~\ref{eq:msemu}) for each estimate.
-The final estimated Moho depth is the one that minimizes the MSE.
+For all inversions, the initial Moho depth estimate
+used to start the Gauss-Newton optimization
+was set to 60 km depth for all inversion parameters.
+Finally, we computed the mean square error (MSE, Eq.~\ref{eq:msemu})
+for each estimate and chose as the final estimated Moho model
+the one that minimizes the MSE.
 
@@
 \subsection{Model based on CRUST1.0}
+
+In this test, we simulate the anomalous Moho of South America
+using the Moho depth of the CRUST1.0 model
+\citep[][ Fig.~\ref{fig:crust1-data}a]{laske2013}.
+The Normal Earth Moho is $z_{ref} = 30\ km$ and
+the density-contrast is $\Delta\rho = 350\ kg/m^3$.
+We forward model the gravitational attraction of the anomalous Moho
+on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
+(a total of 18921 observations) at a constant height of 50 km.
+We contaminate the synthetic data with normally distributed pseudo-random noise
+with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).
+
+The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
+requires knowledge of the Moho depth at certain points,
+usually from seismic experiments.
+Thus, we must also generate synthetic seismic data about the Moho depth.
+We produce such data by interpolating the Moho depth shown in
+Fig.~\ref{fig:crust1-data}a on the same geographic coordinates as the
+data from \citet{assumpcao2012}.
+The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
 

### 2016-02-23 manuscript/manuscript.tex
Add model information in crust1 synthetic

@@
 In this test, we simulate the anomalous Moho of South America
-using the Moho depth of the CRUST1.0 model
-\citep[][ Fig.~\ref{fig:crust1-data}a]{laske2013}.
-The Normal Earth Moho is $z_{ref} = 30\ km$ and
+using Moho depth information extracted from the CRUST1.0 model
+\citep{laske2013}.
+We construct a model with
+$M_{lat} \times M_{lon} = 80 \times 60$ tesseroids, 4800 in total,
+using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
+In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
 the density-contrast is $\Delta\rho = 350\ kg/m^3$.
@@
 The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
-requires knowledge of the Moho depth at certain points,
+requires knowledge of the Moho depth at certain points
+($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
 usually from seismic experiments.
@@
 The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
+
+We ran cross-validation to estimate an optimal regularization parameter ($\mu$)
+by separating the synthetic data into training and testing data sets
+(Fig.~\ref{fig:grid_separation}).
+The training data set is a regular grid
+with half the grid spacing of the original data
+($N_{lat} \times N_{lon} = 159 \times $)
 

### 2016-02-23 manuscript/manuscript.tex
Better description of our method
Didn't even mention tesseroids before. Better wording for benchmark
part.

@@
 the anomalous Moho in spherical coordinates.
-Our formulation maintains the regularized solution
+To adapt Bott's method to spherical coordinates,
+we replace the right-rectangular prisms in the forward modeling
+($\mathbf{d}(\mathbf{p}^k)$ in Eq.~\ref{eq:bott})
+with tesseroids.
+The tesseroid forward modeling uses the adaptive discretization algorithm
+of \citet{uieda2016} to achieve accurate results.
+Furthermore, our formulation maintains the regularized solution
 for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
@@
 \citep{uieda2016}.
-Benchmarks suggest that
-forward modeling accounts for approximately $99.8\%$
-of the computation time for a Gauss-Newton inversion
-(see section~\ref{sec:simple-synthetic} and table~\ref{profiling} below).
-Hence, this formulation allows us to retain the efficiency of Bott's method
+Our benchmarks suggest that
+sparse matrix multiplications and solving the sparse linear system
+in Eq.~\ref{eq:gaussnewton-regul}
+account for less than 0.2\%
+of the computation time of a single inversion
+(see section~\ref{sec:simple-synthetic} and table~\ref{profiling}).
+Hence, by employing the use of space matrices,
+our formulation retains the efficiency of Bott's method
 while stabilizing the solution through the well established formalism of

### 2016-02-23 manuscript/manuscript.tex
Sparse matrix linalg is 0.1% not 0.2%

@@
 in Eq.~\ref{eq:gaussnewton-regul}
-account for less than 0.2\%
+account for less than 0.1\%
 of the computation time of a single inversion
 (see section~\ref{sec:simple-synthetic} and table~\ref{profiling}).
-Hence, by employing the use of space matrices,
+Hence, by employing the use of sparse matrices,
 our formulation retains the efficiency of Bott's method

### 2016-02-23 manuscript/manuscript.tex
Describe model and what was done in crust1 synthetic
Better descriptions for model and data. Results were inexistent.
Need to write about the final results now.

@@
 was set to 60 km depth for all inversion parameters.
+Furthermore, $z_{ref}$ and $\Delta\rho$ are set to their respective true values.
 Finally, we computed the mean square error (MSE, Eq.~\ref{eq:msemu})
@@
 \citep{laske2013}.
-We construct a model with
-$M_{lat} \times M_{lon} = 80 \times 60$ tesseroids, 4800 in total,
+We construct a tesseroid model with
+$M_{lat} \times M_{lon} = 80 \times 60$ juxtaposed elements, 4800 in total,
 using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
@@
 the density-contrast is $\Delta\rho = 350\ kg/m^3$.
-We forward model the gravitational attraction of the anomalous Moho
-on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
-(a total of 18921 observations) at a constant height of 50 km.
+We produce the synthetic data at a constant height of 50 km
+and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
+(a total of 18921 observations).
 We contaminate the synthetic data with normally distributed pseudo-random noise
@@
 We produce such data by interpolating the Moho depth shown in
-Fig.~\ref{fig:crust1-data}a on the same geographic coordinates as the
-data from \citet{assumpcao2012}.
+Fig.~\ref{fig:crust1-data}a on the same geographic coordinates
+as the 937 points from the \citet{assumpcao2012} data set.
 The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
 
-We ran cross-validation to estimate an optimal regularization parameter ($\mu$)
-by separating the synthetic data into training and testing data sets
-(Fig.~\ref{fig:grid_separation}).
-The training data set is a regular grid
-with half the grid spacing of the original data
-($N_{lat} \times N_{lon} = 159 \times $)
+We perform the cross-validation procedures in two parts.
+First, we run the cross-validation to estimate
+an optimal regularization parameter ($\mu$).
+The starting estimate for all inversions is
+60 km depth for all model parameters.
+For this cross-validation,
+we keep $z_{ref}$ and $\Delta\rho$ fixed to
+$20\ km$ and $500\ kg/m^3$, respectively.
+Our investigations suggest that the outcome of this round of cross-validation
+does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
+Second, we use the estimated $\mu$ to run the cross-validation
+to estimate $z_{ref}$ and $\Delta\rho$,
+thus obtaining the final estimated Moho depths.
+Fig.~\ref{fig:crust1-results} summarizes the final results.
+
+For the first cross-validation,
+we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
+a training set with half the grid spacing of the original data
+($N_{lat} \times N_{lon} = 80 \times 60$)
+and a testing set with 14,121 observations.
+We run the inversion for 16 different values of $\mu$,
+equally spaced in a logarithmic scale between $10^{-7}$ and $10^{-2}$.
+For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
+shown in Fig.~\ref{fig:crust1-results}d as function of $\mu$.
+The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
+(indicated by the red triangle).
+
+In the second cross-validation,
+we use the estimated value of $\mu$ in all inversions.
+We test 7 values of $z_{ref}$ from 20 to 35 km with 2.5 km intervals
+and 7 values of $\Delta\rho$ from 200 to 500 $kg/m^3$
+with 50 $kg/m^3$ intervals.
+We run the inversion for each combination of $z_{ref}$ and $\Delta\rho$,
+totaling 49 inversions.
+Finally, we calculate the Mean Square Error (Eq.~\ref{eq:msehyper})
+for each of the 49 estimates
+and choose the values of $z_{ref}$ and $\Delta\rho$ that minimize the MSE.
+Fig.~\ref{fig:crust1-results}h
+shows a colored-contour map of the MSE
+with a minimum (marked by the red triangle)
+at $z_{ref} = 30\ km$ and $\Delta\rho = 350\ kg/m^3$.
 

### 2016-02-23 manuscript/manuscript.tex
Reverse order of crust1 results figure to match text
The order in which I talked about the results didn't match the order
they were presented in the figure. So moved the 4 graphs to the left.

@@
 For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
-shown in Fig.~\ref{fig:crust1-results}d as function of $\mu$.
+shown in Fig.~\ref{fig:crust1-results}a as function of $\mu$.
 The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
@@
 and choose the values of $z_{ref}$ and $\Delta\rho$ that minimize the MSE.
-Fig.~\ref{fig:crust1-results}h
+Fig.~\ref{fig:crust1-results}b
 shows a colored-contour map of the MSE
@@
 at $z_{ref} = 30\ km$ and $\Delta\rho = 350\ kg/m^3$.
+
+Fig.~\ref{fig:crust1-results}c shows the final solution after both
+cross-validation procedures.
 
@@
         Inversion results from the CRUST1.0 synthetic data.
-        (a) The estimated Moho depth.
-        (b) The inversion residuals (observed minus predicted data).
-        (c) Histogram of the residuals shown in (b).
-        (d) Cross-validation curve used to determine
+        (a) Cross-validation curve used to determine
         the regularization parameter (Eq.~\ref{eq:goalfunction}).
@@
         $\mu = 0.0001$ (red triangle).
-        (e) difference between the CRUST1.0 model depths
-        (Fig.~\ref{fig:crust1-data}a)
-        and the estimated depths.
-        (f) Difference between the synthetic seismic observations
-        (Fig.~\ref{fig:crust1-data}c)
-        and the estimated depths.
-        (g) Histogram of the differences shown in (f).
-        (h) Cross-validation results used to determine
+        (b) Cross-validation results used to determine
         the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
@@
         and $\Delta\rho = 350\ kg/m^3$.
+        (c) The estimated Moho depth.
+        (d) Difference between the CRUST1.0 model depths
+        (Fig.~\ref{fig:crust1-data}a)
+        and the estimated depths.
+        (e) Histogram of the differences shown in (d).
+        (f) Histogram of the inversion residuals
+        (observed minus predicted data).
+        (g) The inversion residuals.
+        (h) Difference between the synthetic seismic observations
+        (Fig.~\ref{fig:crust1-data}c)
+        and the estimated depths.
     }

### 2016-02-24 manuscript/manuscript.tex
Put residuals histogram before seismic diff
In CRUST1 synthetic results figure.

@@
 The recovered model is smooth, indicating that the cross-validation procedure
-was effective at estimating an optimal regularization parameter.
+was effective in estimating an optimal regularization parameter.
 Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
@@
 cross-validation procedures.
+The recovered model is smooth, indicating that the cross-validation procedure
+was effective in estimating an optimal regularization parameter.
+Fig.~\ref{fig:crust1-results}d shows the difference between
+the true Moho depth shown in Fig.~\ref{fig:crust1-data}a
+and the estimate.
+The maximum and minimum differences are, respectively,
+9.8 and -8.2 km.
 
@@
         and the estimated depths.
-        (e) Histogram of the differences shown in (d).
-        (f) Histogram of the inversion residuals
+        (e) Histogram of the inversion residuals
         (observed minus predicted data).
+        (f) Histogram of the differences between
+        the synthetic seismic observations (Fig.~\ref{fig:crust1-data}c)
+        and the estimated depths.
         (g) The inversion residuals.
-        (h) Difference between the synthetic seismic observations
-        (Fig.~\ref{fig:crust1-data}c)
-        and the estimated depths.
+        (h) Difference between the seismic and the estimated depths.
     }

### 2016-02-24 manuscript/manuscript.tex
More text about the differences and residuals in CRUST1

@@
 9.8 and -8.2 km.
+The largest absolute differences are located along the central and northern
+Andes, where there is a sharp increase in the true Moho depth.
+Positive differences (indicating a too shallow estimate)
+appear along the central portion of the Andes,
+flanked by regions of negative differences (indicating a too deep estimate)
+on the continental and Pacific sides.
+Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
+between the observed and predicted data).
+The inversion residuals appear normally distributed,
+with 0.03 mGal mean and a standard deviation of 4.10 mGal.
+The residuals follow the same pattern as the differences shown in
+Fig.~\ref{fig:crust1-results}d,
+with the largest residuals (in absolute value) along the Andes.
+The pattern of the residuals is inverted, though,
+with the central portion being dominated by negative residuals
+and flanked by positive residuals on both sides.
 

### 2016-02-24 manuscript/manuscript.tex
Finish first draft of CRUST1 synthetic results
Fixes #5

@@
-%\documentclass[]{article}
-%\usepackage{natbib}
-% \documentclass[extra,mreferee]{gji}
-\documentclass[extra]{gji}
+\documentclass[extra,mreferee]{gji}
+%\documentclass[extra]{gji}
 \usepackage{timet}
@@
 and flanked by positive residuals on both sides.
+Figs.~\ref{fig:crust1-results}f and h show the differences between
+the synthetic seismic data (Fig.~\ref{fig:crust1-data}c)
+and the estimated Moho depths.
+Once more, the largest differences are concentrated along the Andes,
+particularly in the central Andes and near Ecuador and Colombia.
+The differences are smaller along the Atlantic coast of South America,
+with notable larger differences in a few points of northeastern Brazil
+and along the Amazon river.
 

### 2016-02-26 manuscript/manuscript.tex
Paragraph about hyperparameter estimation

@@
 \usepackage[utf8]{inputenc}
-
+% To make two column figures appear in the correct order
+\usepackage{fixltx2e}
+% To make annotations on the sides
 \usepackage{todonotes}
@@
 % Document metadata
-% =================
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\Title}{
@@
 \newcommand{\Keywords}{
-        Moho;
-        gravity inversion;
-        spherical coordinates;
-        tesseroid;
-        South America
+    Inverse theory;
+    Gravity anomalies and Earth structure;
+    Satellite gravity;
+    South America;
 }
@@
 }
-
+% Metadata for the generated PDF
 \usepackage[pdftex,colorlinks=true]{hyperref}
@@
 
-%\label{firstpage}
+\label{firstpage}
 \maketitle
@@
 \section{Introduction}
+
+The Mohorovičić discontinuity (or Moho) that marks the transition from the
+crust to the mantle, is studied almost exclusively through indirect geophysical
+methods.
+The two main methods used to estimate the depth of the Moho are seismology,
+with both natural and controlled sources, and gravimetry.
+With the advent of satellite gravimetry missions like GRACE and GOCE,
+gravity derived crustal models can be produced in regional or global scales
+\citep[e.g. ][]{reguzzoni2013,vandermeijde2013,vandermeijde2015}.
+New spherical harmonic gravity models that use these satellite observation,
+like GOCO5S \citep{mayer-guerr2015}, provide almost homogeneous data coverage
+in difficult to access regions traditionally poor in terrestrial data.
+An example is South America, where seismologic and terrestrial gravity data
+are traditionally concentrated around large urban centers and coastal areas.
+
+Estimating Moho depth from gravity data is a non-linear inverse problem.
+One can generalize this problem to estimating the relief of an interface,
+such as the basement of a sedimentary basin or the relief of the anomalous
+Moho.
+Several methods have been developed over the years to solve this inverse
+problem, for example
+\citet{bott1960, barbosa1999b, barbosa1999a, barnes2012, leao1996, martins2010,
+martins2011, oldenburg1974, reguzzoni2013, santos2015, silva2006, silva2014},
+to name a few.
+Solving the inverse problem is computationally demanding because it requires
+the construction of large dense matrices and the solution of large linear
+systems.
+As a result, some authors search for ways to increase the computational
+efficiency of this class of inverse problem.
+\citet{bott1960} proposed a method based on iteratively applying corrections to
+a starting estimate based on the inversion residuals.
+The algorithm is fast because it bypasses the construction and solution of
+linear systems and only involves forward modeling.
+\citet{oldenburg1974} showed that the fast FFT-based forward modeling of
+\citet{parker1973} could be rearranged to estimate the relief.
+\citet{barnes2012} use a form of adaptive discretization to compute the
+Jacobian, or sensitivity, matrix.
+For each data point, the discretization will be progressively coarser
+the further way from the point.
+This reduces the matrix and, consequently, the linear systems to a sparse form
+that can be solved efficiently.
+Recently, \citet{silva2014} extended and generalized the original method of
+\citet{bott1960} and \citet{santos2015} used this extension to estimate a
+basement relief with sharp boundaries.
+
+Most non-linear gravity inversion methods discretize the relief of the
+interface into juxtaposed right-rectangular prisms with a known density
+contrast.
+The inverse problem is then to estimate the thickness of each prism from the
+gravity data.
+The use of rectangular prisms implies a planar Earth approximation and may not
+be adequate for continental and global scale studies.
+In such cases, a spherical Earth approximation is preferred.
+\citet{wieczorek1998} developed a spherical harmonic equivalent of the
+Parker-Oldenburg FFT algorithm and applied it to estimate the crustal structure
+of the Moon.
+\citet{reguzzoni2013} use a spherical approximation to estimate the global
+Moho relief from GOCE satellite gravity data.
+Conversely, one could adapt one of the methods developed for
+right-rectangular prisms to use tesseroids (spherical prisms) instead.
+One of the difficulties of this approach is that the forward problem for a
+tesseroid must be solved numerically.
+Two alternatives proposed in the literature to the numerical solution are
+Taylor series expansion \citep{heck2007, grombein2013}
+and the Gauss-Legendre Quadrature
+\citep{asgharzadeh2007}.
+Numerical experiments by \citet{wild-pfeiffer2008} suggest that the
+Gauss-Legendre Quadrature (GLQ) offers superior results.
+However, the GLQ suffers from numerical instability when the computation point
+is close to the tesseroid \citep{asgharzadeh2007}.
+To overcome the numerical instability, \citet{li2011} proposed an adaptive
+discretization algorithm which was later improved upon by \citet{uieda2016}.
+
+In any gravity inversion for the relief of an interface, two hyper-parameters
+control the inversion results: the density-contrast between the two mediums
+and the reference level around which the interface undulates.
+The reference level is the depth of the Normal Earth Moho in the case of the
+anomalous Moho.
+For regularized inversions, an additional hyper-parameter is the regularization
+parameter that balances data-misfit and regularization.
+The two most commonly used methods for estimating the regularization parameter
+are the L-curve criterion and Generalized Cross Validation (GCV).
+\citet{farquharson2004} provide for a thorough comparison of both methods.
+Estimating the density-contrast in a sedimentary basin context has been tackled
+by \citet{silva2006} and \citet{martins2010} when the basement depth is known
+at a few points.
+To the authors knowledge no attempt has been made to estimate the reference
+level.
 
@@
 $\gamma(P)$ is calculated using
-the closed-form solution presented by \citet{li2001}.
+the closed-form solution presented by \citet{li2001a}.
 The difference between the observed gravity at point P ($g(P)$)
@@
 of the computation time of a single inversion
-(see section~\ref{sec:simple-synthetic} and table~\ref{profiling}).
+(see section~\ref{sec:simple-synthetic} and Table~\ref{profiling}).
 Hence, by employing the use of sparse matrices,
@@
 \subsection{Estimating the regularization parameter}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/cv-grid-separation}
+    \caption{Sketch of a data grid separated into
+        the training (white dots with black outlines)
+        and testing (black dots) data sets.
+        The training data set is still displayed on a regular grid
+        but with twice the grid spacing
+        of the original data grid.}
+    \label{fig:grid_separation}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/cv-grid-separation}
-    \caption{Sketch of a data grid separated into
-        the training (white dots with black outlines)
-        and testing (black dots) data sets.
-        The training data set is still displayed on a regular grid
-        but with twice the grid spacing
-        of the original data grid.}
-    \label{fig:grid_separation}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{enumerate}
-    \item For each combination of
+    \item For every combination of
         $z_{ref,l} \in [z_{ref,1},z_{ref,2},\ldots,z_{ref,N_z}]$ and
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Software implementation}
+\subsection{Software implementation}\label{sec:software}
 
@@
 for plots and maps,
-and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
+and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013a}
 for geophysics specific tasks,
@@
 
-All source code, data, and Jupyter notebooks
+All source code, Jupyter notebooks, data, and results
 can be found at the online repository
@@
 \url{http://dx.doi.org/...}
-(\textbf{Note to reviewers: the archived version will be uploaded only upon
+(\textbf{Note to reviewers: the archived version will be uploaded upon
 publication}).
@@
 \subsection{Simple model}\label{sec:simple-synthetic}
-
-We simulate the transition from a continental-type Moho to an oceanic-type Moho
-using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
-juxtaposed tesseroids (a total of $M = 2000$ model elements).
-The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
-and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
-Fig.~\ref{fig:simple-data}a shows the model Moho depths,
-where each pixel in the pseudo-color image corresponds to
-a tesseroid of the model.
-
-The synthetic data were forward modeled on a regular grid of
-$N_{lat} \times N_{lon} = 79 \times 99$ points
-(a total of $N = 7821$ observations)
-at a constant height of 50 km.
-The data were contaminated with pseudo-random noise
-sampled from a normal distribution with zero mean and 5 mGal standard deviation.
-Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set.
-The data grid spacing is half the grid spacing of the tesseroid model
-so that, when separating the training and testing data sets
-(Fig.~\ref{fig:grid_separation}),
-the training data set points will fall directly above each model element.
-
-We separated the synthetic data into training and testing data sets
-following Fig.~\ref{fig:grid_separation}.
-The training data set is a regular grid of
-$N_{lat} \times N_{lon} = 40 \times 50$ points
-(a total of $N_{train} = 2000$).
-The testing data set is composed of $N_{test} = 5821$ observations.
-We used cross-validation to estimate an optimal regularization parameter ($\mu$)
-from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
-between $10^{-6}$ and $10^{-1}$.
-We ran our regularized inversion on the training data set
-for each value of $\mu$,
-obtaining 16 Moho depth estimates.
-For all inversions, the initial Moho depth estimate
-used to start the Gauss-Newton optimization
-was set to 60 km depth for all inversion parameters.
-Furthermore, $z_{ref}$ and $\Delta\rho$ are set to their respective true values.
-Finally, we computed the mean square error (MSE, Eq.~\ref{eq:msemu})
-for each estimate and chose as the final estimated Moho model
-the one that minimizes the MSE.
-
-Fig.~\ref{fig:simple-results} summarizes the inversion results.
-Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
-after cross-validation.
-The recovered model is smooth, indicating that the cross-validation procedure
-was effective in estimating an optimal regularization parameter.
-Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
-(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
-The differences appear to be semi-randomly distributed with a maximum
-coinciding with a short-wavelength feature in the true model.
-The maximum and minimum differences are approximately
-2.19 and -2.13 km, respectively.
-Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
-the observed and predicted data), in mGal.
-The largest residual (in absolute value) coincides with the largest difference
-between the true model and the estimate.
-The inversion residuals are normally distributed,
-as shown in Fig.~\ref{fig:simple-results}d,
-with 0.02 mGal mean and a standard deviation of 3.63 mGal.
-The cross-validation curve in Fig.~\ref{fig:simple-results}e
-shows a clear minimum MSE at $\mu = 0.00046$
-(indicated by the red triangle).
-Fig.~\ref{fig:simple-results}f shows the convergence of
-the Gauss-Newton optimization in eight iterations.
-
-We also investigated the computation time spent in each section of the inversion
-process using a source code profiler.
-The profiler measures how much time is spent inside each function during
-the execution of a program.
-We ran the profiler on a single inversion of the training data set
-using the estimated regularization parameter.
-We tracked the total time spent inside each of the three functions
-that represent the largest computational bottlenecks of the inversion:
-solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
-using the conjugate gradient method,
-performing the dot products required to compute
-the Hessian matrix (Eq.~\ref{eq:hessian-regul})
-and the gradient vector (Eq.~\ref{eq:gradient-regul}),
-and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
-The profiling results presented in table~\ref{profiling}
-show that the time spent on forward modeling accounts for approximately
-99.8\% of the total computation time.
-
-\input{profiling.tex}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Model based on CRUST1.0}
-
-In this test, we simulate the anomalous Moho of South America
-using Moho depth information extracted from the CRUST1.0 model
-\citep{laske2013}.
-We construct a tesseroid model with
-$M_{lat} \times M_{lon} = 80 \times 60$ juxtaposed elements, 4800 in total,
-using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
-In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
-the density-contrast is $\Delta\rho = 350\ kg/m^3$.
-We produce the synthetic data at a constant height of 50 km
-and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
-(a total of 18921 observations).
-We contaminate the synthetic data with normally distributed pseudo-random noise
-with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).
-
-The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
-requires knowledge of the Moho depth at certain points
-($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
-usually from seismic experiments.
-Thus, we must also generate synthetic seismic data about the Moho depth.
-We produce such data by interpolating the Moho depth shown in
-Fig.~\ref{fig:crust1-data}a on the same geographic coordinates
-as the 937 points from the \citet{assumpcao2012} data set.
-The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
-
-We perform the cross-validation procedures in two parts.
-First, we run the cross-validation to estimate
-an optimal regularization parameter ($\mu$).
-The starting estimate for all inversions is
-60 km depth for all model parameters.
-For this cross-validation,
-we keep $z_{ref}$ and $\Delta\rho$ fixed to
-$20\ km$ and $500\ kg/m^3$, respectively.
-Our investigations suggest that the outcome of this round of cross-validation
-does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
-Second, we use the estimated $\mu$ to run the cross-validation
-to estimate $z_{ref}$ and $\Delta\rho$,
-thus obtaining the final estimated Moho depths.
-Fig.~\ref{fig:crust1-results} summarizes the final results.
-
-For the first cross-validation,
-we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
-a training set with half the grid spacing of the original data
-($N_{lat} \times N_{lon} = 80 \times 60$)
-and a testing set with 14,121 observations.
-We run the inversion for 16 different values of $\mu$,
-equally spaced in a logarithmic scale between $10^{-7}$ and $10^{-2}$.
-For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
-shown in Fig.~\ref{fig:crust1-results}a as function of $\mu$.
-The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
-(indicated by the red triangle).
-
-In the second cross-validation,
-we use the estimated value of $\mu$ in all inversions.
-We test 7 values of $z_{ref}$ from 20 to 35 km with 2.5 km intervals
-and 7 values of $\Delta\rho$ from 200 to 500 $kg/m^3$
-with 50 $kg/m^3$ intervals.
-We run the inversion for each combination of $z_{ref}$ and $\Delta\rho$,
-totaling 49 inversions.
-Finally, we calculate the Mean Square Error (Eq.~\ref{eq:msehyper})
-for each of the 49 estimates
-and choose the values of $z_{ref}$ and $\Delta\rho$ that minimize the MSE.
-Fig.~\ref{fig:crust1-results}b
-shows a colored-contour map of the MSE
-with a minimum (marked by the red triangle)
-at $z_{ref} = 30\ km$ and $\Delta\rho = 350\ kg/m^3$.
-
-Fig.~\ref{fig:crust1-results}c shows the final solution after both
-cross-validation procedures.
+We simulate the transition from a continental-type Moho to an oceanic-type Moho
+using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
+juxtaposed tesseroids (a total of $M = 2000$ model elements).
+The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
+and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
+Fig.~\ref{fig:simple-data}a shows the model Moho depths,
+where each pixel in the pseudo-color image corresponds to
+a tesseroid of the model.
+
+The synthetic data were forward modeled on a regular grid of
+$N_{lat} \times N_{lon} = 79 \times 99$ points
+(a total of $N = 7821$ observations)
+at a constant height of 50 km.
+The data were contaminated with pseudo-random noise
+sampled from a normal distribution with zero mean and 5 mGal standard deviation.
+Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set.
+The data grid spacing is half the grid spacing of the tesseroid model
+so that, when separating the training and testing data sets
+(Fig.~\ref{fig:grid_separation}),
+the training data set points will fall directly above each model element.
+
+We separated the synthetic data into training and testing data sets
+following Fig.~\ref{fig:grid_separation}.
+The training data set is a regular grid of
+$N_{lat} \times N_{lon} = 40 \times 50$ points
+(a total of $N_{train} = 2000$).
+The testing data set is composed of $N_{test} = 5821$ observations.
+We used cross-validation to estimate an optimal regularization parameter ($\mu$)
+from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
+between $10^{-6}$ and $10^{-1}$.
+We ran our regularized inversion on the training data set
+for each value of $\mu$,
+obtaining 16 Moho depth estimates.
+For all inversions, the initial Moho depth estimate
+used to start the Gauss-Newton optimization
+was set to 60 km depth for all inversion parameters.
+Furthermore, $z_{ref}$ and $\Delta\rho$ are set to their respective true values.
+Finally, we computed the mean square error (MSE, Eq.~\ref{eq:msemu})
+for each estimate and chose as the final estimated Moho model
+the one that minimizes the MSE.
+
+Fig.~\ref{fig:simple-results} summarizes the inversion results.
+Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
+after cross-validation.
 The recovered model is smooth, indicating that the cross-validation procedure
 was effective in estimating an optimal regularization parameter.
-Fig.~\ref{fig:crust1-results}d shows the difference between
-the true Moho depth shown in Fig.~\ref{fig:crust1-data}a
-and the estimate.
-The maximum and minimum differences are, respectively,
-9.8 and -8.2 km.
-The largest absolute differences are located along the central and northern
-Andes, where there is a sharp increase in the true Moho depth.
-Positive differences (indicating a too shallow estimate)
-appear along the central portion of the Andes,
-flanked by regions of negative differences (indicating a too deep estimate)
-on the continental and Pacific sides.
-Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
-between the observed and predicted data).
-The inversion residuals appear normally distributed,
-with 0.03 mGal mean and a standard deviation of 4.10 mGal.
-The residuals follow the same pattern as the differences shown in
-Fig.~\ref{fig:crust1-results}d,
-with the largest residuals (in absolute value) along the Andes.
-The pattern of the residuals is inverted, though,
-with the central portion being dominated by negative residuals
-and flanked by positive residuals on both sides.
-Figs.~\ref{fig:crust1-results}f and h show the differences between
-the synthetic seismic data (Fig.~\ref{fig:crust1-data}c)
-and the estimated Moho depths.
-Once more, the largest differences are concentrated along the Andes,
-particularly in the central Andes and near Ecuador and Colombia.
-The differences are smaller along the Atlantic coast of South America,
-with notable larger differences in a few points of northeastern Brazil
-and along the Amazon river.
+Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
+(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
+The differences appear to be semi-randomly distributed with a maximum
+coinciding with a short-wavelength feature in the true model.
+The maximum and minimum differences are approximately
+2.19 and -2.13 km, respectively.
+Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
+the observed and predicted data), in mGal.
+The largest residual (in absolute value) coincides with the largest difference
+between the true model and the estimate.
+The inversion residuals are normally distributed,
+as shown in Fig.~\ref{fig:simple-results}d,
+with 0.02 mGal mean and a standard deviation of 3.63 mGal.
+The cross-validation curve in Fig.~\ref{fig:simple-results}e
+shows a clear minimum MSE at $\mu = 0.00046$
+(indicated by the red triangle).
+Fig.~\ref{fig:simple-results}f shows the convergence of
+the Gauss-Newton optimization in eight iterations.
+
+We also investigated the computation time spent in each section of the inversion
+process using a source code profiler.
+The profiler measures how much time is spent inside each function during
+the execution of a program.
+We ran the profiler on a single inversion of the training data set
+using the estimated regularization parameter.
+We tracked the total time spent inside each of the three functions
+that represent the largest computational bottlenecks of the inversion:
+solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
+using the conjugate gradient method,
+performing the dot products required to compute
+the Hessian matrix (Eq.~\ref{eq:hessian-regul})
+and the gradient vector (Eq.~\ref{eq:gradient-regul}),
+and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
+The profiling results presented in Table~\ref{profiling}
+show that the time spent on forward modeling accounts for approximately
+99.8\% of the total computation time.
+
+% Insert the profiling results table
+\input{profiling.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Model based on CRUST1.0}\label{sec:crust1}
 
@@
 
+In this test, we simulate the anomalous Moho of South America
+using Moho depth information extracted from the CRUST1.0 model
+\citep{laske2013}.
+We construct a tesseroid model with
+$M_{lat} \times M_{lon} = 80 \times 60$ juxtaposed elements, 4800 in total,
+using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
+In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
+the density-contrast is $\Delta\rho = 350\ kg/m^3$.
+We produce the synthetic data at a constant height of 50 km
+and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
+(a total of 18921 observations).
+We contaminate the synthetic data with normally distributed pseudo-random noise
+with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).
+
+The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
+requires knowledge of the Moho depth at certain points
+($\mathbf{z}_s^o$ in Eq.~\ref{eq:msehyper}),
+usually from seismic experiments.
+Thus, we must also generate synthetic seismic data about the Moho depth.
+We produce such data by interpolating the Moho depth shown in
+Fig.~\ref{fig:crust1-data}a on the same geographic coordinates
+as the 937 points from the \citet{assumpcao2013a} data set.
+The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
+
+We perform the cross-validation procedures in two parts.
+First, we run the cross-validation to estimate
+an optimal regularization parameter ($\mu$).
+The starting estimate for all inversions is
+60 km depth for all model parameters.
+For this cross-validation,
+we keep $z_{ref}$ and $\Delta\rho$ fixed to
+$20\ km$ and $500\ kg/m^3$, respectively.
+Our investigations suggest that the outcome of this round of cross-validation
+does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
+Second, we use the estimated $\mu$ to run the cross-validation
+to estimate $z_{ref}$ and $\Delta\rho$,
+thus obtaining the final estimated Moho depths.
+Fig.~\ref{fig:crust1-results} summarizes the results
+from both cross-validation runs and the final inversion results.
+
+For the first cross-validation,
+we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
+a training set with twice the grid spacing of the original data
+($N_{lat} \times N_{lon} = 80 \times 60$)
+and a testing set with 14,121 observations.
+We run the inversion for 16 different values of $\mu$
+equally spaced in a logarithmic scale between $10^{-7}$ and $10^{-2}$.
+For each of the 16 estimates we compute the MSE (Eq.~\ref{eq:msemu}),
+shown in Fig.~\ref{fig:crust1-results}a as function of $\mu$.
+The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
+(indicated by the red triangle).
+
+In the second cross-validation,
+we use the estimated value of $\mu$ in all inversions.
+We test seven values of $z_{ref}$ from 20 to 35 km with 2.5 km intervals
+and seven values of $\Delta\rho$ from 200 to 500 $kg/m^3$
+with 50 $kg/m^3$ intervals.
+We run the inversion for every combination of $z_{ref}$ and $\Delta\rho$,
+totaling 49 inversions.
+Finally, we calculate the Mean Square Error (Eq.~\ref{eq:msehyper})
+for each of the 49 estimates
+and choose the values of $z_{ref}$ and $\Delta\rho$ that minimize the MSE.
+Fig.~\ref{fig:crust1-results}b
+shows a colored-contour map of the MSE
+with a minimum (marked by the red triangle)
+at $z_{ref} = 30\ km$ and $\Delta\rho = 350\ kg/m^3$.
+
+Fig.~\ref{fig:crust1-results}c shows the final solution after both
+cross-validation procedures.
+The recovered model is smooth, indicating that the cross-validation procedure
+was effective in estimating an optimal regularization parameter.
+Fig.~\ref{fig:crust1-results}d shows the difference between
+the true Moho depths (Fig.~\ref{fig:crust1-data}a)
+and the estimated depths.
+The maximum and minimum differences are, respectively,
+9.8 and -8.2 km.
+The largest absolute differences are located along the central and northern
+Andes, where there is a sharp increase in the true Moho depth
+(Fig.~\ref{fig:crust1-data}a).
+Positive differences (indicating a too shallow estimate)
+appear along the central portion of the Andes,
+flanked by regions of negative differences (indicating a too deep estimate)
+on the continental and Pacific sides.
+Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
+between the observed and predicted data).
+The inversion residuals appear normally distributed,
+with 0.03 mGal mean and a standard deviation of 4.10 mGal.
+The residuals follow a similar, though reversed, pattern
+to the differences shown in Fig.~\ref{fig:crust1-results}d.
+The largest residuals (in absolute value) are along the Andes,
+with the central portion being dominated by negative residuals
+and flanked by positive residuals on both sides.
+Figs.~\ref{fig:crust1-results}f and h show the differences between
+the synthetic seismic data (Fig.~\ref{fig:crust1-data}c)
+and the estimated Moho depths.
+Once more, the largest differences are concentrated along the Andes,
+particularly in the central Andes and near Ecuador and Colombia.
+The differences are smaller along the Atlantic coast of South America,
+with notable larger differences in a few points of northeastern Brazil
+and along the Amazon river.
+In general, large residuals are associated with sharp increases in Moho depth.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+We apply the inversion method proposed here to invert for the Moho depth of the
+South American continent.
+We follow the application of \citet{vandermeijde2013} but with some
+differences, mainly using a different data set and performing all modeling
+in spherical coordinates using tesseroids.
+The data are corrected of the effects of topography and sedimentary basins.
+Crust and mantle heterogeneities cannot be properly accounted for
+in regions where information coverage is sparse and readily accessible models
+are not available, like in South America and Africa.
+Hence, for the purposes of this study, we will assume to be negligible all
+other crustal and mantle sources, including lateral variations in density along
+the Moho.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Gravity and seismic data}
-
-The gravitational effect of the topography
-is removed using the
-ETOPO1 digital terrain model
-\citep[][ \url{http://dx.doi.org/10.7289/V5C8276M}]{amante2009}.
-The effect of sedimentary basins is removed using the
-CRUST1.0 model
-\citep[][ \url{http://igppweb.ucsd.edu/~gabi/rem.html}]{laske2013}.
-Lateral variations in density along the Moho cannot be properly accounted for
-in regions where information coverage is sparse and readily accessible models
-are not available, like in the South American and African continents.
-For the purposes of this study, we will assume that all other crustal sources
-and lateral variations in density are negligible.
 
@@
         corrections.
-        (a) Topography from ETOPO1 sampled at $0.1^\circ$ grid spacing.
-        (b) Gravitational attraction of the topography calculated
+        (a) The gravity disturbance (Eq.~\ref{eq:disturbance}) calculated from
+        the raw gravity data.
+        (b) Topography from ETOPO1.
+        (c) Gravitational attraction of the topography calculated
         at the observation height using tesseroids.
-        (c) The gravity disturbance (Eq.~\ref{eq:disturbance}) calculated from
-        the raw gravity data.
         (d) The Bouguer disturbance (Eq.~\ref{eq:bouguer}) obtained by
-        subtracting (b) from (c).
+        subtracting (c) from (a).
         The upper (e), middle (f), and lower (g) sediment layer thicknesses
@@
         (b) Seismological Moho depth estimates from
-        \citet{assumpcao2012}.
+        \citet{assumpcao2013a}.
     }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inversion results}
-
-Bla bla bla.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/south-america-moho}
-    \caption{
-        Inversion results for the South American Moho.
-        (a) The estimated Moho depth of South America.
-        (b) Differences between the seismological depths of
-        \citet{assumpcao2012} and our gravity-derived estimate shown in (a).
-        The inset in (b) shows a histogram of the differences along with their
-        calculated mean and standard deviation (std).
-    }
-    \label{fig:sam-moho}
-\end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/south-america-residuals}
-    \caption{
-        Residuals for the South American Moho inversion.
-        The residuals are the observed data in Fig.~\ref{fig:sam-data}a
-        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a.
-        Shown as (a) a map and (b) a histogram with the calculated mean and
-        standard deviation.
-        (c) The value of the goal function (Eq.~\ref{eq:goalfunction})
-        per Gauss-Newton iteration showing the convergence of the algorithm.
-        Note that the y-axis is in logarithmic scale.
-    }
-    \label{fig:sam-residuals}
-\end{figure}
+The raw gravity data are generated from the satellite only
+spherical harmonic model GOCO5S \citet{mayer-guerr2015}.
+The GOCO5S model combines data from 15 satellites, including the complete
+mission data from the GOCE satellite.
+The data were downloaded from the
+International Centre for Global Earth Models (ICGEM) web-service
+\citep[][ \url{http://icgem.gfz-potsdam.de/ICGEM/})]{barthelmes2012}
+in the form of the complete gravity field
+on a regular grid with $0.2^\circ$ grid spacing at ellipsoidal height 50 km.
+We calculate the gravity disturbance
+($\delta(P)$ in Eq.~\ref{eq:disturbance})
+by subtracting from the raw data
+the normal gravity of the WGS84 reference ellipsoid ($\gamma(P)$)
+using the formula of \citet{li2001a}.
+Fig.~\ref{fig:sam-corrections}a show the calculated gravity disturbance of
+South America.
+
+We remove the gravitational effect of the topography
+from the gravity disturbance
+by modeling the ETOPO1 digital terrain model
+\citep[][ \url{http://dx.doi.org/10.7289/V5C8276M}]{amante2009}
+using tesseroids (Fig.~\ref{fig:sam-corrections}b).
+We used the standard densities of $2670\ kg/m^3$ for continents and
+$-1630\ kg/m^3$ for the oceans.
+Fig.~\ref{fig:sam-corrections}c shows the calculated gravitational attraction
+of the topographic masses at 50 km height.
+Fig.~\ref{fig:sam-corrections}d shows the Bouguer disturbance
+(Eq.~\ref{eq:bouguer}) obtained after subtracting the topographic effect from
+the gravity disturbance.
+
+The effect of sedimentary basins is removed using
+tesseroid models of the three sedimentary layers present in the CRUST1.0 model
+\citep[][ \url{http://igppweb.ucsd.edu/~gabi/rem.html}]{laske2013}.
+Each sedimentary layer model includes the density
+of each $1^\circ \times 1^\circ$ model cell.
+Figs.~\ref{fig:sam-corrections}e-g show the thickness of the upper, middle, and
+lower sedimentary layers, respectively.
+The density-contrasts of the tesseroid model is obtained by subtracting
+$2670\ kg/m^3$ from the density of each model element.
+Fig.~\ref{fig:sam-corrections}h shows the combined gravitational attraction of
+the sedimentary basin tesseroid model.
+We subtract the total effect of sediments from the Bouguer disturbance in
+Fig.~\ref{fig:sam-corrections}d to obtain
+the sediment-free Bouguer disturbance (Fig.~\ref{fig:sam-data}a),
+which will be used as input for the inversion.
+
+The seismic point estimates of Moho depth used in the cross-validation
+procedure are from the data set of \citet{assumpcao2013a}.
+The 937 data points in this data set are shown in Fig.~\ref{fig:sam-data}b.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Inversion and cross-validation}
 
@@
 
+As in the CRUST1.0 synthetic data test (section~\ref{sec:crust1}),
+we perform the cross-validation in two parts.
+First, we run the cross-validation to estimate
+an optimal regularization parameter ($\mu$).
+The starting estimate for all inversions is
+60 km depth for all model parameters.
+For this cross-validation,
+we keep $z_{ref}$ and $\Delta\rho$ fixed to
+$20\ km$ and $500\ kg/m^3$, respectively.
+Second, we use the estimated $\mu$ to run the cross-validation
+to estimate $z_{ref}$ and $\Delta\rho$,
+thus obtaining the final estimated Moho depth model.
+
+We split the sediment-free gravity data into the training and testing data
+sets.
+The training data set is a regular grid with $0.4^\circ$ grid spacing
+(twice the spacing of the original data grid)
+and $N_{lat} \times N_{lon} = 201 \times 151$ grid points,
+a total of 30,351 observations.
+The remaining 90,350 points compose the testing data set.
+We test 16 values of the regularization parameter ($\mu$)
+equally spaced on a logarithmic scale between $10^{-10}$ and $10^{-2}$.
+Fig.~\ref{fig:sam-cv}a shows the Mean Square Error (MSE)
+as a function of $\mu$.
+The minimum MSE is found at $\mu = 10^{-10}$, the lowest value of $\mu$ tested,
+suggesting that little or no regularization is required.
+
+We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
+inversions.
+We test all combinations of
+seven values of $z_{ref}$, from 20 to 35 km with 2.5 km intervals,
+and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
+with 50 $kg/m^3$ intervals.
+Fig.~\ref{fig:sam-cv}b shows a map of the MSE
+with respect to the \citet{assumpcao2013a} data set.
+The MSE has a well defined minimum, indicated by the red triangle,
+at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Moho model for South America}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/south-america-moho}
+    \caption{
+        Inversion results for the South American Moho.
+        (a) The estimated Moho depth of South America.
+        The solid light grey line is the 35 km Moho depth contour.
+        (b) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
+        minus the data predicted by the estimate (a)).
+        (c) Differences between the seismological depths of
+        \citet{assumpcao2013a} and our gravity-derived estimate shown in (a).
+        The inset in (c) shows a histogram of the differences along with their
+        calculated mean and standard deviation (std).
+    }
+    \label{fig:sam-moho}
+\end{figure*}
+
+The final Moho depth model for South America is shown
+as a pseudo-color map in Fig.~\ref{fig:sam-moho}a.
+The model is available in the online repository that accompanies
+this contribution (see section~\ref{sec:software}).
+Each model element is a $0.4^\circ \times 0.4^\circ$ tesseroid,
+represented by the pixels in the pseudo-color map.
+
+Our model differs significantly from CRUST1.0 (Fig.~\ref{fig:crust1-data}a)
+but contains most of the large-scale features
+present in the GMSA12 gravity-derived model of \citet{vandermeijde2013}.
+The deepest Moho is along the central Andes, reaching depths upward of 70 km.
+The oceanic areas present the shallowest Moho, ranging approximately
+from 7.5 to 20 km.
+The Brazilian and Guiana shields have a deeper Moho (greater than 35 km),
+with the deepest portion in the area of the São Francisco craton.
+The Moho is shallower than 35 km along the western Amazon and Andean foreland
+regions, as well as along the Amazon river.
+
+Fig.~\ref{fig:sam-moho}b shows the inversion residuals
+(observed minus predicted data)
+and Fig.~\ref{fig:sam-moho}c shows the differences between
+the seismic-derived depths of \citet{assumpcao2013a}
+(Fig.~\ref{fig:sam-data}b) and the depths in our model.
+The differences range from approximately -23 to 23 km
+and have a mean of 1.18 km and a standard deviation of 6.84 km.
+The residuals and differences from seismic are smallest in the oceanic areas,
+southern Patagonia, and the eastern coast of the continent.
+The largest residuals are located along the Andes and correlate with the
+deepest Moho depths.
+These large residuals follow a pattern of a negative value in the center
+flanked by positive values to the East and West.
+This same pattern is observed in the CRUST1.0 synthetic test results
+(Fig.~\ref{fig:crust1-results}),
+suggesting that this is a byproduct of the inversion method, not the data.
+Likewise, larger residuals also appear to be associated with sharp variations
+in the estimated Moho depth.
+Along the Andes, large differences with seismic data are correlated with the
+large inversion residuals.
+Conversely, this correlation is absent from the large differences seen in
+points around Venezuela.
+In the Borborema province, northeastern Brazil,
+our model slightly overestimates the Moho depth.
+On the other hand, our model underestimates the depths
+in the Amazon region and the Paraná basin.
+Particularly in the Amazon basin,
+where our model predicts a Moho depth of approximately 30 km,
+the residuals and the differences with the seismic data are larger than in the
+Paraná basin.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Meh.
+We have developed a computationally efficient gravity inversion method in
+spherical coordinates.
+Our method extends the Gauss-Newton formulation of Bott's method
+\citep{silva2014} to use tesseroids as model elements and smoothness
+regularization.
+We retain the computational efficiency of Bott's method by taking advantage of
+the sparse nature of all matrices involved.
+We employ two cross-validation techniques to estimate the hyper-parameters of
+the inversion: the regularization parameter, the Moho density-contrast, and the
+Normal Earth Moho depth.
+
+The test on simple synthetic data shows that our inversion method is able to
+recover a smooth Moho relief with a homogeneous density-contrast.
+The inversion was not able to fully recover the shortest wavelength feature in
+the model, possibly due to the smoothness constraints which tends to soften
+high-frequency (sharp) variations.
+The cross-validation Mean Square Error curve in Fig.~\ref{fig:simple-results}e
+has a well-defined minimum, indicating a value of the regularization parameter
+($\mu$) whose corresponding estimate best predicts data that were not included
+in the inversion.
+Using this value of $\mu$ in the inversion leads to a smooth Moho relief and
+acceptable data misfit.
+
+The source code profiling results presented in Table~\ref{profiling}
+confirm the efficiency of the proposed method.
+When using sparse matrices, solving linear systems and performing matrix
+multiplications together account for a mere 0.067\% of the total computation
+time required for a single inversion.
+The majority of the computation time (99.824\%) is spent on forward modeling.
+Thus, we are able to retain the high computational efficiency of Bott's method
+while using a classic Tikhonov regularization formulation.
+This approach could, in theory, be extended to other types of regularization
+(e.g., Total Variation) and misfit functions (e.g., re-weighted least squares)
+already available in the literature.
+For example, the Total Variation approach used by \citet{martins2011} could
+potentially be implemented in a more straight forward manner than done by
+\citet{santos2015}.
+
+The more complex synthetic data test based on CRUST1.0
+(Fig.~\ref{fig:crust1-results})
+shows that the cross-validation using pointwise Moho depth information
+is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
+Earth Moho depth ($z_{ref}$).
+This test indicates that the inversion neither correctly estimates Moho depth
+nor adequately fits the gravity and pointwise data when sharp variations in
+Moho depth occur.
+This phenomenon is particularly strong in the region below the Andes.
+A likely explanation is that the smoothness regularization
+is intrinsically unable to produce sharp variations in Moho depth.
+These effects might be mitigated with the use of sharpness-inducing
+regularization, like Total Variation \citep{martins2011},
+Cauchy norm regularization \citep{sacchi1996, pilkington2008},
+or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.
+
+We applied the method proposed here to estimate the Moho depth for South
+America.
+Our Moho depth model is in accordance with previous results by
+\citet{vandermeijde2013}.
+The model fits well the gravity and seismic data in all oceanic regions, the
+central portion of the Andean foreland, Patagonia, and coastal and central
+parts of Brazil.
+However, the model is unable to fit the gravity and seismic data in places with
+sharp variations in Moho depth, particularly below the Andes.
+This might indicate the improper use of smoothness regularization, as suggested
+by the CRUST1.0 synthetic data test, or the presence of crustal or mantle
+density anomalies that were unaccounted for during the data corrections.
+In the coastal region of Venezuela, along the central Amazon and Solimões
+basins, and in the Paraná basin, the model is able to fit the gravity data but
+differs significantly from the seismic data.
+\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
+Paraná and Amazon basins, respectively, as high density rocks in the lower
+crust.
+In general, differences between a gravity and a seismically derived Moho model
+may indicate the presence of crustal or mantle density anomalies that were
+unaccounted for in the data processing.
+Such locations warrant further detailed investigation.
 
@@
 
-The authors are indebted to the developers and maintainers of the open-source
+We are indebted to the developers and maintainers of the open-source
 software without which this work would not have been possible.
+L. Uieda was supported by a scholarship from
+Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
+(CAPES).
+V.C.F. Barbosa was supported by a fellowship from
+Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
+\todo{Coloco o projeto da FAPERJ também?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-02-26 manuscript/manuscript.tex
Finish first draft of introduction
Fixes #3

@@
 level.
+
+We present a non-linear gravity inversion to estimate the Moho depth in
+a spherical Earth approximation.
+Our method is based on the \citet{silva2014} Gauss-Newton formulation of the
+method of \citet{bott1960}.
+We use tesseroids to discretize the anomalous Moho and the adaptive
+discretization algorithm of \citet{uieda2016} for the forward modeling.
+The stability of the inversion is achieved through smoothness regularization.
+In order to maintain the computational efficiency of Bott's method,
+we exploit the sparse nature of all matrices involved in the computations.
+We employ a variant of GCV known as hold-out cross-validation \citep{kim2009}
+to estimate the regularization parameter.
+Additionally, we estimate the density-contrast and reference level
+simultaneously in a second cross-validation.
+Similarly to \citet{silva2006} and \citet{martins2010}, this cross-validation
+procedure uses knowledge of the Moho depth at certain points.
+Finally, we apply the proposed method to estimate the Moho depth for South
+America using gravity data from the GOCO5S model \citep{mayer-guerr2015} and
+the seismological data of \citet{assumpcao2013a}.
 
@@
 
-A similar approach was used by \citet{martins2010}
+A similar approach was used by \citet{silva2006} and \citet{martins2010}
 to estimate the parameters defining

### 2016-02-26 manuscript/manuscript.tex
First draft of abstract
Fixes #17

@@
 \begin{abstract}
+    Estimating the relief of the Moho from gravity data is a computationally
+    intensive non-linear inverse problem.
+    What is more, the modeling must take the Earths curvature into account when
+    the study area is of regional scale or greater.
+    We present a regularized non-linear gravity inversion method that has a low
+    computational footprint and employs a spherical Earth approximation.
+    To achieve this, we combine the highly efficient Bott's method with
+    smoothness regularization and a discretization of the anomalous Moho into
+    tesseroids (spherical prisms).
+    The computational efficiency of our method is attained by harnessing the
+    fact that all matrices involved are sparse.
+    The inversion results are controlled by three hyper-parameters: the
+    regularization parameter, the anomalous Moho density-contrast, and the
+    reference Moho depth.
+    We estimate the regularization parameter using the method of hold-out
+    cross-validation.
+    Additionally, we estimate the density-contrast and the reference depth
+    using knowledge of the Moho depth at certain points.
+    We apply the proposed method to estimate the Moho depth for the South
+    American continent using satellite gravity data and seismological data.
+    The final Moho model is in accordance with previous gravity-derived models
+    and seismological data.
+    The misfit to the gravity and seismological data is worse in the Andes and
+    best in oceanic areas, central Brazil and Patagonia, and along the Atlantic
+    coast.
+    Similarly to previous results, the model suggests a thinner crust of 30-35
+    km under the Andean foreland basins.
+    Discrepancies with the seismological data are greatest in the Guiana
+    shield, the central Solimões and Amazon basins, the Paraná basin, and the
+    Borborema province.
+    These differences suggest the existence of crustal or mantle density
+    anomalies that were unaccounted for during gravity data processing.
 \end{abstract}

### 2016-03-10 manuscript/manuscript.tex
Fix citation to Silva 2001

@@
 are ill-posed and require additional constraints in the form of
-regularization \citep{silva2001}.
+regularization \citep{silva2001b}.
 A common approach is to use the first-order Tikhonov regularization to impose

### 2016-03-19 manuscript/manuscript.tex
Add mantle source to problem concept figure
Add reference to it in the figure caption as well.

Remove the data grid from the figure as it makes no sense anymore.

@@
         ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
-        (c) The gravity disturbance ($\delta(P)$) and
-        the corresponding density anomalies after removal of the normal gravity:
-        topography, oceans, crustal heterogeneities, and the anomalous Moho.
+        (c) The gravity disturbance ($\delta(P)$) and the corresponding density
+        anomalies after removal of the normal gravity: topography, oceans,
+        crustal and mantle heterogeneities, and the anomalous Moho.
         (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic

### 2016-03-19 manuscript/manuscript.tex
Use Basin with capitol B for proper names

@@
     Discrepancies with the seismological data are greatest in the Guiana
-    shield, the central Solimões and Amazon basins, the Paraná basin, and the
+    shield, the central Solimões and Amazon Basins, the Paraná Basin, and the
     Borborema province.
@@
 On the other hand, our model underestimates the depths
-in the Amazon region and the Paraná basin.
-Particularly in the Amazon basin,
+in the Amazon region and the Paraná Basin.
+Particularly in the Amazon Basin,
 where our model predicts a Moho depth of approximately 30 km,
 the residuals and the differences with the seismic data are larger than in the
-Paraná basin.
+Paraná Basin.
 
@@
 In the coastal region of Venezuela, along the central Amazon and Solimões
-basins, and in the Paraná basin, the model is able to fit the gravity data but
+Basins, and in the Paraná Basin, the model is able to fit the gravity data but
 differs significantly from the seismic data.
 \citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
-Paraná and Amazon basins, respectively, as high density rocks in the lower
+Paraná and Amazon Basins, respectively, as high density rocks in the lower
 crust.

### 2016-03-19 manuscript/manuscript.tex
Corrections to introduction by Val

@@
 methods.
-The two main methods used to estimate the depth of the Moho are seismology,
-with both natural and controlled sources, and gravimetry.
+The two main geophysical methods used to estimate the depth of the Moho are
+seismology, with both natural and controlled sources, and gravimetry.
 With the advent of satellite gravimetry missions like GRACE and GOCE,
-gravity derived crustal models can be produced in regional or global scales
+gravity-derived crustal models can be produced in regional or global scales
 \citep[e.g. ][]{reguzzoni2013,vandermeijde2013,vandermeijde2015}.
@@
 An example is South America, where seismologic and terrestrial gravity data
-are traditionally concentrated around large urban centers and coastal areas.
+are traditionally concentrated around urban centers and coastal areas,
+resulting in large areas (e.g., forests and mountains) devoid of data.
 
 Estimating Moho depth from gravity data is a non-linear inverse problem.
-One can generalize this problem to estimating the relief of an interface,
-such as the basement of a sedimentary basin or the relief of the anomalous
-Moho.
+One can generalize this problem of estimating the depths of an interface
+separating two media,
+such as the sediment-basement interface of a sedimentary basin or the
+crust-mantle interface (Moho).
 Several methods have been developed over the years to solve this inverse
@@
 
-Most non-linear gravity inversion methods discretize the relief of the
-interface into juxtaposed right-rectangular prisms with a known density
-contrast.
-The inverse problem is then to estimate the thickness of each prism from the
-gravity data.
-The use of rectangular prisms implies a planar Earth approximation and may not
-be adequate for continental and global scale studies.
-In such cases, a spherical Earth approximation is preferred.
+A spherical Earth approximation is preferred when estimating the Moho depth
+from gravity data in continental and global scale studies.
 \citet{wieczorek1998} developed a spherical harmonic equivalent of the
@@
 of the Moon.
-\citet{reguzzoni2013} use a spherical approximation to estimate the global
-Moho relief from GOCE satellite gravity data.
-Conversely, one could adapt one of the methods developed for
-right-rectangular prisms to use tesseroids (spherical prisms) instead.
+\citet{reguzzoni2013} use a spherical Earth approximation to estimate the
+global Moho relief using data from the GOCE satellite mission.
+Another approach is to use
+non-spectral (space domain) gravity inversion methods.
+Many such methods were developed for estimating the basement relief of a
+sedimentary basin
+\citep[e.g., ][]{barbosa1999a, barbosa1999b, martins2010, martins2011, sun2014}.
+These methods approximate the sedimentary pack by a set of juxtaposed
+right-rectangular prisms.
+The top of the prisms coincide with the Earth's surface and the prisms'
+thicknesses represent the depths to the basement and are the parameters to be
+estimated in the inversion.
+The use of rectangular prisms implies a planar Earth approximation and may not
+be adequate for depth-to-Moho estimates in a continental-scale study.
+A straightforward way to circumvent this hindrance is to adapt one of the
+methods developed for rectangular prisms to use tesseroids (spherical prisms).
 One of the difficulties of this approach is that the forward problem for a
@@
 
-In any gravity inversion for the relief of an interface, two hyper-parameters
-control the inversion results: the density-contrast between the two mediums
-and the reference level around which the interface undulates.
-The reference level is the depth of the Normal Earth Moho in the case of the
-anomalous Moho.
+In any gravity inversion for estimating the relief of an interface, two
+hyper-parameters control the inversion results: the density-contrast between
+the two media and the reference level around which the interface undulates.
+The reference level is the constant depth of the Normal Earth Moho in the case
+of the anomalous Moho.
 For regularized inversions, an additional hyper-parameter is the regularization
-parameter that balances data-misfit and regularization.
+parameter that balances the relative importance between the data-misfit measure
+and the regularizing function.
 The two most commonly used methods for estimating the regularization parameter
@@
 at a few points.
-To the authors knowledge no attempt has been made to estimate the reference
+To the authors' knowledge no attempt has been made to estimate the reference
 level.
@@
 Similarly to \citet{silva2006} and \citet{martins2010}, this cross-validation
-procedure uses knowledge of the Moho depth at certain points.
+procedure uses knowledge of the Moho depths at certain points.
 Finally, we apply the proposed method to estimate the Moho depth for South

### 2016-03-20 manuscript/manuscript.tex
Corrections to start of methodology by Val

@@
 
-In potential field methods,
-we must isolate the target anomalous density distribution prior to modeling and
-inversion.
+In potential field methods, we must isolate the target anomalous density
+distribution before modeling and inversion.
 In our case, the target is the relief of the real Moho undulating around a
@@
 
-In order to invert for the anomalous Moho relief,
+To estimate the anomalous Moho relief from gravity data,
 we must first isolate its gravitational attraction.
-Thus, all other effects
+Thus, all other gravitational effects
 must be either removed or assumed negligible.
-Here, we will remove the effect of the topography and oceans
-in order to obtain the full Bouguer disturbance
+Here, we will remove the gravitational effect produced by the known topography
+and ocean masses to obtain the full Bouguer disturbance
 (Fig~\ref{fig:anomalysketch}d),
@@
 \noindent
-We will remove the effect of sedimentary basins
+We will also remove the gravitational effect of know sedimentary basins
 but assume that the effects of

### 2016-03-20 manuscript/manuscript.tex
Corrections to inverse problem and parametrization
by Val

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Parametrization}
+\subsection{Parametrization and the forward problem}
 
@@
 (see Fig.~\ref{fig:anomalysketch}b).
-In cases where the true Moho is above $z_{ref}$,
+If the true Moho is above $z_{ref}$,
 the top of the $k$th tesseroid is the Moho depth $z_{k}$,
@@
 We wish to estimate the parameter vector $\mathbf{p}$ from a set of observed
-gravity anomaly data $\mathbf{d}^o$.
+gravity data $\mathbf{d}^o$.
 The least-squares estimate is the one that minimizes the data-misfit function
@@
     \phi(\mathbf{p}) =
-    [\mathbf{d}^o - \mathbf{d}(\mathbf{p})]^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p})].
+        [\mathbf{d}^o - \mathbf{d}(\mathbf{p})]^T
+        [\mathbf{d}^o - \mathbf{d}(\mathbf{p})].
     \label{eq:data-misfit}
@@
 methods like Gauss-Newton or Steepest Descent.
-Such methods start from an initial estimate $\mathbf{p}^0$ and iteratively
-update the estimate until a minimum is reached.
+Such methods start from an initial approximation to the model parameter vector
+$\mathbf{p}^0$ and estimate a parameter perturbation vector
+$\mathbf{\Delta p}^0$.
+The perturbation vector is used to update $\mathbf{p}^0$ to
+$\mathbf{p}^1 =  \mathbf{p}^0 + \mathbf{\Delta p}^0$.
+This procedure is repeated until a minimum of function $\phi(\mathbf{p})$
+(Eq.~\ref{eq:data-misfit}) is reached.
 
 For the Gauss-Newton method,
-the update at the $k$th iteration,
-$\mathbf{\Delta p} = \mathbf{p}^{k+1} - \mathbf{p}^k$,
-is the solution of the linear system
-
-\begin{equation}
-    \mathbf{H}^k\mathbf{\Delta p} = -\mathbf{\nabla\phi}^k,
+the parameter perturbation vector at the $k$th iteration $\mathbf{\Delta p}^k$
+is obtained by solving the linear system
+
+\begin{equation}
+    \mathbf{H}^k\mathbf{\Delta p}^k = -\mathbf{\nabla\phi}^k,
     \label{eq:gaussnewton}
@@
 
-The Steepest Descent method uses only the gradient direction
-to update the initial estimate \citep{kelley1987}.
-The update at the $k$th iteration is achieved by equating the Hessian
-in Eq.~\ref{eq:gaussnewton} to the identity matrix,
-
-\begin{equation}
-    \mathbf{\Delta p} = -\mathbf{\nabla\phi}^k.
-    \label{eq:steepest}
-\end{equation}
-
-\noindent
-Thus, it does not require the computation and storage of the Hessian matrix
-nor the solution of linear systems.
-However, the Steepest Descent method has poor convergence when the
-current solution is close to the minimum of the goal function
-\citep{kelley1987}.
-
 The gradient vector and the Gauss-Newton approximation of the Hessian matrix
@@
 \begin{equation}
-    \mathbf{\nabla\phi}^k = -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)],
+    \mathbf{\nabla\phi}^k = -2{\mathbf{A}^k}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)],
     \label{eq:gradient}
@@
 \begin{equation}
-    \mathbf{H}^k \approx 2\mathbf{A}^T\mathbf{A},
+    \mathbf{H}^k \approx 2{\mathbf{A}^k}^T{\mathbf{A}^k},
     \label{eq:hessian}
@@
 \noindent in which
-$\mathbf{A}$ is the Jacobian or sensitivity matrix,
-
-\begin{equation}
-    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mathbf{p^k}).
+$\mathbf{A}^k$ is the $N \times M$ Jacobian or sensitivity matrix
+whose elements are
+
+\begin{equation}
+    A_{ij}^k = \dfrac{\partial f_i}{\partial p_j}(\mathbf{p}^k).
     \label{eq:jacobian}

### 2016-03-20 manuscript/manuscript.tex
Corrections to regularization by Val

@@
 
-Non-linear inversions for the relief of an interface (like the Moho)
-are ill-posed and require additional constraints in the form of
-regularization \citep{silva2001b}.
-A common approach is to use the first-order Tikhonov regularization to impose
-smoothness on the solution.
+Non-linear gravity inversions for estimating the relief of an interface
+separating two media (like the Moho) are ill-posed and require additional
+constraints in the form of regularization \citep{silva2001b}.
+A common approach is to use the first-order Tikhonov regularization
+\citep{tikhonov1977} to impose smoothness on the solution.
 The cost function for smoothness regularization is given by
@@
 \noindent where $\mathbf{R}$ is an $L \times M$ finite-difference matrix
-representing the $L$ first-order differences between adjacent tesseroids.
-
-The solution $\hat{\mathbf{p}}$ to the regularized inverse problem is the one that
-minimizes the goal function
+representing $L$ first-order differences between adjacent tesseroids.
+
+To transform the ill-posed inverse problem into a well-posed one via Tikhonov
+regularization, we adopted the well-established procedure
+of formulating a constrained inverse problem that is solved by minimizing an
+unconstrained goal function
 
@@
 in which $\mu$ is the regularization parameter that controls the balance
-between fitting the observed data and obeying the smoothness constraint.
+between fitting the observed data and obeying the smoothness constraint imposed
+by the regularizing function $\theta(\mathbf{p})$ (Eq.~\ref{eq:regul}).
 
 The goal function $\Gamma(\mathbf{p})$ is also non-linear with respect to
-$\mathbf{p}$ and can be minimized using the Gauss-Newton or Steepest Descent
-methods.
+$\mathbf{p}$ and can be minimized using the Gauss-Newton method.
 The gradient vector and Hessian matrix of the goal function are, respectively,
@@
     \mathbf{\nabla\Gamma}^k =
-        -2\mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] +
+        -2{\mathbf{A}^k}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] +
         2\mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
@@
 \begin{equation}
-    \mathbf{H}^k = 2\mathbf{A}^T\mathbf{A} + 2\mu\mathbf{R}^T\mathbf{R}.
+    \mathbf{H}^k = 2{\mathbf{A}^k}^T{\mathbf{A}^k}
+                   + 2\mu\mathbf{R}^T\mathbf{R}.
     \label{eq:hessian-regul}
@@
 
-\noindent The parameter updates for the regularized Gauss-Newton and Steepest
-Descent methods, respectively, then become
-
-\begin{equation}
-    \left[\mathbf{A}^T\mathbf{A} + \mu\mathbf{R}^T\mathbf{R}\right]
-    \mathbf{\Delta p} =
-        \mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] -
-        \mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
+At the $k$th iteration, the parameter perturbation vector
+$\mathbf{\Delta p}^k$ is obtained by solving the linear equation system
+
+\begin{equation}
+    \left[{\mathbf{A}^k}^T{\mathbf{A}^k} + \mu\mathbf{R}^T\mathbf{R}\right]
+    \mathbf{\Delta p}^k =
+    {\mathbf{A}^k}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] -
+    \mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k.
     \label{eq:gaussnewton-regul}
@@
 
-\noindent and
-
-\begin{equation}
-    \mathbf{\Delta p} =
-        \mathbf{A}^T[\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)] -
-        \mu\mathbf{R}^T\mathbf{R}\mathbf{p}^k,
-    \label{eq:steepest-regul}
-\end{equation}
-
-Producing the regularized solution using the above equations is computationally
+Estimating the Moho depths using the above equations is computationally
 costly because of two main factors:
 (1) the evaluation and storage of the dense $N \times M$ Jacobian matrix
-$\mathbf{A}$
+${\mathbf{A}^k}$
 and (2) the solution of the resulting $M \times M$ equation system
@@
 are often calculated through a first-order finite-difference approximation.
-Thus, evaluating $\mathbf{A}$ requires $2\times M \times N$ forward modeling
+Thus, evaluating ${\mathbf{A}^k}$ requires $2\times M \times N$ forward modeling
 operations for each iteration of the gradient descent algorithm.
-These computations are performed for each iteration of the optimization.
+These computations are performed for each iteration of the optimization
+of the goal function $\Gamma(\mathbf{p})$.
 

### 2016-03-20 manuscript/manuscript.tex
Corrections to Bott's method by Val

@@
 
-\citet{bott1960} developed an efficient method to determined the basement
-relief of a sedimentary basin from gravity observations.
+\citet{bott1960} developed an efficient method to determined the depth of the
+basement of a sedimentary basin from gravity observations.
 The method requires data on a regular grid of $N_x \times N_y = N$
@@
 M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
-Bott's iterative method starts with an initial estimate of the basement relief
-$\mathbf{p}^0$ equal to the null vector and updates the estimate using the formula
-
-\begin{equation}
-    \mathbf{\Delta p} = \dfrac{\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)}{2\pi G \Delta \rho},
+Bott's iterative method starts with an initial approximation of the basement
+depths $\mathbf{p}^0$ equal to the null vector.
+The method updates the approximation by calculating a parameter perturbation
+vector $\mathbf{\Delta p}^k$ using the formula
+
+\begin{equation}
+    \mathbf{\Delta p}^k =
+        \dfrac{\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)}{2\pi G \Delta \rho},
     \label{eq:bott}
@@
 \noindent
-in which $G$ is the gravitational constant and $\Delta \rho$ is the basin
-density contrast.
+in which $G$ is the gravitational constant and $\Delta \rho$ is the
+contrast between the density of the sediments and the reference density.
 The iterative process stops when the inversion residuals
-$\mathbf{r} = \mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)$ fall below the assumed noise level
+$\mathbf{r}^k = \mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)$ fall below the assumed noise level
 of the data.
@@
 \noindent
-in which $\mathbf{I}$ is the identity matrix.
+where $\mathbf{I}$ is the identity matrix.
 In this framework,
@@
 
-We propose that Bott's method can also be formulated as a special case of the
-Steepest Descent method (Eq.~\ref{eq:steepest}) by setting the Jacobian matrix to
-
-\begin{equation}
-    \mathbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mathbf{I}.
-    \label{eq:bott-steepest}
-\end{equation}
-
-\noindent
-In practice, both formulations lead to Eq.~\ref{eq:bott}.
 One of the advantages of Bott's method over the traditional Gauss-Newton or
-Steepest Descent is eliminating the computation and storage of the dense
-Jacobian matrix $\mathbf{A}$.
+Steepest Descent is the elimination of the computation and storage of the dense
+Jacobian matrix $\mathbf{A}^k$.
 Furthermore, Bott's method also does not require the solution of equation

### 2016-03-20 manuscript/manuscript.tex
Corrections to section about our method by Val

@@
 
-We propose a regularized version of Bott's method to invert for the relief of
-the anomalous Moho in spherical coordinates.
+We propose a regularized version of Bott's method to invert gravity data for
+estimating the depth of the Moho in spherical coordinates.
 To adapt Bott's method to spherical coordinates,
@@
 (Eq.~\ref{eq:bott-gaussnewton}).
-This linearizes the Jacobian matrix and reduces it to a sparse diagonal matrix,
-thus eliminating the cost of computing and storing $\mathbf{A}$.
+Here, the Jacobian matrix is a diagonal matrix whose elements are invariant
+along successive iterations.
+Using this approximation eliminates the cost of computing and storing
+the full Jacobian matrix $\mathbf{A}^k$ at each iteration
+(Eq.~\ref{eq:jacobian}).
 Matrix arithmetic operations can be performed efficiently by taking advantage
@@
 \citep{uieda2016}.
-Our benchmarks suggest that
-sparse matrix multiplications and solving the sparse linear system
-in Eq.~\ref{eq:gaussnewton-regul}
-account for less than 0.1\%
-of the computation time of a single inversion
-(see section~\ref{sec:simple-synthetic} and Table~\ref{profiling}).
-Hence, by employing the use of sparse matrices,
-our formulation retains the efficiency of Bott's method
-while stabilizing the solution through the well established formalism of
-Tikhonov regularization.
+We show later in this article that sparse matrix multiplications and solving
+the sparse linear system in Eq.~\ref{eq:gaussnewton-regul} account for less
+than 0.1\% of the computation time required for a single inversion.
+Hence, by employing the use of sparse matrices, our formulation retains the
+efficiency of Bott's method while stabilizing the solution through the well
+established formalism of Tikhonov regularization.
 
@@
     \caption{Sketch of a data grid separated into
-        the training (white dots with black outlines)
+        the training (open circles)
         and testing (black dots) data sets.

### 2016-03-20 manuscript/manuscript.tex
Corrections to simple synthetic by Val

@@
 by applying it to two noise-corrupted synthetic data sets.
-The first data set is generated by a simple Moho model simulating the transition
+The first one is generated by a simple Moho model simulating the transition
 from a thicker continental crust to a thinner oceanic crust.
@@
         (a) The estimated Moho depth.
-        (b) The difference between the true model depths
-        and the estimated depths.
-        (c) The inversion residuals (observed data minus
-        the data predicted by the estimate).
-        (d) Histogram of the residuals. Also shown are the calculated
-        mean and standard deviation (std) of the residuals.
-        Note that the data were contaminated with normally distributed
-        pseudo-random noise with zero mean and 5 mGal standard deviation.
+        (b) The Moho depth residuals (difference between the true and estimated
+        Moho depths).
+        (c) The gravity residuals (difference between the observed and
+        predicted gravity data).
+        (d) Histogram of the gravity residuals shown in c, with the calculated
+        mean and standard deviation (std) of the residuals in mGal.
         (e) Cross-validation curve used to determine the optimal regularization
@@
 and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
-Fig.~\ref{fig:simple-data}a shows the model Moho depths,
-where each pixel in the pseudo-color image corresponds to
-a tesseroid of the model.
+Fig.~\ref{fig:simple-data}a shows the model Moho depths where we can clearly
+see an eastward crustal thinning.
+In Fig.~\ref{fig:simple-data}a, each pixel in the pseudo-color image
+corresponds to a tesseroid of the model.
 
@@
 sampled from a normal distribution with zero mean and 5 mGal standard deviation.
-Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set.
+Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set
+exhibiting an eastward increase due to the simulated eastward
+crustal thinning shown in Fig.~\ref{fig:simple-data}a.
 The data grid spacing is half the grid spacing of the tesseroid model
@@
 
-Fig.~\ref{fig:simple-results} summarizes the inversion results.
 Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
@@
 2.19 and -2.13 km, respectively.
-Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
-the observed and predicted data), in mGal.
+Fig.~\ref{fig:simple-results}c shows inversion residuals, defined as the
+difference between the observed and predicted data (in mGal).
 The largest residual (in absolute value) coincides with the largest difference

### 2016-03-20 manuscript/manuscript.tex
Corrections to CRUST1 synthetic by Val

@@
         (b) Noise-corrupted synthetic gravity data generated from the model.
-        (c) Synthetic seismic data simulating point estimates of Moho depth.
-        The point estimates were obtained by interpolating
-        the Moho depth in (a).
+        (c) Simulated points where the Moho depths are known from seismological
+        estimates (color dots).  Here, these point were obtained by
+        interpolating the Moho depth in (a).
     }
@@
 We produce such data by interpolating the Moho depth shown in
-Fig.~\ref{fig:crust1-data}a on the same geographic coordinates
-as the 937 points from the \citet{assumpcao2013a} data set.
+Fig.~\ref{fig:crust1-data}a on the same 937 geographic coordinates
+pinpointed in the data set of \citet{assumpcao2013a}.
 The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
@@
 The optimal regularization parameter that minimizes the MSE is $\mu = 10^{-4}$
-(indicated by the red triangle).
+(red triangle in Fig.~\ref{fig:crust1-results}a).
 
@@
 the true Moho depths (Fig.~\ref{fig:crust1-data}a)
-and the estimated depths.
+and the estimated depths (Fig.~\ref{fig:crust1-results}c).
 The maximum and minimum differences are, respectively,
@@
 on the continental and Pacific sides.
-Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
-between the observed and predicted data).
-The inversion residuals appear normally distributed,
+Figs.~\ref{fig:crust1-results}e and g show the gravity residuals,
+defined as the difference between the observed and predicted gravity data.
+The residuals appear normally distributed,
 with 0.03 mGal mean and a standard deviation of 4.10 mGal.
-The residuals follow a similar, though reversed, pattern
+The gravity residuals follow a similar, though reversed, pattern
 to the differences shown in Fig.~\ref{fig:crust1-results}d.

### 2016-03-20 manuscript/manuscript.tex
Corrections to SAm data sections by Val
Not included the model discussion

@@
 
-The seismic point estimates of Moho depth used in the cross-validation
-procedure are from the data set of \citet{assumpcao2013a}.
-The 937 data points in this data set are shown in Fig.~\ref{fig:sam-data}b.
+Fig.~\ref{fig:sam-data}b shows the 937 known Moho depths (colored dots) which
+were estimated from seismological data by \citet{assumpcao2013a}.
+This data set is used in the cross-validation procedure.
 
@@
 
-We split the sediment-free gravity data into the training and testing data
-sets.
+We split the sediment-free gravity disturbance (Fig.~\ref{fig:sam-data}a) into
+the training and testing data sets.
 The training data set is a regular grid with $0.4^\circ$ grid spacing
@@
 We test all combinations of
-seven values of $z_{ref}$, from 20 to 35 km with 2.5 km intervals,
+seven values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
 and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
@@
 with respect to the \citet{assumpcao2013a} data set.
-The MSE has a well defined minimum, indicated by the red triangle,
+The MSE has a well-defined minimum, indicated by the red triangle,
 at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.

### 2016-03-20 manuscript/manuscript.tex
Corrections to conclusions by Val (part 1)
Missing the last paragraph

@@
 in the inversion.
-Using this value of $\mu$ in the inversion leads to a smooth Moho relief and
-acceptable data misfit.
+Using this value of $\mu$ in the inversion leads to a stable solution
+characterized by a smooth Moho relief with an acceptable data misfit.
 
@@
 Thus, we are able to retain the high computational efficiency of Bott's method
-while using a classic Tikhonov regularization formulation.
+and use a classic Tikhonov regularization formulation.
 This approach could, in theory, be extended to other types of regularization
-(e.g., Total Variation) and misfit functions (e.g., re-weighted least squares)
+(e.g., total variation) and misfit functions (e.g., re-weighted least squares)
 already available in the literature.
-For example, the Total Variation approach used by \citet{martins2011} could
+For example, the total variation approach used by \citet{martins2011} could
 potentially be implemented in a more straight forward manner than done by
@@
 These effects might be mitigated with the use of sharpness-inducing
-regularization, like Total Variation \citep{martins2011},
+regularization, like
+the weighted smoothness inversion \citep{barbosa1999a},
 Cauchy norm regularization \citep{sacchi1996, pilkington2008},
+entropic regularization \citep{silva2010},
+total variation regularization \citep{martins2011},
 or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.
@@
 Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
-\todo{Coloco o projeto da FAPERJ também?}
 

### 2016-03-21 manuscript/manuscript.tex
Corrections to last paragraph of conclusion by Val

@@
 America.
-Our Moho depth model is in accordance with previous results by
+Our estimated Moho depth model is in accordance with previous results by
 \citet{vandermeijde2013}.
@@
 However, the model is unable to fit the gravity and seismic data in places with
-sharp variations in Moho depth, particularly below the Andes.
-This might indicate the improper use of smoothness regularization, as suggested
-by the CRUST1.0 synthetic data test, or the presence of crustal or mantle
-density anomalies that were unaccounted for during the data corrections.
+sharp variations in Moho depth, particularly below the Andes and in the
+boundaries of the main geotectonic provinces of the South American Plate, like
+the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
+This might indicate that smoothness regularization should not be applied
+indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
+data test.
+Another reason for the observed misfit might be the presence of crustal or
+mantle density anomalies whose gravitational effects were not removed during
+the data corrections.
 In the coastal region of Venezuela, along the central Amazon and Solimões
-Basins, and in the Paraná Basin, the model is able to fit the gravity data but
-differs significantly from the seismic data.
+Basins, and in the Paraná Basin, our Moho depth model is able to fit the
+gravity data but differs significantly from the seismic data.
 \citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the

### 2016-03-21 manuscript/manuscript.tex
Figure with residuals and seismic diffs
For the South America model. Plot the tectonic provinces without names.

@@
-\documentclass[extra,mreferee]{gji}
-%\documentclass[extra]{gji}
+%\documentclass[extra,mreferee]{gji}
+\documentclass[extra]{gji}
 \usepackage{timet}
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/south-america-residuals}
+    \caption{
+        Inversion results for the South American Moho.
+        (a) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
+        minus the data predicted by the estimate (a)).
+        (b) Differences between the seismological depths of
+        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate
+        (Fig.~\ref{fig:sam-moho}).
+        The inset in b shows a histogram of the differences along with their
+        calculated mean and standard deviation (std).
+    }
+    \label{fig:sam-residuals}
+\end{figure*}
+
 The final Moho depth model for South America is shown

### 2016-03-22 manuscript/manuscript.tex
Add names of plates and provinces to moho map

@@
     \caption{
-        Inversion results for the South American Moho.
-        (a) The estimated Moho depth of South America.
+        The estimated Moho depth of South America.
+        Dotted lines represent the boundaries between major geologic provinces
+        \citep[after][]{assumpcao2013a, goutorbe2015};
+        AD: Andean Province,
+        AFB: Andean foreland basins,
+        AM: Amazonas Basin,
+        BR: Brazilian Shield,
+        BO: Borborema province,
+        CH: Chaco Basin,
+        GB: Guyana Basin,
+        GU: Guyana Shield,
+        PB: Parnaíba Basin,
+        PC: Parecis Basin,
+        PR: Paraná Basin,
+        PT: Patagonia province,
+        SF: São Francisco Craton,
+        SM: Solimões Basin.
+        Solid orange lines mark the limits of the main lithospheric plates
+        \citep{bird2003a};
+        AF: Africa Plate,
+        AN: Antarctica Plate,
+        CA: Caribbean Plate,
+        CO: Cocos Plate,
+        SA: South America Plate,
+        SC: Scotia Plate,
+        NZ: Nazca Plate.
         The solid light grey line is the 35 km Moho depth contour.
-        (b) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
-        minus the data predicted by the estimate (a)).
-        (c) Differences between the seismological depths of
-        \citet{assumpcao2013a} and our gravity-derived estimate shown in (a).
-        The inset in (c) shows a histogram of the differences along with their
-        calculated mean and standard deviation (std).
     }

### 2016-03-22 manuscript/manuscript.tex
Fix caption for residuals figure

@@
     \caption{
-        Inversion results for the South American Moho.
-        (a) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
-        minus the data predicted by the estimate (a)).
-        (b) Differences between the seismological depths of
-        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate
-        (Fig.~\ref{fig:sam-moho}).
+        Residuals for the estimated South American Moho depth in
+        Fig.~\ref{fig:sam-moho}.
+        (a) Gravity residuals, defined as the difference between the observed data in Fig.~\ref{fig:sam-data}a
+        and the data predicted by the estimate in Fig.~\ref{fig:sam-moho}.
+        (b) Differences between the seismological depth estimates of
+        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate.
         The inset in b shows a histogram of the differences along with their
         calculated mean and standard deviation (std).
+        Dotted lines mark the limits of major geologic provinces and
+        lithospheric plates.
     }

### 2016-03-22 manuscript/manuscript.tex
Replace k indexes in hyper-param  text
k is already used in the iterations of Gauss-Newton.

Correction by Val.

@@
-%\documentclass[extra,mreferee]{gji}
-\documentclass[extra]{gji}
+\documentclass[extra,mreferee]{gji}
+%\documentclass[extra]{gji}
 \usepackage{timet}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimating the regularization parameter}
+\subsection{Estimating the inversion hyper-parameters}
+
+\subsubsection{The regularization parameter}
 
@@
 and used to judge the quality of the chosen value of $\mu$.
-For a value of the regularization parameter $\mu_k$,
-the training set is inverted using $\mu_k$
-to obtain an estimate $\mathbf{\hat{p}}^k$.
+For a value of the regularization parameter $\mu_n$,
+the training set is inverted using $\mu_n$
+to obtain an estimate $\mathbf{\hat{p}}^n$.
 This estimate is used to calculate predicted data
@@
 via forward modeling
-($\mathbf{d}_{test}^k = \mathbf{f}(\mathbf{\hat{p}}^k$)).
-The metric chosen to evaluate $\mu_k$ is
+
+\begin{equation}
+    \mathbf{d}_{test}^n = \mathbf{f}(\mathbf{\hat{p}}^n).
+    \label{eq:predicted_testing}
+\end{equation}
+
+The metric chosen to evaluate $\mu_n$ is
 the mean square error (MSE) of the misfit
@@
 \begin{equation}
-    MSE_k = \dfrac{\|\mathbf{d}^o_{test} - \mathbf{d}^k_{test}\|^2}{N_{test}},
+    MSE_n = \dfrac{\|\mathbf{d}^o_{test} - \mathbf{d}^n_{test}\|^2}{N_{test}},
     \label{eq:msemu}
@@
         and testing ($\mathbf{d}^o_{test}$) sets.
-    \item For each $\mu_k \in [\mu_1, \mu_2, \ldots, \mu_{N_{\mu}}]$:
+    \item For each $\mu_n \in [\mu_1, \mu_2, \ldots, \mu_{N_{\mu}}]$:
     \begin{enumerate}
-        \item Estimate $\mathbf{\hat{p}}^k$ by inverting the training set
+        \item Estimate $\mathbf{\hat{p}}^n$ by inverting the training set
             $\mathbf{d}^o_{inv}$.
-        \item Use $\mathbf{\hat{p}}^k$ to calculate the predicted testing set
-            $\mathbf{d}^k_{test}$.
-        \item Calculate the mean square error $MSE_k$ using Eq.~\ref{eq:msemu}.
+        \item Use $\mathbf{\hat{p}}^n$ to calculate the predicted testing set
+            $\mathbf{d}^n_{test}$ using Eq.~\ref{eq:predicted_testing}.
+        \item Calculate the mean square error $MSE_n$ using Eq.~\ref{eq:msemu}.
     \end{enumerate}
-    \item The final solution is the $\mathbf{\hat{p}}^k$ corresponding to the
-        smallest $MSE_k$.
+    \item The final solution is the $\mathbf{\hat{p}}^n$ corresponding to the
+        smallest $MSE_n$.
 \end{enumerate}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimating $z_{ref}$ and $\Delta\rho$}
+\subsubsection{$z_{ref}$ and $\Delta\rho$}
 
@@
 We use the mean square error (MSE)
-as a measure of how well a given inversion output $\mathbf{\hat{p}}^k$
+as a measure of how well a given inversion output $\mathbf{\hat{p}}^{l,m}$
 fits the know depths.
@@
 Before computing the MSE,
-we interpolate $\mathbf{\hat{p}}^k$ on the known points
-to obtain the predicted depths $\mathbf{z}_s^k$.
+we interpolate $\mathbf{\hat{p}}^{l,m}$ on the known points
+to obtain the predicted depths $\mathbf{z}_s^{l,m}$.
 The MSE is defined as
@@
 \begin{equation}
-    MSE = \dfrac{\|\mathbf{z}^o_s - \mathbf{z}^k_{s}\|^2}{N_s}.
+    MSE = \dfrac{\|\mathbf{z}^o_s - \mathbf{z}^{l,m}_{s}\|^2}{N_s}.
     \label{eq:msehyper}

### 2016-03-22 manuscript/manuscript.tex
Make subsection for hyper-param estimation
The two other two subsections are subsubsections and add an opening
paragraph for overview.

Fixes #21

@@
 
-\subsubsection{The regularization parameter}
+Parameters that influence the inversion result but are not estimated directly
+in the inversion are known as hyper-parameters.
+In the case of our regularized Moho depth inversion, the hyper-parameters are
+the regularization parameter $\mu$ (Eq.~\ref{eq:goalfunction}),
+the Moho density-contrast $\Delta \rho$ (Eq.~\ref{eq:bott-gaussnewton}),
+and the depth of the Normal Earth Moho, or reference level, $z_{ref}$
+(Fig.~\ref{fig:anomalysketch}b).
+
+We estimate these hyper-parameters in two steps.
+First, we assume fixed values for
+$z_{ref}$ and $\Delta\rho$ and perform a cross-validation procedure
+\citep{hansen1992} to estimate an optimal value for $\mu$.
+Our investigations suggest that the outcome of this round of cross-validation
+does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
+Second, we use the estimated $\mu$ to perform a second cross-validation
+procedure to estimate $z_{ref}$ and $\Delta\rho$.
+The outcome of both cross-validations is not only the values of the three
+hyper-parameters but the final estimated Moho depths.
+
+\subsubsection{Estimating the regularization parameter}
 
@@
 i.e. the one that best predicts the testing data.
-We emphasize that the inversion is performed only on the training data set.
+We emphasize that the inversion is performed on the training data set only.
 
@@
 fall on a similar grid but with twice the grid spacing
-(white dots with black outlines in Fig.~\ref{fig:grid_separation}).
+(open circles in Fig.~\ref{fig:grid_separation}).
 All other points from the original data grid
@@
 
-\subsubsection{$z_{ref}$ and $\Delta\rho$}
+\subsubsection{Estimating $z_{ref}$ and $\Delta\rho$}
 
@@
 $20\ km$ and $500\ kg/m^3$, respectively.
-Our investigations suggest that the outcome of this round of cross-validation
-does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
 Second, we use the estimated $\mu$ to run the cross-validation

### 2016-03-23 manuscript/profiling.tex
Move units to header of table
Changed this by hand. Need to re-run the notebook later

@@
     \caption{
-        Total time spent on each function during a single inversion of
+        Time spent on each function during a single inversion of
         simple synthetic data.
@@
     \begin{tabular}{lcc}
-        Function description & Time & Percentage of total time\\
+        Function description & Time (s) & Percentage of total time (\%)\\
         \hline
-        Sparse conjugate gradient & 0.021 s & 0.050\%\\
-        Sparse dot product & 0.007 s & 0.017\%\\
-        Tesseroid forward modeling & 42.059 s & 99.824\%\\
+        Sparse conjugate gradient & 0.021 & 0.050\\
+        Sparse dot product & 0.007 & 0.017\\
+        Tesseroid forward modeling & 42.059 & 99.824\\
         \hline

### 2016-03-23 manuscript/manuscript.tex
Minor change to sentence in CV section
Corrections to Moho model for SAm by Val

@@
     km under the Andean foreland basins.
-    Discrepancies with the seismological data are greatest in the Guiana
-    shield, the central Solimões and Amazon Basins, the Paraná Basin, and the
+    Discrepancies with the seismological data are greatest in the Guyana
+    Shield, the central Solimões and Amazonas Basins, the Paraná Basin, and the
     Borborema province.
@@
 \citep{hansen1992} to estimate an optimal value for $\mu$.
-Our investigations suggest that the outcome of this round of cross-validation
-does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
+Our investigations suggest that the optimal value of $\mu$ does not depend on
+the particular values of $z_{ref}$ and $\Delta\rho$ used.
 Second, we use the estimated $\mu$ to perform a second cross-validation
@@
 The final Moho depth model for South America is shown
-as a pseudo-color map in Fig.~\ref{fig:sam-moho}a.
+as a pseudo-color map in Fig.~\ref{fig:sam-moho}.
 The model is available in the online repository that accompanies
@@
 from 7.5 to 20 km.
-The Brazilian and Guiana shields have a deeper Moho (greater than 35 km),
-with the deepest portion in the area of the São Francisco craton.
-The Moho is shallower than 35 km along the western Amazon and Andean foreland
-regions, as well as along the Amazon river.
-
-Fig.~\ref{fig:sam-moho}b shows the inversion residuals
-(observed minus predicted data)
-and Fig.~\ref{fig:sam-moho}c shows the differences between
-the seismic-derived depths of \citet{assumpcao2013a}
-(Fig.~\ref{fig:sam-data}b) and the depths in our model.
-The differences range from approximately -23 to 23 km
-and have a mean of 1.18 km and a standard deviation of 6.84 km.
-The residuals and differences from seismic are smallest in the oceanic areas,
-southern Patagonia, and the eastern coast of the continent.
-The largest residuals are located along the Andes and correlate with the
-deepest Moho depths.
+The Brazilian and Guyana Shields have a deeper Moho (greater than 35 km),
+with the deepest portions in the area around the São Francisco Craton
+and the northern border of the Parecis Basin.
+The Moho is shallower than 35 km along the Guyana Basin, the Andean foreland
+basins, the Chaco Basin, and along the centers of the Solimões, Amazonas, and
+Paraná Basins.
+
+Fig.~\ref{fig:sam-residuals}a shows the gravity residuals,
+defined as the difference between the observed and predicted gravity data.
+Fig.~\ref{fig:sam-residuals}b shows the differences between
+the seismic-derived Moho depths of \citet{assumpcao2013a}
+(Fig.~\ref{fig:sam-data}b) and the depths of our gravity-derived model
+(Fig.~\ref{fig:sam-moho}).
+The differences shown in Fig.~\ref{fig:sam-residuals}b range from approximately
+-23 to 23 km and have a mean of 1.18 km and a standard deviation of 6.84 km.
+The gravity residuals and Moho depth differences from seismic are smallest in
+the oceanic areas, southern Patagonia, and the eastern coast of the continent.
+The largest gravity residuals are located along the Andes and correlate with
+the deepest Moho depths.
 These large residuals follow a pattern of a negative value in the center
-flanked by positive values to the East and West.
+flanked by positive values to the east and west.
 This same pattern is observed in the CRUST1.0 synthetic test results
-(Fig.~\ref{fig:crust1-results}),
-suggesting that this is a byproduct of the inversion method, not the data.
-Likewise, larger residuals also appear to be associated with sharp variations
-in the estimated Moho depth.
+(Fig.~\ref{fig:crust1-results}).
+In general, larger gravity residuals appear to be associated with sharp
+variations in the estimated Moho depth.
 Along the Andes, large differences with seismic data are correlated with the
-large inversion residuals.
-Conversely, this correlation is absent from the large differences seen in
-points around Venezuela.
+larger gravity residuals.
+Conversely, this correlation is absent from the large differences seen in the
+Guyana, Paraná, and the Solimões Basins.
 In the Borborema province, northeastern Brazil,
 our model slightly overestimates the Moho depth.
-On the other hand, our model underestimates the depths
-in the Amazon region and the Paraná Basin.
-Particularly in the Amazon Basin,
-where our model predicts a Moho depth of approximately 30 km,
-the residuals and the differences with the seismic data are larger than in the
-Paraná Basin.
+On the other hand, our model underestimates the Moho depths in the Amazonas,
+Solimões, and Paraná Basins.
+Particularly in the Amazonas and Solimões Basins, where our model predicts a
+Moho depth of approximately 30 km, the differences with the seismological
+estimates can reach 10 km or more.
 
@@
 the data corrections.
-In the coastal region of Venezuela, along the central Amazon and Solimões
-Basins, and in the Paraná Basin, our Moho depth model is able to fit the
-gravity data but differs significantly from the seismic data.
+In the Guyana Basin on the coastal region of Venezuela, along the central
+Amazonas and Solimões Basins, and in the Paraná Basin, our Moho depth model is
+able to fit the gravity data but differs significantly from the seismic data.
 \citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
-Paraná and Amazon Basins, respectively, as high density rocks in the lower
+Paraná and Amazonas Basins, respectively, as high density rocks in the lower
 crust.

### 2016-03-23 code/mohoinv.py
Better docstrings for classes

@@ -10,11 +10,11 @@ Defines the classes:
 
 * `TesseroidRelief`: Class to represent a relief undulating around a reference
   level and discretized into tesseroids.
-  
+
 See the Jupyter notebooks 'moho-inversion-example.ipynb' and
 'tesseroid-relief-example.ipynb' for instructions and example usage of these
 classes.
-  
+
 Also defines utility functions for cross-validation:
 
 * `fit_all`: Call the fit method of a list of solvers in parallel
@@ -41,7 +41,7 @@ import warnings
 def score_all(solutions, test_data, points, njobs=1):
     """
     Get the cross-validation score for all solutions using *njobs* processes.
-    
+
     If points is True, will assume test_data are the seismic point constraints.
     Otherwise, will assume it's the test data set.
     """
@@ -59,7 +59,7 @@ def score_all(solutions, test_data, points, njobs=1):
 def _call_score(args):
     """
     Call score_test_set or score_seismic_constraints on the solution.
-    
+
     Needed because multiprocessing.Pool.map only allows functions with
     a single argument.
     """
@@ -76,16 +76,16 @@ def _call_score(args):
 
 def predict_seismic(moho, lat, lon):
     """
-    Calculate the predicted Moho depth at the seismic points 
+    Calculate the predicted Moho depth at the seismic points
     from the estimated model.
-    
+
     Values are interpolated onto (lat, lon) from the given 'moho'.
     """
-    estimated = gridder.interp_at(moho.clat.ravel(), moho.clon.ravel(), moho.relief, 
+    estimated = gridder.interp_at(moho.clat.ravel(), moho.clon.ravel(), moho.relief,
                                   lat, lon, extrapolate=True)
     return estimated
 
-    
+
 def score_seismic_constraints(moho, lat, lon, height):
     """
     Return the MSE between the moho estimate and the point constraints.
@@ -95,10 +95,10 @@ def score_seismic_constraints(moho, lat, lon, height):
     return score
 
 
-def fit_all(solvers, njobs=1): 
+def fit_all(solvers, njobs=1):
     """
     Run ``fit`` for all solvers using *njobs* processes.
-    
+
     Utility function for cross-validation.
     """
     if njobs > 1:
@@ -114,9 +114,9 @@ def fit_all(solvers, njobs=1):
 def _call_fit(solver):
     """
     Call the ``fit`` method of a solver object.
-    
+
[…]

### 2016-03-23 manuscript/figures/strip-fonts.sh
Script to remove the fonts from the EPS figures
Does some hacky stuff

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+# Inspired by the solutions in 
+# http://stackoverflow.com/questions/28797418/replace-all-font-glyphs-in-a-pdf-by-converting-them-to-outline-shapes
+# http://tex.stackexchange.com/questions/24355/convert-from-pdf-to-eps-while-keeping-outlining-fonts
+
+for f in *.eps
+do
+    epstool --copy --bbox $f tmp.eps
+    gs -dNOPAUSE -dNOCACHE -dBATCH -sDEVICE=pdfwrite -dNoOutputFonts -dEPSCrop \
+        -sOutputFile="$(basename "$f" .eps).pdf" tmp.eps    
+    pdftops "$(basename "$f" .eps).pdf" -eps $f
+    convert -density 300 $f "$(basename "$f" .eps).png"
+    rm tmp.eps "$(basename "$f" .eps).pdf"
+done

### 2016-03-24 manuscript/figures/strip-fonts.sh
Convert text in EPS figures to paths

@@ -1,6 +1,7 @@
 #!/bin/bash
 
-# Inspired by the solutions in 
+# Remove the fonts embedded in the EPS files. The journal doesn't like them.
+# Inspired by the solutions in
 # http://stackoverflow.com/questions/28797418/replace-all-font-glyphs-in-a-pdf-by-converting-them-to-outline-shapes
 # http://tex.stackexchange.com/questions/24355/convert-from-pdf-to-eps-while-keeping-outlining-fonts
 
@@ -8,8 +9,7 @@ for f in *.eps
 do
     epstool --copy --bbox $f tmp.eps
     gs -dNOPAUSE -dNOCACHE -dBATCH -sDEVICE=pdfwrite -dNoOutputFonts -dEPSCrop \
-        -sOutputFile="$(basename "$f" .eps).pdf" tmp.eps    
-    pdftops "$(basename "$f" .eps).pdf" -eps $f
-    convert -density 300 $f "$(basename "$f" .eps).png"
-    rm tmp.eps "$(basename "$f" .eps).pdf"
+        -sOutputFile=tmp.pdf tmp.eps
+    pdftops tmp.pdf -eps $f
+    rm tmp.eps tmp.pdf
 done

### 2016-03-24 manuscript/figures/topng.sh
Script to convert eps to pngs
The journal system doesn't like the EPS figures inserted into the PDF.
They get very lowres and look terrible. The script converts to png and
latex then uses them instead.

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+# Convert the EPS files to PNG for the initial submission. The EPS are too high
+# res (especially the Moho models) and don't render properly on the journal
+# system.
+# use: bash topng.sh DPI
+
+for f in *.eps
+do
+    convert -density 400 $f "$(basename "$f" .eps).png"
+done
+convert -density 800 south-america-moho.eps south-america-moho.png

### 2016-03-24 manuscript/figures/topng.sh
Convert to high res pngs and then resample to lower res
Needed this because direct conversion to low res resulted in ugly white
lines in the Moho results figures.

@@ -7,6 +7,12 @@
 
 for f in *.eps
 do
-    convert -density 400 $f "$(basename "$f" .eps).png"
+    echo "Converting "$f
+    # Convert first to highres PNG because converting the Moho estimates to
+    # lowres is ugly. White lines appear between the model tiles.
+    convert -density 1200 $f tmp.png
+    # Now I can resample the highres PNG to a lower DPI without the ugly white
+    # lines.
+    convert -units PixelsPerInch tmp.png -resample 300 "$(basename "$f" .eps).png"
+    rm tmp.png
 done
-convert -density 800 south-america-moho.eps south-america-moho.png

### 2016-08-05 manuscript/manuscript.tex
Script to convert eps to pngs
The journal system doesn't like the EPS figures inserted into the PDF.
They get very lowres and look terrible. The script converts to png and
latex then uses them instead.
Thank Marcelo Assumpção for the seismological data
Tweaks to the R matrix definition
It contains the difference between adjacent **depths** of
tesseroids

@@
     pdfcreator={pdfTeX},
-    allcolors=blue,
+    allcolors=black,
 }
@@
     \centering
-    \includegraphics{figures/problem-concept}
+    \includegraphics[width=0.5\columnwidth]{figures/problem-concept}
     \caption{
@@
     \centering
-    \includegraphics{figures/tesseroid-coord-sys}
+    \includegraphics[width=0.5\columnwidth]{figures/tesseroid-coord-sys}
     \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
@@
 \noindent where $\mathbf{R}$ is an $L \times M$ finite-difference matrix
-representing $L$ first-order differences between adjacent tesseroids.
+representing $L$ first-order differences between the depths of adjacent
+tesseroids.
 
@@
     \centering
-    \includegraphics{figures/cv-grid-separation}
+    \includegraphics[width=0.5\columnwidth]{figures/cv-grid-separation}
     \caption{Sketch of a data grid separated into
@@
     \centering
-    \includegraphics{figures/synthetic-simple-data}
+    \includegraphics[width=0.5\columnwidth]{figures/synthetic-simple-data}
     \caption{
@@
     \centering
-    \includegraphics{figures/south-america-cv}
+    \includegraphics[width=0.5\columnwidth]{figures/south-america-cv}
     \caption{
@@
 software without which this work would not have been possible.
+We thank Dr. Marcelo Assumpção for making available to us the seismological
+Moho depth estimates.
 L. Uieda was supported by a scholarship from

### 2016-08-05 manuscript/manuscript.tex
Remove reference to steepest descent

@@
 ${\mathbf{A}^k}$
-and (2) the solution of the resulting $M \times M$ equation system
-(not required for Steepest Descent).
+and (2) the solution of the resulting $M \times M$ equation system.
 In practice, the derivatives in the Jacobian (Eq.~\ref{eq:jacobian})

### 2016-08-09 manuscript/manuscript.tex
Specify earth radius and correct bottlenecks statement

@@
 We tracked the total time spent inside each of the three functions
-that represent the largest computational bottlenecks of the inversion:
+that represent the potential bottlenecks of the inversion:
 solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
@@
 the Moho.
+All tesseroid models are defined with respect to a spherical Earth of radius
+6,378.137 km.
 

### 2016-08-17 manuscript/manuscript.tex
Rename our method section
Make it clearer where the speed gain comes from (not calculating A all
the time).

Fixes #31

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Regularized Bott's method in spherical coordinates}
+\subsection{Combining Bott's method, regularization, and tesseroids}
 
@@
 Using this approximation eliminates the cost of computing and storing
-the full Jacobian matrix $\mathbf{A}^k$ at each iteration
+the full $N \times M$-dimensional Jacobian matrix $\mathbf{A}^k$ at each
+iteration
 (Eq.~\ref{eq:jacobian}).
+Traditionally, the Jacobian matrix is computed using a first-order finite
+difference scheme,
+which requires $2 \times N \times M$ forward modeling operations per iteration.
+Using Eq.~\ref{eq:bott-gaussnewton} requires $N$ multiplications that need only
+be performed once.
+This provides a considerable speed gain.
+
 Matrix arithmetic operations can be performed efficiently by taking advantage
@@
 than 0.1\% of the computation time required for a single inversion.
-Hence, by employing the use of sparse matrices, our formulation retains the
+
+The main computational advantage of our formulation is that it retains the
 efficiency of Bott's method while stabilizing the solution through the well
@@
 Our method extends the Gauss-Newton formulation of Bott's method
-\citep{silva2014} to use tesseroids as model elements and smoothness
+\citep{silva2014} to use tesseroids as model elements and Tikhonov
 regularization.
-We retain the computational efficiency of Bott's method by taking advantage of
-the sparse nature of all matrices involved.
+The computational efficiency of our method is due to
+using Bott's approximation for the Jacobian matrix
+(Eq.~\ref{eq:bott-gaussnewton})
+and using sparse matrix algorithms for arithmetic operations and the solution
+of linear systems..
 We employ two cross-validation techniques to estimate the hyper-parameters of

### 2016-08-17 manuscript/figures/topng.sh
Make png conversion better use the Makefile
Instead of converting all eps to png in the script, use the Makefile to
manage dependencies.

@@ -3,16 +3,12 @@
 # Convert the EPS files to PNG for the initial submission. The EPS are too high
 # res (especially the Moho models) and don't render properly on the journal
 # system.
-# use: bash topng.sh DPI
-
-for f in *.eps
-do
-    echo "Converting "$f
-    # Convert first to highres PNG because converting the Moho estimates to
-    # lowres is ugly. White lines appear between the model tiles.
-    convert -density 1200 $f tmp.png
-    # Now I can resample the highres PNG to a lower DPI without the ugly white
-    # lines.
-    convert -units PixelsPerInch tmp.png -resample 300 "$(basename "$f" .eps).png"
-    rm tmp.png
-done
+# use: bash topng.sh figure.eps
+OUT=${1%.eps}.png
+echo "Converting "$1 to $OUT
+# Convert first to highres PNG because converting the Moho estimates to
+# lowres is ugly. White lines appear between the model tiles.
+convert -density 1200 $1 $OUT
+# Now I can resample the highres PNG to a lower DPI without the ugly white
+# lines.
+convert -units PixelsPerInch $OUT -resample 300 $OUT

### 2016-08-17 manuscript/manuscript.tex
Make CV plots pcolor instead of contourf
Fixes #33

@@
         the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
-        The colored contours represent
-        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
+        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}) in
+        $km^2$.
         The minimum (red triangle) is found at $z_{ref} = 30\ km$
@@
         the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
-        The colored contours represent
-        the Mean Square Error (Eq.~\ref{eq:msehyper}).
+        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}).
         The minimum (red triangle) is found at $z_{ref} = 35\ km$
@@
 with respect to the \citet{assumpcao2013a} data set.
-The MSE has a well-defined minimum, indicated by the red triangle,
+The MSE has a minimum, indicated by the red triangle,
 at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.
+The minimum is not as well-defined as for the CRUST1.0 synthetic
+(Fig.~\ref{fig:crust1-results}b),
+which is expected because $\Delta\rho$ is not homogeneous across all of
+South America and the surrounding oceans.
 

### 2016-08-17 manuscript/manuscript.tex
Mention that Bouguer plate works
Fixes #28

@@
 and using sparse matrix algorithms for arithmetic operations and the solution
-of linear systems..
+of linear systems.
+The Bouguer plate approximation in Eq.~\ref{eq:bott-gaussnewton} is adequate
+and the method converges
+even when the data are at higher altitudes and the model is not outcropping,
+as shown by the applications to synthetic data.
 We employ two cross-validation techniques to estimate the hyper-parameters of

### 2016-08-17 manuscript/manuscript.tex
Replace cross-validation with validation using seismological data
Fixes #29

@@
 in difficult to access regions traditionally poor in terrestrial data.
-An example is South America, where seismologic and terrestrial gravity data
+An example is South America, where seismological and terrestrial gravity data
 are traditionally concentrated around urban centers and coastal areas,
@@
 Additionally, we estimate the density-contrast and reference level
-simultaneously in a second cross-validation.
-Similarly to \citet{silva2006} and \citet{martins2010}, this cross-validation
-procedure uses knowledge of the Moho depths at certain points.
+simultaneously in a second validation step using knowledge of the Moho depth at
+a few points, similarly to \citet{silva2006} and \citet{martins2010}.
 Finally, we apply the proposed method to estimate the Moho depth for South
@@
 First, we assume fixed values for
-$z_{ref}$ and $\Delta\rho$ and perform a cross-validation procedure
+$z_{ref}$ and $\Delta\rho$ and perform a hold-out cross-validation procedure
 \citep{hansen1992} to estimate an optimal value for $\mu$.
@@
 the particular values of $z_{ref}$ and $\Delta\rho$ used.
-Second, we use the estimated $\mu$ to perform a second cross-validation
+Second, we use the estimated $\mu$ to perform a validation
 procedure to estimate $z_{ref}$ and $\Delta\rho$.
-The outcome of both cross-validations is not only the values of the three
-hyper-parameters but the final estimated Moho depths.
+The final outcomes of both steps are the values of the three hyper-parameters
+and the final estimated Moho depths.
 
@@
 information that is independent of the gravity data,
-such as knowledge of the parameters at certain points.
+such as knowledge of the parameters (Moho depths) at certain points.
 This information can be used in a manner similar to
@@
 the South American portion of the global CRUST1.0 model \citep{laske2013}.
-This application uses cross-validation to estimate all three hyper-parameters:
-$\mu$, $\Delta\rho$, and $z_{ref}$.
+This second application uses cross-validation to estimate $\mu$ and
+the validation procedure using synthetic seismological data
+to estimate $\Delta\rho$ and $z_{ref}$.
 The model and corresponding synthetic data are meant to simulate
@@
         $\mu = 0.0001$ (red triangle).
-        (b) Cross-validation results used to determine
+        (b) Validation results used to determine
         the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
@@
 
-The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
+The validation procedure to determine $\Delta\rho$ and $z_{ref}$
 requires knowledge of the Moho depth at certain points
@@
 
-We perform the cross-validation procedures in two parts.
+We estimate the three hyper-parameters in two parts.
 First, we run the cross-validation to estimate
@@
 $20\ km$ and $500\ kg/m^3$, respectively.
-Second, we use the estimated $\mu$ to run the cross-validation
+Second, we use the estimated $\mu$ to run the validation
+procedure with the synthetic seismological data
 to estimate $z_{ref}$ and $\Delta\rho$,
 thus obtaining the final estimated Moho depths.
-Fig.~\ref{fig:crust1-results} summarizes the results
-from both cross-validation runs and the final inversion results.
-
-For the first cross-validation,
+Fig.~\ref{fig:crust1-results} summarizes the results.
+
+For the cross-validation,
 we separate the synthetic data (Fig.~\ref{fig:grid_separation}) into
@@
 
-In the second cross-validation,
+In the validation using seismological data,
 we use the estimated value of $\mu$ in all inversions.
@@
 Fig.~\ref{fig:crust1-results}b
-shows a colored-contour map of the MSE
+shows a pseudo-color map of the MSE
 with a minimum (marked by the red triangle)
@@
 
-Fig.~\ref{fig:crust1-results}c shows the final solution after both
-cross-validation procedures.
+Fig.~\ref{fig:crust1-results}c shows the final solution after
+cross-validation and validation using seismological data.
 The recovered model is smooth, indicating that the cross-validation procedure
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Gravity and seismic data}
+\subsection{Gravity and seismological data}
 
@@
 were estimated from seismological data by \citet{assumpcao2013a}.
-This data set is used in the cross-validation procedure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inversion and cross-validation}
+This data set is used in the validation procedure.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Inversion, cross-validation, and validation using seismological
+data}
 
@@
         corresponds to $\mu = 10^{-10}$.
-        (b) Cross-validation to determine
+        (b) Validation to determine
         the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
@@
 As in the CRUST1.0 synthetic data test (section~\ref{sec:crust1}),
-we perform the cross-validation in two parts.
+we estimate the hyper-parameters in two steps.
 First, we run the cross-validation to estimate
@@
 $20\ km$ and $500\ kg/m^3$, respectively.
-Second, we use the estimated $\mu$ to run the cross-validation
+Second, we use the estimated $\mu$ to run the validation
+using the seismological data of \citet{assumpcao2013a}
 to estimate $z_{ref}$ and $\Delta\rho$,
@@
 
-We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
-inversions.
+We proceed with the validation using seismological data
+using $\mu = 10^{-10}$ in all inversions.
 We test all combinations of
-seven values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
+nine values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
 and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
 with 50 $kg/m^3$ intervals.
-Fig.~\ref{fig:sam-cv}b shows a map of the MSE
+Fig.~\ref{fig:sam-cv}b shows a pseudo-color map of the MSE
 with respect to the \citet{assumpcao2013a} data set.
@@
 (Fig.~\ref{fig:crust1-results}b),
-which is expected because $\Delta\rho$ is not homogeneous across all of
-South America and the surrounding oceans.
+which is expected because in reality $\Delta\rho$ is not homogeneous across all
+of South America and the surrounding oceans.
 
@@
 as shown by the applications to synthetic data.
-We employ two cross-validation techniques to estimate the hyper-parameters of
-the inversion: the regularization parameter, the Moho density-contrast, and the
-Normal Earth Moho depth.
+We employ hold-out cross-validation to estimate the regularization parameter
+and a validation procedure using seismological data to estimate the Moho
+density-contrast and the Normal Earth Moho depth.
 
@@
 (Fig.~\ref{fig:crust1-results})
-shows that the cross-validation using pointwise Moho depth information
+shows that the validation using pointwise Moho depth information
 is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
@@
 software without which this work would not have been possible.
-We thank Dr. Marcelo Assumpção for making available to us the seismological
-Moho depth estimates.
+We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
+estimates.
 L. Uieda was supported by a scholarship from

### 2016-08-18 manuscript/manuscript.tex
Main advantages of our method in the conclusion
Fixes #30

@@
 
+There are two main advantages of the proposed method over previous works.
+First, unlike the Parker-Oldenburg method \citep{oldenburg1974} or methods
+using rectangular prisms, our inversion method does not require the data to be
+projected onto a plane.
+Second, the Parker-Oldenburg method and methods derived from \citet{bott1960}
+\citep[e.g., ][]{silva2014,santos2015} cannot apply the
+traditional methodology for constraining inverse problems
+described in \citet{silva2001b}.
+Our method has no such restriction because we use the formalism of traditional
+Tikhonov inversion.
+However, the proposed method is not without limitations.
+It requires data on a regular grid and restricts the
+model to be a regular mesh tied to the data grid.
+There is also the limitation that, like \citet{bott1960},
+our method only works for gravity disturbances and not the gravity gradients.
+
 The test on simple synthetic data shows that our inversion method is able to

### 2016-08-18 manuscript/manuscript.tex
Started discussion section explaining why andes is wrong
Fixes #32

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Discussion}
+
+Differences between our Moho depth model and the seismological data
+(shown in Fig.~\ref{fig:sam-residuals}b)
+may indicate regions where our initial assumptions
+(summarized in Fig.~\ref{fig:anomalysketch})
+are inadequate or where we have
+failed to correct for all crustal and mantle sources.
+In general, our model fits both the seismological and gravity data well
+in the oceans and in the Atlantic coast.
+The largest differences are seen the along the Andean Province.
+These differences are likely caused by the fact that our model does not include
+the subducting Nazca plate.
+Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
+suggests that our inversion method is not able to fully recover deep Moho
+depths in the Andes,
+even without the effect of the subducting plate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}

### 2016-08-18 manuscript/manuscript.tex
Describe parecis and parnaiba

@@
 failed to correct for all crustal and mantle sources.
-In general, our model fits both the seismological and gravity data well
-in the oceans and in the Atlantic coast.
 The largest differences are seen the along the Andean Province.
@@
 even without the effect of the subducting plate.
+
+In general, our model fits both the seismological and gravity data well
+in the oceans and in the Atlantic coast.
+The Parnaíba Basin has deep Moho surrounding its continental borders, following
+inward with a shallower Moho, then a deeper step, and finally a shallower
+part in the middle of the basin.
+Our model has small differences with the few seismological data points that
+fall inside and on the borders of the basin.
+However, recent deep seismic reflection studies by \citet{daly2014} that cross
+the basin in from west to east agree with our model.
+Our model reveals a deep Moho in the Northern border of the Parecis Basin that
+is corroborated by a single seismological data point.
 

### 2016-08-18 manuscript/manuscript.tex
Explain amazon and parana basin discrepancies

@@
 
-In general, our model fits both the seismological and gravity data well
-in the oceans and in the Atlantic coast.
+In the Amazon and Paraná Basins, our model underestimates the seismological
+data by up to 15 km but fits the gravity data.
+This indicates that a mass excess is present in the crust or upper mantle.
+A body with positive density contrast that was unaccounted in the data
+processing will make the observed gravity disturbance greater than it would
+be otherwise.
+This will lead the inversion to produce a shallower Moho estimate.
+These discrepancies between gravity and seismological estimates has been noted
+before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
+for the Paraná Basin.
+Both studies propose high density rocks in the lower crust as probable causes
+for the discrepancies.
+Another possible cause for the observed discrepancy in our model is our failure
+to fully remove from the data the igneous intrusions present in both basins.
+Our sediment correction was performed with the CRUST1.0 model
+\citep{laske2013}.
+Using a more detailed sediment model for South America might lead to more
+accurate results for these basins.
+
+Greater confidence in our Moho model can be had in areas where it is able to
+fit both the gravity and the seismological data.
+In such places, a gravity-derived model can serve as a better interpolator for
+the seismological point estimates.
+In general, our model fits both both data sets in the oceans and in the
+Atlantic coast of the continent.
 The Parnaíba Basin has deep Moho surrounding its continental borders, following

### 2016-08-18 manuscript/manuscript.tex
About the Guyana Basin and finish discussion
Fixes #35

--- 2016-08-18 manuscript/manuscript.tex
@@
 Differences between our Moho depth model and the seismological data
-(shown in Fig.~\ref{fig:sam-residuals}b)
+(Fig.~\ref{fig:sam-residuals}b)
 may indicate regions where our initial assumptions
@@
 failed to correct for all crustal and mantle sources.
-In general, our model fits both the seismological and gravity data well
-in the oceans and in the Atlantic coast.
-The largest differences are seen the along the Andean Province.
-These differences are likely caused by the fact that our model does not include
+The largest differences are seen along the Andean Province and
+are likely caused by the fact that our model does not include
 the subducting Nazca plate.
@@
 even without the effect of the subducting plate.
+In the Guyana Basin, our model is able to fit the gravity data
+but differs from the seismological data by up to $\pm 10$ km with
+no clear pattern for the distribution of the  differences.
+A possible explanation is an inaccuracy in the CRUST1.0 sediment model
+\citep{laske2013} used to correct our gravity data.
+The inversion results will be biased
+if the input data includes effects other than the anomalous Moho.
+
+In the Amazon and Paraná Basins, our model fits the gravity data but
+underestimates the seismological data by up to 15 km.
+This indicates that a mass excess is present in the crust or upper mantle.
+A body with positive density contrast whose gravitational effect was not
+removed from the data during processing will make the observed gravity
+disturbance greater than it would be otherwise.
+This will cause the inversion to produce a shallower Moho estimate.
+These discrepancies between gravity and seismological estimates have been noted
+before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
+for the Paraná Basin.
+Both studies propose high density rocks in the lower crust as probable causes
+for the discrepancies.
+Another possible cause for the observed discrepancy in our model could be our
+failure to fully remove from the data the effects of the igneous intrusions
+present in both basins.
+Using a sediment model for South America more detailed than CRUST1.0
+might lead to more accurate results for these basins.
+
+Greater confidence in our Moho model can be had in areas where it is able to
+fit both the gravity and the seismological data.
+In such places, a gravity-derived model can serve as an interpolator for
+the seismological point estimates.
+In general, our model fits both data sets in the oceans,
+the Atlantic coast of the continent, and central Brazil.
+In the Parnaíba Basin, our model has small differences with the few
+seismological data points that fall inside and on the borders of the basin.
+The Moho surrounding the basins continental borders is deep, following
+inward with a shallower Moho, then a deeper step, and finally a shallower
+part in the middle of the basin.
+Recent deep seismic reflection studies by \citet{daly2014} that cross
+the basin from west to east agree with our model.
+The Northern border of the Parecis Basin has a deep Moho in our model that
+is corroborated by a single seismological data point.
 

### 2016-08-20 manuscript/manuscript.tex
Thank the editor and reviewers
Fixes #24
Minor changes to the text

@@
 problem, for example
-\citet{bott1960, barbosa1999b, barbosa1999a, barnes2012, leao1996, martins2010,
-martins2011, oldenburg1974, reguzzoni2013, santos2015, silva2006, silva2014},
+\citet{bott1960, barbosa1997, barbosa1999b, barbosa1999a, barnes2012, leao1996,
+martins2010, martins2011, oldenburg1974, reguzzoni2013, santos2015, silva2006,
+silva2014},
 to name a few.
@@
 sedimentary basin
-\citep[e.g., ][]{barbosa1999a, barbosa1999b, martins2010, martins2011, sun2014}.
+\citep[e.g., ][]{barbosa1997, barbosa1999a, barbosa1999b, martins2010,
+martins2011, sun2014}.
 These methods approximate the sedimentary pack by a set of juxtaposed
@@
 The use of rectangular prisms implies a planar Earth approximation and may not
-be adequate for depth-to-Moho estimates in a continental-scale study.
+be adequate for depth-to-Moho estimates in continental- or global-scale study.
 A straightforward way to circumvent this hindrance is to adapt one of the
@@
 Bott's method uses a Bouguer plate approximation of the gravitational effect of
-the relief, $d_i = 2\pi G \Delta\rho z_i$.
-The derivative of $d_i$ with respect to the parameter $z_i$ is
+the relief, $d_i = 2\pi G \Delta\rho\ p_i$.
+The derivative of $d_i$ with respect to the parameter $p_i$ is
 $2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
@@
 for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
-but replaces the full Jacobian matrix with the Bouguer plate approximation
-(Eq.~\ref{eq:bott-gaussnewton}).
-Here, the Jacobian matrix is a diagonal matrix whose elements are invariant
-along successive iterations.
+but replaces the full Jacobian matrix with the Bouguer plate approximation.
+Here, the Jacobian matrix is replaced by a diagonal matrix
+(Eq.~\ref{eq:bott-gaussnewton}) whose elements are invariant along successive
+iterations.
 Using this approximation eliminates the cost of computing and storing
@@
 (Eq.~\ref{eq:jacobian}).
-Traditionally, the Jacobian matrix is computed using a first-order finite
+Traditionally, the full Jacobian matrix is computed using a first-order finite
 difference scheme,
@@
 
-The main computational advantage of our formulation is that it retains the
+The main advantage of our formulation is that it retains the
 efficiency of Bott's method while stabilizing the solution through the well
 established formalism of Tikhonov regularization.
+For example, the total variation approach used by \citet{martins2011} could
+potentially be implemented in a more straight forward manner than done by
+\citet{santos2015}.
 
@@
 Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
-after cross-validation.
+after the cross-validation.
 The recovered model is smooth, indicating that the cross-validation procedure
@@
 and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
-(a total of 18921 observations).
+(a total of 18,921 observations).
 We contaminate the synthetic data with normally distributed pseudo-random noise
@@
 International Centre for Global Earth Models (ICGEM) web-service
-\citep[][ \url{http://icgem.gfz-potsdam.de/ICGEM/})]{barthelmes2012}
+\citep[][ \url{http://icgem.gfz-potsdam.de/ICGEM/}]{barthelmes2012}
 in the form of the complete gravity field
@@
 underestimates the seismological data by up to 15 km.
-This indicates that a mass excess is present in the crust or upper mantle.
+This indicates that a mass excess may be present in the crust or in the upper
+mantle.
 A body with positive density contrast whose gravitational effect was not
@@
 Our method extends the Gauss-Newton formulation of Bott's method
-\citep{silva2014} to use tesseroids as model elements and Tikhonov
+to use tesseroids as model elements and Tikhonov
 regularization.
@@
 using Bott's approximation for the Jacobian matrix
-(Eq.~\ref{eq:bott-gaussnewton})
 and using sparse matrix algorithms for arithmetic operations and the solution
 of linear systems.
-The Bouguer plate approximation in Eq.~\ref{eq:bott-gaussnewton} is adequate
-and the method converges
+This approximation for the Jacobian matrix is adequate and the method converges
 even when the data are at higher altitudes and the model is not outcropping,
@@
 There are two main advantages of the proposed method over previous works.
-First, unlike the Parker-Oldenburg method \citep{oldenburg1974} or methods
+First, unlike the Parker-Oldenburg method or methods
 using rectangular prisms, our inversion method does not require the data to be
 projected onto a plane.
-Second, the Parker-Oldenburg method and methods derived from \citet{bott1960}
-\citep[e.g., ][]{silva2014,santos2015} cannot apply the
-traditional methodology for constraining inverse problems
-described in \citet{silva2001b}.
+Second, the Parker-Oldenburg method and methods derived from Bott's method
+cannot apply the traditional methodology for constraining inverse problems.
 Our method has no such restriction because we use the formalism of traditional
@@
 model to be a regular mesh tied to the data grid.
-There is also the limitation that, like \citet{bott1960},
-our method only works for gravity disturbances and not the gravity gradients.
+Like Bott's method, our method only works for gravity disturbances and not for
+the gravity gradients.
 
 The test on simple synthetic data shows that our inversion method is able to
-recover a smooth Moho relief with a homogeneous density-contrast.
+recover a smooth Moho relief with a homogeneous density-contrast distribution.
 The inversion was not able to fully recover the shortest wavelength feature in
@@
 high-frequency (sharp) variations.
-The cross-validation Mean Square Error curve in Fig.~\ref{fig:simple-results}e
-has a well-defined minimum, indicating a value of the regularization parameter
-($\mu$) whose corresponding estimate best predicts data that were not included
-in the inversion.
+The cross-validation Mean Square Error curve has a well-defined minimum,
+indicating a value of the regularization parameter ($\mu$) whose corresponding
+estimate best predicts data that were not included in the inversion.
 Using this value of $\mu$ in the inversion leads to a stable solution
@@
 
-The source code profiling results presented in Table~\ref{profiling}
-confirm the efficiency of the proposed method.
-When using sparse matrices, solving linear systems and performing matrix
-multiplications together account for a mere 0.067\% of the total computation
-time required for a single inversion.
+The efficiency of the proposed method is because solving linear systems and
+performing matrix multiplications together account for a mere 0.067\% of the
+total computation time required for a single inversion.
 The majority of the computation time (99.824\%) is spent on forward modeling.
@@
 already available in the literature.
-For example, the total variation approach used by \citet{martins2011} could
-potentially be implemented in a more straight forward manner than done by
-\citet{santos2015}.
 
 The more complex synthetic data test based on CRUST1.0
-(Fig.~\ref{fig:crust1-results})
 shows that the validation using pointwise Moho depth information
@@
 regularization, like
-the weighted smoothness inversion \citep{barbosa1999a},
-Cauchy norm regularization \citep{sacchi1996, pilkington2008},
-entropic regularization \citep{silva2010},
-total variation regularization \citep{martins2011},
-or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.
+the weighted smoothness inversion,
+Cauchy norm regularization,
+entropic regularization,
+total variation regularization,
+or an adaptive mixed smoothness-sharpness regularization.
 
@@
 America.
-Our estimated Moho depth model is in accordance with previous results by
-\citet{vandermeijde2013}.
+Our estimated Moho depth model is in accordance with previous results.
 The model fits well the gravity and seismic data in all oceanic regions, the
@@
 able to fit the gravity data but differs significantly from the seismic data.
-\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
-Paraná and Amazonas Basins, respectively, as high density rocks in the lower
-crust.
+These discrepancies in the Paraná and Amazonas Basins are interpreted in the
+literature as high density rocks in the lower crust.
 In general, differences between a gravity and a seismically derived Moho model
@@
 We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
-estimates.
+estimates,
+Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
+comments that helped improve this work.
 L. Uieda was supported by a scholarship from

### 2016-10-05 manuscript/manuscript.tex
Fixes reference to bird20013
Had an extra "a" in the citation tag

@@
         Solid orange lines mark the limits of the main lithospheric plates
-        \citep{bird2003a};
+        \citep{bird2003};
         AF: Africa Plate,

### 2016-10-06 manuscript/manuscript.tex
Add reference to archived repo on figshare

@@
 
-All source code, Jupyter notebooks, data, and results
-can be found at the online repository
-\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
+All source code, Jupyter notebooks, data, and model results
+are made available through an online repository
+\citep[][ \url{http://dx.doi.org/10.6084/m9.figshare.3987267} or
+\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}]{uieda2016a}.
 The repository also contains instructions for replicating all results presented
 here.
-An archived version of this repository is also available at
-\url{http://dx.doi.org/...}
-(\textbf{Note to reviewers: the archived version will be uploaded upon
-publication}).
 

### 2016-10-06 manuscript/manuscript.tex
Add sentence to conclusion about figshare repo
Thank PhD commity for feedback
Fixes #38

@@
 
+Our gravity-derived Moho model for South America
+can be downloaded from the online repository 
+\url{http://dx.doi.org/10.6084/m9.figshare.3987267}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 software without which this work would not have been possible.
-We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
-estimates,
-Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
+We thank 
+Marcelo Assumpção for providing the seismological Moho depth estimates,
+Naomi Ussami, Julio C. S. O. Lyrio, Cosme F. P. Neto, and Daniel R. Franco
+for their constructive feedback,
+and Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
 comments that helped improve this work.

### 2019-10-04 manuscript/manuscript.tex
Format manuscript without GJI style for archival

@@
-\documentclass[extra,mreferee]{gji}
-%\documentclass[extra]{gji}
-\usepackage{timet}
+\documentclass[twocolumn]{article}
+\usepackage{graphicx}
 \usepackage{amsmath}
-\usepackage{graphicx}
+\usepackage[left=0.7in,right=0.7in,top=1.3in,bottom=1in]{geometry}
+\usepackage[utf8]{inputenc}
+\usepackage[round]{natbib}
+\usepackage{fixltx2e}
 \usepackage{url}
-\usepackage[utf8]{inputenc}
-% To make two column figures appear in the correct order
-\usepackage{fixltx2e}
-% To make annotations on the sides
-\usepackage{todonotes}
+\usepackage[pdftex,colorlinks=true]{hyperref}
+\usepackage{fancyhdr}
 
@@
 }
-\title[]{\Title}
-\author[]{
-    Leonardo Uieda$^{1,2}$,
-    Valéria C. F. Barbosa$^{2}$
+\newcommand{\Author}{Uieda, L. and Barbosa, V.C.F.}
+\newcommand{\AuthorAffil}{
+    {\large
+        Leonardo Uieda$^{1,2,*}$
+        and
+        Val\'eria C. F. Barbosa$^{2}$
+    }
+    \\[0.4cm]
+    {\small $^1$ Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.}
     \\
-    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
-    e-mail: leouieda@gmail.com
+    {\small $^2$ Observat\'orio Nacional, Rio de Janeiro, Brazil.}
     \\
-    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
-}
-% Metadata for the generated PDF
-\usepackage[pdftex,colorlinks=true]{hyperref}
+    {\small $^*$ e-mail: leouieda@gmail.com}
+}
+\newcommand{\Journal}{Geophysical Journal International}
+\newcommand{\Year}{2017}
+\newcommand{\DOI}{10.1093/gji/ggw390}
+\newcommand{\DOILink}{\href{https://doi.org/\DOI}{doi.org/\DOI}}
+
+\setlength{\columnsep}{2\columnsep}
 \hypersetup{
+    allcolors=blue,
     pdftitle={\Title},
-    pdfauthor={Leonardo Uieda (leouieda@gmail.com)},
-    pdfsubject={},
+    pdfauthor={\Author},
     pdfkeywords={\Keywords},
-    pdfcreator={pdfTeX},
-    allcolors=black,
-}
+}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{
+    \fontsize{9pt}{12pt}\selectfont
+    \Author{}, \Year{}, doi:\DOI{}
+}
+\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
+\renewcommand{\headrulewidth}{0pt}
 
@@
 
-\label{firstpage}
+\title{\Title}
+\author{\AuthorAffil}
+\date{
+    \normalsize
+    Accepted 2016 October 13. Received in original form 2016 March 24.
+    \\[0.4cm]
+    This is a pre-copyedited, author-produced PDF of an article
+    published in \textit{\Journal} following peer review.
+    The version of record
+    ``\textit{\Author{} (\Year{}). \Title{}. \Journal{}. doi:\DOI{}}''
+    is available online at: \DOILink{}.
+}
+
 \maketitle
@@
 
+\vspace{0.4cm}
 \noindent\textbf{Key words:} \Keywords
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/problem-concept}
+    \includegraphics[width=\columnwidth]{figures/problem-concept}
     \caption{
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/cv-grid-separation}
+    \includegraphics[width=\columnwidth]{figures/cv-grid-separation}
     \caption{Sketch of a data grid separated into
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/synthetic-simple-data}
+    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
     \caption{
@@
 \end{figure}
+
+We simulate the transition from a continental-type Moho to an oceanic-type Moho
+using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
+juxtaposed tesseroids (a total of $M = 2000$ model elements).
+The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
+and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
+Fig.~\ref{fig:simple-data}a shows the model Moho depths where we can clearly
+see an eastward crustal thinning.
+In Fig.~\ref{fig:simple-data}a, each pixel in the pseudo-color image
+corresponds to a tesseroid of the model.
+
+The synthetic data were forward modeled on a regular grid of
+$N_{lat} \times N_{lon} = 79 \times 99$ points
+(a total of $N = 7821$ observations)
+at a constant height of 50 km.
+The data were contaminated with pseudo-random noise
+sampled from a normal distribution with zero mean and 5 mGal standard deviation.
+Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set
+exhibiting an eastward increase due to the simulated eastward
+crustal thinning shown in Fig.~\ref{fig:simple-data}a.
+The data grid spacing is half the grid spacing of the tesseroid model
+so that, when separating the training and testing data sets
+(Fig.~\ref{fig:grid_separation}),
+the training data set points will fall directly above each model element.
 
@@
 \end{figure*}
-
-We simulate the transition from a continental-type Moho to an oceanic-type Moho
-using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
-juxtaposed tesseroids (a total of $M = 2000$ model elements).
-The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
-and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
-Fig.~\ref{fig:simple-data}a shows the model Moho depths where we can clearly
-see an eastward crustal thinning.
-In Fig.~\ref{fig:simple-data}a, each pixel in the pseudo-color image
-corresponds to a tesseroid of the model.
-
-The synthetic data were forward modeled on a regular grid of
-$N_{lat} \times N_{lon} = 79 \times 99$ points
-(a total of $N = 7821$ observations)
-at a constant height of 50 km.
-The data were contaminated with pseudo-random noise
-sampled from a normal distribution with zero mean and 5 mGal standard deviation.
-Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set
-exhibiting an eastward increase due to the simulated eastward
-crustal thinning shown in Fig.~\ref{fig:simple-data}a.
-The data grid spacing is half the grid spacing of the tesseroid model
-so that, when separating the training and testing data sets
-(Fig.~\ref{fig:grid_separation}),
-the training data set points will fall directly above each model element.
 
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/south-america-cv}
+    \includegraphics[width=\columnwidth]{figures/south-america-cv}
     \caption{
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/south-america-moho}
+    \includegraphics[width=0.9\textwidth]{figures/south-america-moho}
     \caption{
